### 2023-07-13 index.qmd
init

---
title: ""
pagetitle: "CarterLab | Home"
toc: false
---

![](images/uni-hall-front.jpg)

The **Action, Cognition, and Metascience Lab** is an interdisciplinary research team investigating basic scientific questions about how the human brain controls and learns skilled actions. We study decision-making for action and practice factors supporting skill acquisition and maintenance in single- and multi-agent scenarios. We also conduct metascience research to gain important insights into research practices within kinesiology and sport science. We are located in the Ivor Wynne Centre, which is home to the [Department of Kinesiology](https://www.science.mcmaster.ca/kinesiology/) within the [Faculty of Science](https://www.science.mcmaster.ca/) at [McMaster University](https://www.mcmaster.ca/).

#### Recent lab news ---------

<font color="#d08770">[June 28 2023].</font> **New award**. Congratulations Dr. Laura St. Germain on a successfully defending your doctoral work.

<font color="#d08770">[June 20 2023].</font> **New award**. Congratulations to Laura St. Germain (Ph.D. Candidate) on winning the 2023 Franklin Henry Young Scientist Award in Motor Control and Learning from the Canadian Society for Psychomotor Learning and Sport Psychology.

<font color="#d08770">[June 16 2023].</font> **New preprint**. McKay, B., Corson, A.E., Seedu, J., De Faveri, C.S., Hasan, H., Arnold, K., Adams, F.C., & Carter, M.J. Reporting bias, not external focus: A robust Bayesian meta-analysis of the attentional focus literature. *SportR*$\chi$*iv*. doi: <https://doi.org/10.51224/SRXIV.304>

<font color="#d08770">[May 26 2023].</font> **Paper accepted**. Lokesh, R., Sullivan, S.R., St. Germain, L., Roth, A.M., Calalo, J.A., Buggeln, J., Ngo, T., Marchhart, V.R.F., Carter, M.J, & Cashaback, J.G.A. Visual accuracy dominates over haptic speed for state estimation of a partner during collaborative sensorimotor interactions. *Journal of Neurophysiology*.

### 2023-07-13 join.qmd
init

---
title: "Interested in joining the team"
pagetitle: "CarterLab | Join"
toc: false
---

We are always seeking curious, creative, and self-motivated students to enhance our research team and learning environment. The Action, Cognition, & Metascience lab at McMaster University is committed to the training and development of all its team members by promoting a highly collaborative research and training environment, and fostering a passion for lifelong learning and discovery. We are committed to supporting and promoting diversity and equity in our lab. **Everyone---regardless of race, nationality, sex, gender, sexual orientation, age, disability, or religion---is welcome in our lab.**

Updates in progress...

### 2023-07-13 news.qmd
init

--- 2023-07-13 index.qmd
@@
 ---
-title: ""
-pagetitle: "CarterLab | Home"
+title: "Lab News"
+pagetitle: "CarterLab | News"
 toc: false
 ---
-
-![](images/uni-hall-front.jpg)
-
-The **Action, Cognition, and Metascience Lab** is an interdisciplinary research team investigating basic scientific questions about how the human brain controls and learns skilled actions.
-We study decision-making for action and practice factors supporting skill acquisition and maintenance in single- and multi-agent scenarios.
-We also conduct metascience research to gain important insights into research practices within kinesiology and sport science.
-We are located in the Ivor Wynne Centre, which is home to the [Department of Kinesiology](https://www.science.mcmaster.ca/kinesiology/) within the [Faculty of Science](https://www.science.mcmaster.ca/) at [McMaster University](https://www.mcmaster.ca/).
-
-#### Recent lab news ---------
 
@@
 *Journal of Neurophysiology*.
+
+<font color="#d08770">[May 19 2023].</font> **New preprint**.
+St.
+Germain, L., McKay, B., Tandon, C., Seedu, J., Barbera, L., Carrillo, C., Brown, D.M.Y., & Carter, M.J.
+Autonomy-supportive instructional language does not enhance skill acquisition compared to controlling instructional language.
+*SportR*$\chi$*iv*.
+doi: <https://doi.org/10.51224/SRXIV.298>
+
+<font color="#d08770">[April 13 2023].</font> **Paper accepted**.
+McKay, B., Bacelar, M.F.B., Parma, J.O., Miller, M.W., & Carter, M.J.
+The combination of reporting bias and underpowered study designs has substantially exaggerated the motor learning benefits of self-controlled practice and enhanced expectancies: A meta-analysis.
+*International Review of Sport and Exercise Psychology*.

### 2023-07-13 papers.qmd
init

---
title: "Papers"
pagetitle: "CarterLab | Papers"
toc: true
toc-title: "Jump to..."
listing:
  - id: preprints
    contents: "papers/preprints/*.qmd"
    template: papers.ejs
    sort:
      - "year desc"
      - "author"
  - id: papers2020
    contents: "papers/2020-25/*.qmd"
    template: papers.ejs
    sort:
      - "year desc"
      - "author"
  - id: papers2015
    contents: "papers/2015-19/*.qmd"
    template: papers.ejs
    sort:
      - "year desc"
      - "author"
  - id: papers2010
    contents: "papers/2010-14/*.qmd"
    template: papers.ejs
    sort:
      - "year desc"
      - "author"
---

## Preprints

:::{#preprints}
:::

## 2020--23

:::{#papers2020}
:::

## 2015--19

:::{#papers2015}
:::

## 2010--14

:::{#papers2010}
:::

### 2023-07-13 papers/2010-14/2010_patterson_hms.qmd
init

---
title: "Learner regulated knowledge of results during the acquisition of multiple timing goals"
type: "article"
author: "Patterson JT. & Carter MJ."
year: "2010"
publication: "Human Movement Science"
pdf: ""
doi: "https://doi.org/10.1016/j.humov.2009.12.003"
github: ""
materials: ""
#supplementary: ""
preprint: ""
toc: false
---

## Citation

### APA 7th

> Patterson, J. T., & Carter, M. J. (2010). Learner regulated knowledge of results during the acquisition of multiple timing goals. *Human Movement Science*, 29(2), 214–227. https://doi.org/10.1016/j.humov.2009.12.003

### Bibtex

<pre>
@article{,
  title = {Learner Regulated Knowledge of Results during the Acquisition of Multiple Timing Goals},
  author = {Patterson, Jae T. and Carter, Michael J.},
  date = {2010-04-01},
  journaltitle = {Human Movement Science},
  shortjournal = {Human Movement Science},
  volume = {29},
  number = {2},
  pages = {214--227},
  issn = {0167-9457},
  doi = {10.1016/j.humov.2009.12.003},
  url = {https://www.sciencedirect.com/science/article/pii/S0167945710000035},
  urldate = {2023-07-13},
  langid = {english},
  keywords = {Knowledge of results,Motor learning,Motor skills,Practice,Self-control}
}
</pre>

## Abstract

The purpose of the present experiment was to examine the advantages of a learner controlled KR schedule during the acquisition of three novel sequential timing tasks. The self-regulated group requested KR when necessary during the acquisition period while participants in the yoked condition replicated the KR schedule of a self-regulated counterpart, without the choice. The self-regulated condition demonstrated superior performance in retention and transfer, with a relative KR frequency similar for all three sequences. Similar to Chiviacowsky and Wulf (2002), learners also demonstrated a preference for KR after perceived good trials, independent of defined task difficulty. Thus, the results extend previous research by suggesting a generalized learning strategy by performers acquiring multiple motor task goals.

### 2023-07-13 papers/2010-14/2011_patterson_rqes.qmd
init

---
title: "Decreasing the proportion of self-control trials during the acquisition period does not compromise the learning advantages in a self-controlled context"
type: "article"
author: "Patterson JT., Carter MJ., & Sanli E."
year: "2011"
publication: "Research Quarterly for Exercise and Sport"
pdf: ""
doi: "https://doi.org/10.1080/02701367.2011.10599799"
github: ""
materials: ""
#supplementary: ""
preprint: ""
toc: false
---

## Citation

### APA 7th

> Patterson, J. T., Carter, M. J., & Sanli, E. (2011). Decreasing the proportion of self-control trials during the acquisition period does not compromise the learning advantages in a self-controlled context. *Research Quarterly for Exercise and Sport*, 82(4), 624–633. https://doi.org/10.1080/02701367.2011.10599799

### Bibtex

<pre>
@article{,
  title = {Decreasing the Proportion of Self-Control Trials during the Acquisition Period Does Not Compromise the Learning Advantages in a Self-Controlled Context},
  author = {Patterson, Jae T. and Carter, Michael J. and Sanli, Elizabeth},
  date = {2011-12-01},
  journaltitle = {Research Quarterly for Exercise and Sport},
  volume = {82},
  number = {4},
  eprint = {22276404},
  eprinttype = {pmid},
  pages = {624--633},
  publisher = {{Routledge}},
  issn = {0270-1367},
  doi = {10.1080/02701367.2011.10599799},
  url = {https://doi.org/10.1080/02701367.2011.10599799},
  urldate = {2023-07-13},
  keywords = {knowledge of results,perceptuomotor processes,sequence learning}
}
</pre>

## Abstract

The present experiment examined the learning effects of participants self-controlling their receipt of knowledge of results (KR) on all or half of their acquisition trials (50%). For participants who were provided 50% self-control, the first half of their acquisition period consisted of receiving KR on all trials, or according to a faded-KR schedule. Participants practiced a sequential timing task. The results showed that independent of practice condition, participants who self-controlled their KR during the acquisition period demonstrated superior performance compared to the respective yoked conditions in the retention and transfer portion of the experiment. These results extend previous research by suggesting that decreasing the proportion of self-control trials does not compromise learning in a self-controlled context.

### 2023-07-13 papers/2010-14/2012_carter_hms.qmd
init

---
title: "Self-controlled knowledge of results: Age-related differences in motor learning, strategies, and error detection"
type: "article"
author: "Carter MJ. & Patterson JT."
year: "2012"
publication: "Human Movement Science"
pdf: ""
doi: "https://doi.org/10.1016/j.humov.2012.07.008"
github: ""
materials: ""
#supplementary: ""
preprint: ""
toc: false
---

## Citation

### APA 7th

> Carter, M. J., & Patterson, J. T. (2012). Self-controlled knowledge of results: Age-related differences in motor learning, strategies, and error detection. *Human Movement Science*, 31(6), 1459–1472. https://doi.org/10.1016/j.humov.2012.07.008

### Bibtex

<pre>
@article{,
  title = {Self-Controlled Knowledge of Results: {{Age-related}} Differences in Motor Learning, Strategies, and Error Detection},
  shorttitle = {Self-Controlled Knowledge of Results},
  author = {Carter, Michael J. and Patterson, Jae T.},
  date = {2012-12-01},
  journaltitle = {Human Movement Science},
  shortjournal = {Human Movement Science},
  volume = {31},
  number = {6},
  pages = {1459--1472},
  issn = {0167-9457},
  doi = {10.1016/j.humov.2012.07.008},
  url = {https://www.sciencedirect.com/science/article/pii/S0167945712001017},
  urldate = {2023-07-13},
  langid = {english},
  keywords = {Error detection,Feedback,Older adults,Performance estimation,Practice}
}
</pre>

## Abstract

Research has demonstrated that a self-controlled KR schedule is advantageous for motor learning; however, the usefulness of a self-controlled KR context in older adults remains unknown. To address this gap in knowledge, we examined whether (1) the learning benefits of a self-controlled KR schedule are modulated by the age of the learner; (2) practicing in a self-controlled KR context concurrently strengthens the learner’s error detection mechanism, and (3) the KR strategy during acquisition changes as a function of practice trials completed and age. As a function of age, participants were quasirandomly assigned to either the self-control or yoked group resulting in four experimental groups (Self-Young, Yoked-Young, Self-Old, and Yoked-Old). The results revealed the Self-Young group: (1) demonstrated superior retention performance than all other groups (*p* < .05); (2) was more accurate in estimating motor performance than all other groups during retention (*p* < .05), and (3) self-reported a switch in their strategy for requesting KR during acquisition based on the number of practice trials completed. Collectively, our findings suggest that older adults do not demonstrate the same learning benefits of a self-controlled KR context as younger adults which may be attributed to differences in KR strategies.

### 2023-07-13 papers/2010-14/2013_bajema_ebr.qmd
init

---
title: "Pause time alters the preparation of two-component movements"
type: "article"
author: "Bajema MC., MacKinnon CD., Carter MJ., Kennefick M., Perlmutter S., & Carlsen AN."
year: "2013"
publication: "Experimental Brain Research"
pdf: ""
doi: "https://doi.org/10.1007/s00221-013-3670-6"
github: ""
materials: ""
#supplementary: ""
preprint: ""
toc: false
---

## Citation

### APA 7th

> Bajema, M. C., MacKinnon, C. D., Carter, M. J., Kennefick, M., Perlmutter, S., & Carlsen, A. N. (2013). Pause time alters the preparation of two-component movements. *Experimental Brain Research*, 231(1), 85–96. https://doi.org/10.1007/s00221-013-3670-6

### Bibtex

<pre>
@article{,
  title = {Pause Time Alters the Preparation of Two-Component Movements},
  author = {Bajema, Michael C. and MacKinnon, Colum D. and Carter, Michael J. and Kennefick, Michael and Perlmutter, Sam and Carlsen, Anthony N.},
  date = {2013-11-01},
  journaltitle = {Experimental Brain Research},
  shortjournal = {Exp Brain Res},
  volume = {231},
  number = {1},
  pages = {85--96},
  issn = {1432-1106},
  doi = {10.1007/s00221-013-3670-6},
  url = {https://doi.org/10.1007/s00221-013-3670-6},
  urldate = {2023-07-13},
  langid = {english},
  keywords = {Aiming,Complexity,Movement planning,Pause time,Startle}
}
</pre>

## Abstract

Targeted reciprocal aiming movements are pervasive in everyday life, but it is unclear how the timing parameters between task elements affect the preparation of these movements. This study used a loud (124 dB) startling acoustic stimulus (SAS) to probe how changes in the pause time between the outward and return components of a reciprocal aiming task affected the preparatory state of the motor system. Participants performed a visually guided wrist extension–flexion task to a target located at 20° from the start position and were instructed to pause the movement within the wrist extension target zone for either 50, 200, or 500 ms. A SAS was presented during 25 % of trials before either the onset of the wrist extension (out) or flexion (return) components of the task to determine how motor preparation was affected by task requirements. Results showed that the presentation of a SAS prior to the initial outward movement led to significantly earlier onsets of both the outward and return components (*p* < .05), indicating that the pause time in the planned action was pre-planned. For the longer (200, 500 ms) pause-time conditions, a SAS delivered prior to returning from the target region triggered the return portion of the movement early. These findings suggest that the shortest pause-time movement (50 ms) was preplanned as a single action, whereas for reciprocal movements with longer pause times at least the initial part of the movement and the timing of the pause were preplanned and integrated, while the return portion was more independent.

### 2023-07-13 papers/2010-14/2013_patterson_hms.qmd
init

---
title: "Self-controlled KR schedules: Does repetition order matter?"
type: "article"
author: "Patterson JT., Carter MJ., & Hansen S."
year: "2013"
publication: "Human Movement Science"
pdf: ""
doi: "https://doi.org/10.1016/j.humov.2013.03.005"
github: ""
materials: ""
#supplementary: ""
preprint: ""
toc: false
---

## Citation

### APA 7th

> Patterson, J. T., Carter, M. J., & Hansen, S. (2013). Self-controlled KR schedules: Does repetition order matter? *Human Movement Science*, 32(4), 567–579. https://doi.org/10.1016/j.humov.2013.03.005

### Bibtex

<pre>
@article{,
  title = {Self-Controlled {{KR}} Schedules: {{Does}} Repetition Order Matter?},
  shorttitle = {Self-Controlled {{KR}} Schedules},
  author = {Patterson, Jae T. and Carter, Michael J. and Hansen, Steve},
  date = {2013-08-01},
  journaltitle = {Human Movement Science},
  shortjournal = {Human Movement Science},
  volume = {32},
  number = {4},
  pages = {567--579},
  issn = {0167-9457},
  doi = {10.1016/j.humov.2013.03.005},
  url = {https://www.sciencedirect.com/science/article/pii/S0167945713000456},
  urldate = {2023-07-13},
  langid = {english},
  keywords = {2330,2340,2343,Feedback,Knowledge of results,Learning,Practice schedule,Self-control}
}
</pre>

## Abstract

The impact of an experimenter-defined repetition schedule on the utility of a self-controlled KR context during motor skill acquisition was examined. Participants were required to learn three novel spatial-temporal tasks in either a random or blocked repetition schedule with or without the opportunity to control their KR. Results from the retention period showed that participants provided control over their KR schedule in a random repetition schedule demonstrated superior learning. However, performance measures from the transfer test showed that, independent of repetition schedule, learners provided the opportunity to control their KR schedule demonstrated superior transfer performance compared to their yoked counterparts. The dissociated impact of repetition schedule and self-controlled KR schedules on retention and transfer is discussed.

### 2023-07-13 papers/2010-14/2014_carter_frontpsychol.qmd
init

---
title: "Self-controlled feedback is effective if it is based on the learner’s performance: a replication and extension of Chiviacowsky and Wulf (2005)"
type: "article"
author: "Carter MJ., Carlsen AN., & Ste-Marie DM."
year: "2014"
publication: "Frontiers in Psychology"
pdf: ""
doi: "https://doi.org/10.3389/fpsyg.2014.01325"
github: ""
materials: ""
#supplementary: ""
preprint: ""
toc: false
---

## Citation

### APA 7th

> Carter, M. J., Carlsen, A. N., & Ste-Marie, D. M. (2014). Self-controlled feedback is effective if it is based on the learner’s performance: A replication and extension of Chiviacowsky and Wulf (2005). *Frontiers in Psychology*, 5. https://doi.org/10.3389/fpsyg.2014.01325

### Bibtex

<pre>
@article{,
  title = {Self-Controlled Feedback Is Effective If It Is Based on the Learner’s Performance: {{A}} Replication and Extension of {{Chiviacowsky}} and {{Wulf}} (2005)},
  shorttitle = {Self-Controlled Feedback Is Effective If It Is Based on the Learner’s Performance},
  author = {Carter, Michael J. and Carlsen, Anthony N. and Ste-Marie, Diane M.},
  date = {2014},
  journaltitle = {Frontiers in Psychology},
  volume = {5},
  issn = {1664-1078},
  doi = {10.3389/fpsyg.2014.01325},
  url = {https://www.frontiersin.org/articles/10.3389/fpsyg.2014.01325},
  urldate = {2023-07-13}
}
</pre>

## Abstract

The learning advantages of self-controlled feedback schedules compared to yoked schedules have been attributed to motivational influences and/or information processing activities with many researchers adopting the motivational perspective in recent years. Chiviacowsky and Wulf (2005) found that feedback decisions made before (Self-Before) or after a trial (Self-After) resulted in similar retention performance, but superior transfer performance resulted when the decision to receive feedback occurred after a trial. They suggested that the superior skill transfer of the Self-After group likely emerged from information processing activities such as error estimation. However, the lack of yoked groups and a measure of error estimation in their experimental design prevents conclusions being made regarding the underlying mechanisms of why self-controlled feedback schedules optimize learning. Here, we revisited Chiviacowsky and Wulf’s (2005) design to investigate the learning benefits of self-controlled feedback schedules. We replicated their Self-Before and Self-After groups, but added a Self-Both group that was able to request feedback before a trial, but could then change or stay with their original choice after the trial. Importantly, yoked groups were included for the three self-controlled groups to address the previously stated methodological limitation and error estimations were included to examine whether self-controlling feedback facilitates a more accurate error detection and correction mechanism. The Self-After and Self-Before groups demonstrated similar accuracy in physical performance and error estimation scores in retention and transfer, and both groups were significantly more accurate than the Self-Before group and their respective Yoked groups (*p*’s < 0.05). Further, the Self-Before group was not significantly different from their yoked counterparts (*p*’s > 0.05). We suggest these findings further indicate that informational factors associated with the processing of feedback for the development of one’s error detection and correction mechanism, rather than motivational processes are more critical for why self-controlled feedback schedules optimize motor learning.

### 2023-07-13 papers/2010-14/2014_maslovat_neurolet.qmd
init

---
title: "Startle neural activity is additive with normal cortical initiation-related activation"
type: "article"
author: "Maslovat D., Carter MJ., Kennefick M., & Carlsen AN."
year: "2014"
publication: "Neuroscience Letters"
pdf: ""
doi: "https://doi.org/10.1016/j.neulet.2013.11.009"
github: ""
materials: ""
#supplementary: ""
preprint: ""
toc: false
---

## Citation

### APA 7th

> Maslovat, D., Carter, M. J., Kennefick, M., & Carlsen, A. N. (2014). Startle neural activity is additive with normal cortical initiation-related activation. *Neuroscience Letters*, 558, 164–168. https://doi.org/10.1016/j.neulet.2013.11.009

### Bibtex

<pre>
@article{,
  title = {Startle Neural Activity Is Additive with Normal Cortical Initiation-Related Activation},
  author = {Maslovat, Dana and Carter, Michael J. and Kennefick, Michael and Carlsen, Anthony N.},
  date = {2014-01-13},
  journaltitle = {Neuroscience Letters},
  shortjournal = {Neuroscience Letters},
  volume = {558},
  pages = {164--168},
  issn = {0304-3940},
  doi = {10.1016/j.neulet.2013.11.009},
  url = {https://www.sciencedirect.com/science/article/pii/S0304394013010094},
  urldate = {2023-07-13},
  langid = {english},
  keywords = {Additive model,Initiation,Motor preparation,Neural activation,Startle}
}
</pre>

## Abstract

The current study examined the process of response initiation in a simple reaction time (RT) task using a startling acoustic stimulus (SAS), which has been shown to trigger a prepared movement through an involuntary initiation pathway. The SAS was presented within the RT interval (concurrent with, and 25, 50, 75, 100, and 125 ms following the “go” signal), with the observed response latency used to examine the relative contributions of voluntary and involuntary activation to response initiation. Our results clearly indicate that both voluntary and startle-related initiation activation jointly contribute to the observed RT. The data support a model in which startle-related neural activity is additive with voluntary cortical initiation-related activation. This result also provides indirect support for the hypothesis that both voluntary and SAS-related involuntary activation involve a similar process of response output.

### 2023-07-13 papers/2015-19/2015_carter_jnp.qmd
init

---
title: "Anodal transcranial direct current stimulation applied over the supplementary motor area delays spontaneous antiphase-to-in-phase transitions"
type: "article"
author: "Carter MJ., Maslovat D., & Carlsen AN."
year: "2015"
publication: "Journal of Neurophysiology"
pdf: ""
doi: "https://doi.org/10.1152/jn.00662.2014"
github: ""
materials: ""
#supplementary: ""
preprint: ""
toc: false
---

## Citation

### APA 7th

> Carter, M. J., Maslovat, D., & Carlsen, A. N. (2015). Anodal transcranial direct current stimulation applied over the supplementary motor area delays spontaneous antiphase-to-in-phase transitions. *Journal of Neurophysiology*, 113(3), 780–785. https://doi.org/10.1152/jn.00662.2014

### Bibtex

<pre>
@article{,
  title = {Anodal Transcranial Direct Current Stimulation Applied over the Supplementary Motor Area Delays Spontaneous Antiphase-to-in-Phase Transitions},
  author = {Carter, Michael J. and Maslovat, Dana and Carlsen, Anthony N.},
  date = {2015-02},
  journaltitle = {Journal of Neurophysiology},
  volume = {113},
  number = {3},
  pages = {780--785},
  publisher = {{American Physiological Society}},
  issn = {0022-3077},
  doi = {10.1152/jn.00662.2014},
  url = {https://journals.physiology.org/doi/full/10.1152/jn.00662.2014},
  urldate = {2023-07-13},
  keywords = {bimanual coordination,motor control,neurostimulation,phase transition}
}
</pre>

## Abstract

Coordinated bimanual oscillatory movements often involve one of two intrinsically stable phasing relationships characterized as in-phase (symmetrical) or antiphase (asymmetrical). The in-phase mode is typically more stable than antiphase, and if movement frequency is increasing during antiphase movements, a spontaneous transition to the in-phase pattern occurs. There is converging neurophysiological evidence that the supplementary motor area (SMA) plays a critical role in the successful performance of these patterns, especially during antiphase movements. We investigated whether modulating the excitability of the SMA via offline transcranial direct current stimulation (tDCS) would delay the onset of anti-to-in-phase transitions. Participants completed two sessions (separated by ∼48 h), each consisting of a pre- and post-tDCS block in which they performed metronome-paced trials of rhythmic in- and antiphase bimanual supination-pronation movements as target oscillation frequency was systematically increased. Anodal or cathodal tDCS was applied over the SMA between the pre- and post-tDCS blocks in each session. Following anodal tDCS, participants performed the antiphase pattern with increased accuracy and stability and were able to maintain the coordination pattern at a higher oscillation frequency. Antiphase performance was unchanged following cathodal tDCS, and neither tDCS polarity affected the in-phase mode. Our findings suggest increased SMA excitability induced by anodal tDCS can improve antiphase performance and adds to the accumulating evidence of the pivotal role of the SMA in interlimb coordination.

### 2023-07-13 papers/2015-19/2015_maslovat_ebr.qmd
init

---
title: "Reduced motor preparation during dual-task performance: Evidence from startle"
type: "article"
author: "Maslovat D., Drummond NM., Carter MJ., & Carlsen AN."
year: "2015"
publication: "Experimental Brain Research"
pdf: ""
doi: "https://doi.org/10.1007/s00221-015-4340-7"
github: ""
materials: ""
#supplementary: ""
preprint: ""
toc: false
---

## Citation

### APA 7th

> Maslovat, D., Drummond, N. M., Carter, M. J., & Carlsen, A. N. (2015). Reduced motor preparation during dual-task performance: Evidence from startle. *Experimental Brain Research*, 233(9), 2673–2683. https://doi.org/10.1007/s00221-015-4340-7

### Bibtex

<pre>
@article{,
  title = {Reduced Motor Preparation during Dual-Task Performance: {{Evidence}} from Startle},
  shorttitle = {Reduced Motor Preparation during Dual-Task Performance},
  author = {Maslovat, Dana and Drummond, Neil M. and Carter, Michael J. and Carlsen, Anthony N.},
  date = {2015-09-01},
  journaltitle = {Experimental Brain Research},
  shortjournal = {Exp Brain Res},
  volume = {233},
  number = {9},
  pages = {2673--2683},
  issn = {1432-1106},
  doi = {10.1007/s00221-015-4340-7},
  url = {https://doi.org/10.1007/s00221-015-4340-7},
  urldate = {2023-07-13},
  langid = {english},
  keywords = {Activation,Attention,Dual-task,Preparation,Probe reaction time,Startle}
}
</pre>

## Abstract

Previous studies have used a secondary probe reaction time (RT) task to assess attentional demands of a primary task. The current study used a startling acoustic stimulus (SAS) in a probe RT paradigm to test the hypothesis that attentional resources would be directly related to limitations in response preparation. Participants performed an easy or difficult version of a continuous primary task that was either primarily motor in nature (pursuit tracking) or cognitive (counting backward). Concurrently, participants responded to an auditory cue as fast as possible by performing a wrist extension secondary movement. On selected trials, the auditory cue was replaced with a SAS (120 dB), which is thought to involuntarily trigger a prepared response and thus bypass any response initiation bottleneck that may be present when trying to perform two movements. Although startle trials were performed at a shorter latency, both non-startle and startle probe trials resulted in a delayed RT, as compared to single-task trials, consistent with reduced preparation of the secondary task. In addition, analysis of SAS trial RT when a startle indicator was present versus absent provided evidence that the secondary task was at a lowered state of preparation when engaged in the cognitive primary task as compared to a motor primary task, suggesting a facilitative effect on preparatory activation when both the primary and secondary tasks are motoric in nature.

### 2023-07-13 papers/2015-19/2015_maslovat_neurolet.qmd
init

---
title: "Startle activation is additive with voluntary cortical activation irrespective of stimulus modality"
type: "article"
author: "Maslovat D., Drummond NM., Carter MJ., & Carlsen AN."
year: "2015"
publication: "Neuroscience Letters"
pdf: ""
doi: "https://doi.org/10.1016/j.neulet.2015.08.053"
github: ""
materials: ""
#supplementary: ""
preprint: ""
toc: false
---

## Citation

### APA 7th

> Maslovat, D., Drummond, N. M., Carter, M. J., & Carlsen, A. N. (2015). Startle activation is additive with voluntary cortical activation irrespective of stimulus modality. *Neuroscience Letters*, 606, 151–155. https://doi.org/10.1016/j.neulet.2015.08.053

### Bibtex

<pre>
@article{,
  title = {Startle Activation Is Additive with Voluntary Cortical Activation Irrespective of Stimulus Modality},
  author = {Maslovat, Dana and Drummond, Neil M. and Carter, Michael J. and Carlsen, Anthony N.},
  date = {2015-10-08},
  journaltitle = {Neuroscience Letters},
  shortjournal = {Neuroscience Letters},
  volume = {606},
  pages = {151--155},
  issn = {0304-3940},
  doi = {10.1016/j.neulet.2015.08.053},
  url = {https://www.sciencedirect.com/science/article/pii/S0304394015301233},
  urldate = {2023-07-13},
  langid = {english},
  keywords = {Additive model,ECR,FCR,Initiation,IS,Motor preparation,Neural activation,SAS,SCM,Startle}
}
</pre>

## Abstract

When a startling acoustic stimulus (SAS) is presented during a simple reaction time (RT) task, it can trigger the prepared response through an involuntary initiation pathway. Previous research modelling the effects of presenting a SAS at various intervals following a non-startling auditory imperative signal (IS) suggested that involuntary initiation-related neural activation is additive with the voluntary initiation processes. The current study tested the predictions of this additive model when the SAS and IS are of different modalities by using a visual rather than auditory go-signal. Because voluntary RT latencies are delayed for visual stimuli compared to acoustic stimuli, it was hypothesised that the time course of additive activation would be similarly delayed. Participants performed 150 RT trials requiring a targeted 20° wrist extension task with a SAS presented 0–125 ms following a visual go-signal. Results were not different to those predicted by an additive model (*p* = 0.979), yet were significantly different to those predicted by a horse-race model (*p* = 0.037), indicating a joint contribution of voluntary and involuntary activation, even when the IS and SAS are of different modalities. Furthermore, the results indicated that voluntary RT differences due to stimulus modality are attributable to processes that occur prior to the increase in initiation-related activation.

### 2023-07-13 papers/2015-19/2016_carter_hms.qmd
init

---
title: "Judgments of learning are significantly higher following feedback on relatively good versus relatively poor trials despite no actual learning differences"
type: "article"
author: "Carter MJ."
year: "2016"
publication: "Human Movement Science"
pdf: ""
doi: "https://doi.org/10.1016/j.humov.2015.11.006"
github: ""
materials: ""
#supplementary: ""
preprint: ""
toc: false
---

## Citation

### APA 7th

> Carter, M. J., Smith, V., & Ste-Marie, D. M. (2016). Judgments of learning are significantly higher following feedback on relatively good versus relatively poor trials despite no actual learning differences. *Human Movement Science*, 45, 63–70. https://doi.org/10.1016/j.humov.2015.11.006

### Bibtex

<pre>
@article{,
  title = {Judgments of Learning Are Significantly Higher Following Feedback on Relatively Good versus Relatively Poor Trials despite No Actual Learning Differences},
  author = {Carter, Michael J. and Smith, Victoria and Ste-Marie, Diane M.},
  date = {2016-02-01},
  journaltitle = {Human Movement Science},
  shortjournal = {Human Movement Science},
  volume = {45},
  pages = {63--70},
  issn = {0167-9457},
  doi = {10.1016/j.humov.2015.11.006},
  url = {https://www.sciencedirect.com/science/article/pii/S0167945715300567},
  urldate = {2023-07-13},
  langid = {english},
  keywords = {Knowledge of results,Metacognition,Motor learning,Skill acquisition}
}
</pre>

## Abstract

Studies have consistently shown that prospective metacognitive judgments of learning are often inaccurate because humans mistakenly interpret current performance levels as valid indices of learning. These metacognitive discrepancies are strongly related to conditions of practice. Here, we examined how the type of feedback (after good versus poor trials) received during practice and awareness (aware versus unaware) of this manipulation affected judgments of learning and actual learning. After each six-trial block, participants received feedback on their three best trials or three worst trials and half of the participants were made explicitly aware of the type of feedback they received while the other half were unaware. Judgments of learning were made at the end of each six-trial block and before the 24-h retention test. Results indicated no motor performance differences between groups in practice or retention; however, receiving feedback on relatively good compared to relatively poor trials resulted in significantly higher judgments of learning in practice and retention, irrespective of awareness. These results suggest that KR on relatively good versus relatively poor trials can have dissociable effects on judgments of learning in the absence of actual learning differences, even when participants are made aware of their feedback manipulation.

### 2023-07-13 papers/2015-19/2016_carter_jmld.qmd
init

---
title: "Motor skill retention is modulated by strategy choice during self-controlled knowledge of results schedules "
type: "article"
author: "Carter MJ., Rathwell S., & Ste-Marie DM."
year: "2016"
publication: "Journal of Motor Learning and Development"
pdf: ""
doi: "https://doi.org/10.1123/jmld.2015-0023"
github: ""
materials: ""
#supplementary: ""
preprint: ""
toc: false
---

## Citation

### APA 7th

> Carter, M., Rathwell, S., & Ste-Marie, D. (2016). Motor skill retention is modulated by strategy choice during self-controlled knowledge of results schedules. *Journal of Motor Learning and Development*, 4(1), 100–115. https://doi.org/10.1123/jmld.2015-0023

### Bibtex

<pre>
@article{,
  title = {Motor Skill Retention Is Modulated by Strategy Choice during Self-Controlled Knowledge of Results Schedules},
  author = {Carter, Michael and Rathwell, Scott and Ste-Marie, Diane},
  date = {2016-06-01},
  journaltitle = {Journal of Motor Learning and Development},
  volume = {4},
  number = {1},
  pages = {100--115},
  publisher = {{Human Kinetics, Inc.}},
  issn = {2325-3193, 2325-3215},
  doi = {10.1123/jmld.2015-0023},
  url = {https://journals.humankinetics.com/view/journals/jmld/4/1/article-p100.xml},
  urldate = {2023-07-13},
  langid = {american}
}
</pre>

## Abstract

Investigations into the strategies that are used by participants when they control their knowledge of results (KR) schedule during practice have predominantly relied on multiple-choice questionnaires. More recently, open-ended questions have been used to allow participants to produce their own descriptions rather than selecting a strategy from a predetermined list. This approach has in fact generated new information about the cognitive strategies used by learners to request KR during practice (e.g., Laughlin et al., 2015). Consequently, we examined strategy use in self-controlled KR learning situations using open-ended questions at two different time points during practice. An inductive thematic content analysis revealed five themes that represented participants’ unique strategies for requesting KR. This analysis identified two dominant KR strategies: “establish a baseline understanding” in the first half of practice and “confirm a perceived good trial” in the second half of practice. Both strategies were associated with superior retention compared with a yoked group, a group that was unable to engage in KR request strategies because KR was imposed rather than chosen. Our results indicate that the learning advantages of self-controlled KR schedules over yoked schedules may not only depend on what strategy is used, but also when it is used.

### 2023-07-13 papers/2015-19/2016_martini_pse.qmd
init

---
title: "Development and validation of the Movement Imagery Questionnaire for Children (MIQ-C)"
type: "article"
author: "Martini R., Carter MJ., Yoxon E., Cumming J., & Ste-Marie DM."
year: "2016"
publication: "Psychology of Sport and Exercise"
pdf: ""
doi: "https://doi.org/10.1016/j.psychsport.2015.08.008"
github: ""
materials: ""
#supplementary: ""
preprint: ""
toc: false
---

## Citation

### APA 7th

> Martini, R., Carter, M. J., Yoxon, E., Cumming, J., & Ste-Marie, D. M. (2016). Development and validation of the Movement Imagery Questionnaire for Children (MIQ-C). *Psychology of Sport and Exercise*, 22, 190–201. https://doi.org/10.1016/j.psychsport.2015.08.008

### Bibtex

<pre>
@article{,
  title = {Development and Validation of the {{Movement Imagery Questionnaire}} for {{Children}} ({{MIQ-C}})},
  author = {Martini, Rose and Carter, Michael J. and Yoxon, Emma and Cumming, Jennifer and Ste-Marie, Diane M.},
  date = {2016-01-01},
  journaltitle = {Psychology of Sport and Exercise},
  shortjournal = {Psychology of Sport and Exercise},
  volume = {22},
  pages = {190--201},
  issn = {1469-0292},
  doi = {10.1016/j.psychsport.2015.08.008},
  url = {https://www.sciencedirect.com/science/article/pii/S1469029215300054},
  urldate = {2023-07-13},
  langid = {english},
  keywords = {Ease of imaging,Imagery ability,Scale development}
}
</pre>

## Abstract

The ability to perform movement imagery has been shown to influence motor performance and learning in sports and rehabilitation. Self-report questionnaires have been developed to assess movement imagery ability in adults, such as the Movement Imagery Questionnaire 3 (MIQ-3); however, there is a dearth of developmentally appropriate measures for use with children. To address this gap, the focus of this research was to develop an imagery ability questionnaire for children. This process involved adaptation of the MIQ-3 via: i) cognitive interviewing with twenty children, ii) validation with 206 children by examining its factor structure via multitrait-multi method confirmatory factor analysis, and iii) examination of test-retest reliability with 23 children. The findings of Study 1 led to changes to the wording of the questionnaire and modifications of the instructions to successfully adapt the MIQ-3 for children aged 7–12 years. The validation undertaken in Study 2 found that a correlated-traits correlated-uniqueness model provided the best fit to the data. Finally, test-retest reliabilities varied from fair (for external visual imagery) to substantial (for kinesthetic imagery). With respect to ease of imaging, no significant gender or age-group differences were noted. However, significant difference were found among the three imagery modalities (*p* < .001), with external visual imagery rated as easiest to image and kinesthetic imagery rated as the most difficult. Taken together, findings support the use of the MIQ-C for examining movement imagery ability with children.

### 2023-07-13 papers/2015-19/2016_patterson_pms.qmd
init

---
title: "Measuring investment in learning: Can electrocardiogram provide an indication of cognitive effort during learning?"
type: "article"
author: "Patterson JT., Hart A., Hansen S., Carter MJ., & Ditor D."
year: "2016"
publication: "Perceptual and Motor Skills"
pdf: ""
doi: "https://doi.org/10.1177/0031512516633348"
github: ""
materials: ""
#supplementary: ""
preprint: ""
toc: false
---

## Citation

### APA 7th

> Patterson, J. T., Hart, A., Hansen, S., Carter, M. J., & Ditor, D. (2016). Measuring investment in learning: Can electrocardiogram provide an indication of cognitive effort during learning? *Perceptual and Motor Skills*, 122(2), 375–394. https://doi.org/10.1177/0031512516633348

### Bibtex

<pre>
@article{,
  title = {Measuring Investment in Learning: {{Can}} Electrocardiogram Provide an Indication of Cognitive Effort during Learning?},
  shorttitle = {Measuring {{Investment}} in {{Learning}}},
  author = {Patterson, Jae T. and Hart, Amanda and Hansen, Steve and Carter, Michael J. and Ditor, David},
  date = {2016-04-01},
  journaltitle = {Perceptual and Motor Skills},
  shortjournal = {Percept Mot Skills},
  volume = {122},
  number = {2},
  pages = {375--394},
  publisher = {{SAGE Publications Inc}},
  issn = {0031-5125},
  doi = {10.1177/0031512516633348},
  url = {https://doi.org/10.1177/0031512516633348},
  urldate = {2023-07-13},
  langid = {english}
}
</pre>

## Abstract

Heart rate variability (i.e., low frequency:high frequency ratio) was measured to differentiate invested cognitive effort during the acquisition and retention of a novel task. Participants (12 male, *M* = 25.1 year, *SD* = 3.6; 12 female, *M* = 22.8 year, *SD* = 1.1) were required to produce Braille equivalents of English letter primes on a standardized keyboard in proactive or retroactive conditions (groups, each *n* = 12). The correct Braille response was either provided before (i.e., proactively) or after (i.e., retroactively) the participant’s response. During acquisition, participants in the proactive group demonstrated shorter study time, greater recall success, and reported lower cognitive investment. Participants in the proactive and retroactive groups did not statistically differ in heart rate variability. For retention, the retroactive group showed greater recall success, lower perceived cognitive effort investment, and lower heart rate variability. The results highlight the usefulness of heart rate variability in discriminating the cognitive effort invested for a recently acquired skill.

### 2023-07-13 papers/2015-19/2016_stemarie_jss.qmd
init

---
title: "Self-controlled learning benefits: exploring contributions of self-efficacy and intrinsic motivation via path analysis"
type: "article"
author: "Ste-Marie DM., Carter MJ., Law B., Vertes K., & Smith V."
year: "2016"
publication: "Journal of Sports Sciences"
pdf: ""
doi: "https://doi.org/10.1080/02640414.2015.1130236"
github: ""
materials: ""
#supplementary: ""
preprint: ""
toc: false
---

## Citation

### APA 7th

> Ste-Marie, D. M., Carter, M. J., Law, B., Vertes, K., & Smith, V. (2016). Self-controlled learning benefits: Exploring contributions of self-efficacy and intrinsic motivation via path analysis. *Journal of Sports Sciences*, 34(17), 1650–1656. https://doi.org/10.1080/02640414.2015.1130236

### Bibtex

<pre>
@article{,
  title = {Self-Controlled Learning Benefits: {{Exploring}} Contributions of Self-Efficacy and Intrinsic Motivation via Path Analysis},
  shorttitle = {Self-Controlled Learning Benefits},
  author = {Ste-Marie, Diane M. and Carter, Michael J. and Law, Barbi and Vertes, Kelly and Smith, Victoria},
  date = {2016-09-01},
  journaltitle = {Journal of Sports Sciences},
  volume = {34},
  number = {17},
  eprint = {26707002},
  eprinttype = {pmid},
  pages = {1650--1656},
  publisher = {{Routledge}},
  issn = {0264-0414},
  doi = {10.1080/02640414.2015.1130236},
  url = {https://doi.org/10.1080/02640414.2015.1130236},
  urldate = {2023-07-13},
  keywords = {knowledge of performance,learner-controlled,Motor skill learning,video feedback}
}
</pre>

## Abstract

Research has shown learning advantages for self-controlled practice contexts relative to yoked (i.e., experimenter-imposed) contexts; yet, explanations for this phenomenon remain relatively untested. We examined, via path analysis, whether self-efficacy and intrinsic motivation are important constructs for explaining self-controlled learning benefits. The path model was created using theory-based and empirically supported relationships to examine causal links between these psychological constructs and physical performance. We hypothesised that self-efficacy and intrinsic motivation would have greater predictive power for learning under self-controlled compared to yoked conditions. Participants learned double-mini trampoline progressions, and measures of physical performance, self-efficacy and intrinsic motivation were collected over two practice days and a delayed retention day. The self-controlled group (*M* = 2.04, *SD* = .98) completed significantly more skill progressions in retention than their yoked counterparts (*M* = 1.3, *SD* = .65). The path model displayed adequate fit, and similar significant path coefficients were found for both groups wherein each variable was predominantly predicted by its preceding time point (e.g., self-efficacy time 1 predicts self-efficacy time 2). Interestingly, the model was not moderated by group; thus, failing to support the hypothesis that self-efficacy and intrinsic motivation have greater predictive power for learning under self-controlled relative to yoked conditions.

### 2023-07-13 papers/2015-19/2017_carter_brainstim.qmd
init

---
title: "Intentional switches between coordination patterns are faster following anodal-tDCS applied over the supplementary motor area"
type: "article"
author: "Carter MJ., & Maslovat D., & Carlsen AN."
year: "2017"
publication: "Brain Stimulation"
pdf: ""
doi: "https://doi.org/10.1016/j.brs.2016.11.002"
github: ""
materials: ""
#supplementary: ""
preprint: ""
toc: false
---

## Citation

### APA 7th

> Carter, M. J., Maslovat, D., & Carlsen, A. N. (2017). Intentional switches between coordination patterns are faster following anodal-tDCS applied over the supplementary motor area. *Brain Stimulation*, 10(1), 162–164. https://doi.org/10.1016/j.brs.2016.11.002

### Bibtex

<pre>
@article{,
  title = {Intentional Switches between Coordination Patterns Are Faster Following Anodal-{{tDCS}} Applied over the Supplementary Motor Area},
  author = {Carter, Michael J. and Maslovat, Dana and Carlsen, Anthony N.},
  date = {2017-01-01},
  journaltitle = {Brain Stimulation},
  shortjournal = {Brain Stimulation},
  volume = {10},
  number = {1},
  pages = {162--164},
  issn = {1935-861X},
  doi = {10.1016/j.brs.2016.11.002},
  url = {https://www.sciencedirect.com/science/article/pii/S1935861X1630300X},
  urldate = {2023-07-13},
  langid = {english}
}
</pre>

### 2023-07-13 papers/2015-19/2017_carter_pbr.qmd
init

---
title: "Not all choices are created equal: Task-relevant choices enhance motor learning compared to task-irrelevant choices"
type: "article"
author: "Carter MJ. & Ste-Marie DM."
year: "2017"
publication: "Psychonomic Bulletin & Review"
pdf: ""
doi: "https://doi.org/10.3758/s13423-017-1250-7"
github: ""
materials: ""
#supplementary: ""
preprint: ""
toc: false
---

## Citation

### APA 7th

> Carter, M. J., & Ste-Marie, D. M. (2017). Not all choices are created equal: Task-relevant choices enhance motor learning compared to task-irrelevant choices. *Psychonomic Bulletin & Review*, 24(6), 1879–1888. https://doi.org/10.3758/s13423-017-1250-7

### Bibtex

<pre>
@article{,
  title = {Not All Choices Are Created Equal: {{Task-relevant}} Choices Enhance Motor Learning Compared to Task-Irrelevant Choices},
  shorttitle = {Not All Choices Are Created Equal},
  author = {Carter, Michael J. and Ste-Marie, Diane M.},
  date = {2017-12-01},
  journaltitle = {Psychonomic Bulletin \& Review},
  shortjournal = {Psychon Bull Rev},
  volume = {24},
  number = {6},
  pages = {1879--1888},
  issn = {1531-5320},
  doi = {10.3758/s13423-017-1250-7},
  url = {https://doi.org/10.3758/s13423-017-1250-7},
  urldate = {2023-07-13},
  langid = {english},
  keywords = {Autonomy,Competence,Error estimation,Information processing,Motor learning}
}
</pre>

## Abstract

Lewthwaite et al. (2015) reported that the learning benefits of exercising choice (i.e., their self-controlled condition) are not restricted to task-relevant features (e.g., feedback). They found that choosing one’s golf ball color (Exp. 1) or choosing which of two tasks to perform at a later time plus which of two artworks to hang (Exp. 2) resulted in better retention than did being denied these same choices (i.e., yoked condition). The researchers concluded that the learning benefits derived from choice, whether irrelevant or relevant to the to-be-learned task, are predominantly motivational because choice is intrinsically rewarding and satisfies basic psychological needs. However, the absence of a group that made task-relevant choices and the lack of psychological measures significantly weakened their conclusions. Here, we investigated how task-relevant and task-irrelevant choices affect motor-skill learning. Participants practiced a spatiotemporal motor task in either a task-relevant group (choice over feedback schedule), a task-irrelevant group (choice over the color of an arm-wrap plus game selection), or a no-choice group. The results showed significantly greater learning in the task-relevant group than in both the task-irrelevant and no-choice groups, who did not differ significantly. Critically, these learning differences were not attributed to differences in perceptions of competence or autonomy, but instead to superior error-estimation abilities. These results challenge the perspective that motivational influences are the root cause of self-controlled learning advantages. Instead, the findings add to the growing evidence highlighting that the informational value gained from task-relevant choices makes a greater relative contribution to these advantages than motivational influences.

### 2023-07-13 papers/2015-19/2017_carter_psycholres.qmd
init

---
title: "An interpolated activity during the knowledge-of-results delay interval eliminates the learning advantages of self-controlled feedback schedules"
type: "article"
author: "Carter MJ. & Ste-Marie DM."
year: "2017"
publication: "Psychological Research"
pdf: ""
doi: "https://doi.org/10.1007/s00426-016-0757-2"
github: ""
materials: ""
#supplementary: ""
preprint: ""
toc: false
---

## Citation

### APA 7th

> Carter, M. J., & Ste-Marie, D. M. (2017). An interpolated activity during the knowledge-of-results delay interval eliminates the learning advantages of self-controlled feedback schedules. *Psychological Research*, 81(2), 399–406. https://doi.org/10.1007/s00426-016-0757-2

### Bibtex

<pre>
@article{,
  title = {An Interpolated Activity during the Knowledge-of-Results Delay Interval Eliminates the Learning Advantages of Self-Controlled Feedback Schedules},
  author = {Carter, Michael J. and Ste-Marie, Diane M.},
  date = {2017-03-01},
  journaltitle = {Psychological Research},
  shortjournal = {Psychological Research},
  volume = {81},
  number = {2},
  pages = {399--406},
  issn = {1430-2772},
  doi = {10.1007/s00426-016-0757-2},
  url = {https://doi.org/10.1007/s00426-016-0757-2},
  urldate = {2023-07-13},
  langid = {english},
  keywords = {Interpolate Activity,Learning Benefit,Movement Completion,Performance Appraisal,Root Mean Square Error}
}
</pre>

## Abstract

The learning advantages of self-controlled knowledge-of-results (KR) schedules compared to yoked schedules have been linked to the optimization of the informational value of the KR received for the enhancement of one’s error-detection capabilities. This suggests that information-processing activities that occur after motor execution, but prior to receiving KR (i.e., the KR-delay interval) may underlie self-controlled KR learning advantages. The present experiment investigated whether self-controlled KR learning benefits would be eliminated if an interpolated activity was performed during the KR-delay interval. Participants practiced a waveform matching task that required two rapid elbow extension-flexion reversals in one of four groups using a factorial combination of choice (self-controlled, yoked) and KR-delay interval (empty, interpolated). The waveform had specific spatial and temporal constraints, and an overall movement time goal. The results indicated that the self-controlled + empty group had superior retention and transfer scores compared to all other groups. Moreover, the self-controlled + interpolated and yoked + interpolated groups did not differ significantly in retention and transfer; thus, the interpolated activity eliminated the typically found learning benefits of self-controlled KR. No significant differences were found between the two yoked groups. We suggest the interpolated activity interfered with information-processing activities specific to self-controlled KR conditions that occur during the KR-delay interval and that these activities are vital for reaping the associated learning benefits. These findings add to the growing evidence that challenge the motivational account of self-controlled KR learning advantages and instead highlights informational factors associated with the KR-delay interval as an important variable for motor learning under self-controlled KR schedules.

### 2023-07-13 papers/2015-19/2017_maslovat_jnp.qmd
init

---
title: "Response preparation and execution during intentional bimanual pattern switching"
type: "article"
author: "Maslovat D., Carter MJ., & Carlsen AN."
year: "2017"
publication: "Journal of Neurophysiology"
pdf: ""
doi: "https://doi.org/10.1152/jn.00323.2017"
github: ""
materials: ""
#supplementary: ""
preprint: ""
toc: false
---

## Citation

### APA 7th

> Maslovat, D., Carter, M. J., & Carlsen, A. N. (2017). Response preparation and execution during intentional bimanual pattern switching. *Journal of Neurophysiology*, 118(3), 1720–1731. https://doi.org/10.1152/jn.00323.2017

### Bibtex

<pre>
@article{,
  title = {Response Preparation and Execution during Intentional Bimanual Pattern Switching},
  author = {Maslovat, Dana and Carter, Michael J. and Carlsen, Anthony N.},
  date = {2017-09},
  journaltitle = {Journal of Neurophysiology},
  volume = {118},
  number = {3},
  pages = {1720--1731},
  publisher = {{American Physiological Society}},
  issn = {0022-3077},
  doi = {10.1152/jn.00323.2017},
  url = {https://journals.physiology.org/doi/full/10.1152/jn.00323.2017},
  urldate = {2023-07-13},
  keywords = {coordination dynamics,intentional switching,preparation,startle,transitions}
}
</pre>

## Abstract

During continuous bimanual coordination, in-phase (IP; 0° relative phase) and anti-phase (AP; 180° relative phase) patterns can be stably performed without practice. Paradigms in which participants are required to intentionally switch between these coordination patterns have been used to investigate the interaction between the performer’s intentions and intrinsic dynamics of the body’s preferred patterns. The current study examined the processes associated with switching preparation and execution through the use of a startling acoustic stimulus (SAS) as the switch stimulus. A SAS is known to involuntarily trigger preprogrammed responses at a shortened latency and, thus, can be used to probe advance preparation. Participants performed cyclical IP and AP bimanual elbow extension-flexion movements in which they were required to switch patterns in response to an auditory switch cue, which was either nonstartling (80 dB) or a SAS (120 dB). Results indicated that reaction time to the switch stimulus (i.e., switch onset) was significantly reduced on startle trials, indicative of advance preparation of the switch response. Similarly, switching time was reduced on startle trials, which was attributed to increased neural activation caused by the SAS. Switching time was also shorter for AP to IP trials, but only when the switching stimulus occurred at either the midpoint or reversal locations within the movement cycle, suggesting that the switch location may affect the intrinsic dynamics of the system.

### 2023-07-13 papers/2015-19/2018_carter_psycholres.qmd
init

---
title: "Anodal transcranial direct current stimulation over the primary motor cortex does not enhance the learning benefits of self-controlled feedback schedules"
type: "article"
author: "Carter MJ., Smith V., Carlsen AN., & Ste-Marie DM."
year: "2018"
publication: "Psychological Research"
pdf: ""
doi: "https://doi.org/10.1007/s00426-017-0846-x"
github: ""
materials: ""
#supplementary: ""
preprint: ""
toc: false
---

## Citation

### APA 7th

> Carter, M. J., Smith, V., Carlsen, A. N., & Ste-Marie, D. M. (2018). Anodal transcranial direct current stimulation over the primary motor cortex does not enhance the learning benefits of self-controlled feedback schedules. *Psychological Research*, 82(3), 496–506. https://doi.org/10.1007/s00426-017-0846-x

### Bibtex

<pre>
@article{,
  title = {Anodal Transcranial Direct Current Stimulation over the Primary Motor Cortex Does Not Enhance the Learning Benefits of Self-Controlled Feedback Schedules},
  author = {Carter, Michael J. and Smith, Victoria and Carlsen, Anthony N. and Ste-Marie, Diane M.},
  date = {2018-05-01},
  journaltitle = {Psychological Research},
  shortjournal = {Psychological Research},
  volume = {82},
  number = {3},
  pages = {496--506},
  issn = {1430-2772},
  doi = {10.1007/s00426-017-0846-x},
  url = {https://doi.org/10.1007/s00426-017-0846-x},
  urldate = {2023-07-13},
  langid = {english}
}
</pre>

## Abstract

A distinct learning advantage has been shown when participants control their knowledge of results (KR) scheduling during practice compared to when the same KR schedule is imposed on the learner without choice (i.e., yoked schedules). Although the learning advantages of self-controlled KR schedules are well-documented, the brain regions contributing to these advantages remain unknown. Identifying key brain regions would not only advance our theoretical understanding of the mechanisms underlying self-controlled learning advantages, but would also highlight regions that could be targeted in more applied settings to boost the already beneficial effects of self-controlled KR schedules. Here, we investigated whether applying anodal transcranial direct current stimulation (tDCS) to the primary motor cortex (M1) would enhance the typically found benefits of learning a novel motor skill with a self-controlled KR schedule. Participants practiced a spatiotemporal task in one of four groups using a factorial combination of KR schedule (self-controlled vs. yoked) and tDCS (anodal vs. sham). Testing occurred on two consecutive days with spatial and temporal accuracy measured on both days and learning was assessed using 24-h retention and transfer tests without KR. All groups improved their performance in practice and a significant effect for practicing with a self-controlled KR schedule compared to a yoked schedule was found for temporal accuracy in transfer, but a similar advantage was not evident in retention. There were no significant differences as a function of KR schedule or tDCS for spatial accuracy in retention or transfer. The lack of a significant tDCS effect suggests that M1 may not strongly contribute to self-controlled KR learning advantages; however, caution is advised with this interpretation as typical self-controlled learning benefits were not strongly replicated in the present experiment.

### 2023-07-13 papers/2015-19/2019_barros_hms.qmd
init

---
title: "Examining the impact of error estimation on the effects of self-controlled feedback"
type: "article"
author: "Barros JAC., Yantha ZD., Carter MJ., Hussien J., & Ste-Marie DM."
year: "2019"
publication: "Human Movement Science"
pdf: ""
doi: "https://doi.org/10.1016/j.humov.2018.12.002"
github: ""
materials: ""
#supplementary: ""
preprint: ""
toc: false
---

## Citation

### APA 7th

> Barros, J. A. C., Yantha, Z. D., Carter, M. J., Hussien, J., & Ste-Marie, D. M. (2019). Examining the impact of error estimation on the effects of self-controlled feedback. *Human Movement Science*, 63, 182–198. https://doi.org/10.1016/j.humov.2018.12.002

### Bibtex

<pre>
@article{,
  title = {Examining the Impact of Error Estimation on the Effects of Self-Controlled Feedback},
  author = {Barros, Joao A. C. and Yantha, Zachary D. and Carter, Michael J. and Hussien, Julia and Ste-Marie, Diane M.},
  date = {2019-02-01},
  journaltitle = {Human Movement Science},
  shortjournal = {Human Movement Science},
  volume = {63},
  pages = {182--198},
  issn = {0167-9457},
  doi = {10.1016/j.humov.2018.12.002},
  url = {https://www.sciencedirect.com/science/article/pii/S0167945718304640},
  urldate = {2023-07-13},
  langid = {english},
  keywords = {Autonomy,Competence,Information-processing,Motivation,Motor learning,Yoked feedback}
}
</pre>

## Abstract

Two experiments were conducted that examined the motivational and informational perspectives concerning learning advantages from self-controlled practice. Three groups were tasked with learning a novel skill; self-controlled (SC), yoked traditional (YT), and yoked with error estimation required during the acquisition phase (YE). Results from the delayed learning measures showed the YE group performed better than the SC and YT groups, for Expt. 1. A similar pattern emerged for Expt. 2, albeit, this was not significant. While there were no motivation differences across the groups in either experiment, a strong correlation in Expt. 2 was shown between error estimation capabilities, which were best for the YE group, and learning. These combined results suggest that informational processes contribute more to the self-controlled feedback learning advantage, relative to motivational contributions.

### 2023-07-13 papers/2020-25/2020_stemarie_chapter.qmd
init

---
title: "Self-controlled learning: Current findings, theoretical perspectives, and future directions"
type: "chapter"
author: "Ste-Marie DM., Carter MJ., & Yantha ZD."
year: "2020"
publication: "Skill Acquisition in Sport: Research, theory, and practice"
editors: "In N.J. Hodges & A.M. Williams (Eds.),"
edition: "(3rd ed.)."
publisher: "Routledge."
pdf: ""
doi: "https://doi.org/10.4324/9781351189750-7"
github: ""
materials: ""
#supplementary: ""
preprint: ""
toc: false
---

## Citation

### APA 7th

> Ste-Marie, D. M., Carter, M. J., & Yantha, Z. D. (2020). Self-controlled learning: Current findings, theoretical perspectives, and future directions. In *Skill Acquisition in Sport* (3rd ed.). Routledge.

### Bibtex

<pre>
@incollection{,
  title = {Self-Controlled Learning: {{Current}} Findings, Theoretical Perspectives, and Future Directions},
  shorttitle = {Self-Controlled Learning},
  booktitle = {Skill {{Acquisition}} in {{Sport}}},
  author = {Ste-Marie, Diane M. and Carter, Michael J. and Yantha, Zachary D.},
  year = {2020},
  chapter = {7},
  doi = {10.4324/9781351189750-7},
  month = {11},
  date = {2020},
  booktitle = {Skill acquisition in sport: {Research}, theory, and practice},
  editor = {{Hodges}, {Nicola J.} and {Williams}, {A. Mark}},
  edition = {3}
  publisher = {{Routledge}},
  isbn = {978-1-351-18975-0},
  pagetotal = {22}
}
</pre>

## Abstract

This chapter reviews the findings emanating from research that allows learners choice over: the variability of the practice schedule; the use of action observation; and the use of augmented feedback. It explores the idea that the practitioner may not need to plan everything down to the last detail, and that allowing learners to control aspects of their practice could be advantageous. The typical research protocol of self-controlled learning involves the comparison of learning outcomes for those who are provided choice over the provision of practice variable with those whom are not provided that choice, referred to as the yoked group. Variability in practice scheduling as a function of contextual interference involves granting control over the scheduling of multiple skills or tasks. Providing learners with demonstration, whether by instructor, another peer in the class, or video of someone showing the skill, is a common teaching technique and several researchers have shown advantages associated with such observational practice.

### 2023-07-13 papers/2020-25/2022_stgermain_jephpp.qmd
init

---
title: "Increased perceptions of autonomy through choice fail to enhance motor skill retention"
type: "article"
author: "St. Germain L., Williams A., Balbaa N., Poskus A., Leshchyshen O., Lohse KR., & Carter MJ."
year: "2022"
publication: "Journal of Experimental Psychology: Human Perception and Performance"
pdf: ""
doi: "https://doi.org/10.1037/xhp0000992"
github: "https://github.com/cartermaclab/expt_explicit-yoked"
materials: ""
#supplementary: ""
preprint: "https://psyarxiv.com/s34fg/"
toc: false
---

## Citation

### APA 7th

> St. Germain, L., Williams, A., Balbaa, N., Poskus, A., Leshchyshen, O., Lohse, K. R., & Carter, M. J. (2022). Increased perceptions of autonomy through choice fail to enhance motor skill retention. *Journal of Experimental Psychology: Human Perception and Performance*, 48(4), 370–379. https://doi.org/10.1037/xhp0000992

### Bibtex

<pre>
@article{,
  title = {Increased Perceptions of Autonomy through Choice Fail to Enhance Motor Skill Retention.},
  author = {St. Germain, Laura and Williams, Allison and Balbaa, Noura and Poskus, Andrew and Leshchyshen, Olena and Lohse, Keith R. and Carter, Michael J.},
  date = {2022-04},
  journaltitle = {Journal of Experimental Psychology: Human Perception and Performance},
  shortjournal = {Journal of Experimental Psychology: Human Perception and Performance},
  volume = {48},
  number = {4},
  pages = {370--379},
  issn = {1939-1277, 0096-1523},
  doi = {10.1037/xhp0000992},
  url = {http://doi.apa.org/getdoi.cfm?doi=10.1037/xhp0000992},
  urldate = {2023-07-13},
  langid = {english}
}
</pre>

## Abstract

There has been growing research interest in the effects that motivation plays in motor learning, and specifically how autonomy, competence, and social relatedness may directly benefit the learning process. Here, we present a preregistered manipulation of autonomy-support by providing learners with choice during the practice of a speed cup-stacking task. One group was given control over when a video demonstration was provided and the viewing speed. A yoked control group received an identical demonstration schedule, but without choice (as their schedule was matched to a participant with choice). Critically, we addressed a gap in the literature by adding a yoked group who was explicitly told that they were being denied choice and that their schedule was chosen by another participant. We found no statistically significant learning differences between groups, despite finding evidence that providing choice increased perceived autonomy. Equivalence tests further showed that although the groups were not statistically equivalent, the effect size is likely too small to practically study the effects of autonomy-support through choice in most motor learning labs. These findings add to a growing body of research that questions a causal role of autonomy-support on motor learning, and the robustness of the so-called self-controlled learning advantage.

### 2023-07-13 papers/2020-25/2023_lokesh_jnp.qmd
init

---
title: "Visual accuracy dominates over haptic speed for state estimation of a partner during collaborative sensorimotor interactions"
type: "article"
author: "Lokesh R., Sullivan SR., St. Germain L., Roth AM., Calalo JA., Buggeln J., Ngo T., Marchhart VRF., Carter MJ., & Cashaback JGA."
year: "2023"
publication: "Journal of Neurophysiology"
pdf: ""
doi: "https://doi.org/10.1152/jn.00053.2023"
github: ""
materials: ""
#supplementary: "https://doi.org/10.6084/m9.figshare.22704598"
preprint: ""
toc: false
---

## Citation

### APA 7th

> Lokesh, R., Sullivan, S. R., St. Germain, L., Roth, A. M., Calalo, J. A., Buggeln, J., Ngo, T., Marchhart, V. R. F., Carter, M. J., & Cashaback, J. G. A. (2023). Visual accuracy dominates over haptic speed for state estimation of a partner during collaborative sensorimotor interactions. *Journal of Neurophysiology*, 130(1), 23–42. https://doi.org/10.1152/jn.00053.2023

### Bibtex

<pre>
@article{,
  title = {Visual Accuracy Dominates over Haptic Speed for State Estimation of a Partner during Collaborative Sensorimotor Interactions},
  author = {Lokesh, Rakshith and Sullivan, Seth R. and St. Germain, Laura and Roth, Adam M. and Calalo, Jan A. and Buggeln, John and Ngo, Truc and Marchhart, Vanessa R. F. and Carter, Michael J. and Cashaback, Joshua G. A.},
  date = {2023-07},
  journaltitle = {Journal of Neurophysiology},
  volume = {130},
  number = {1},
  pages = {23--42},
  publisher = {{American Physiological Society}},
  issn = {0022-3077},
  doi = {10.1152/jn.00053.2023},
  url = {https://journals.physiology.org/doi/full/10.1152/jn.00053.2023},
  urldate = {2023-07-13},
  keywords = {collaboration,human-human interaction,optimal feedback control,sensorimotor,uncontrolled manifold}
}
</pre>

## Abstract

We routinely have physical interactions with others, whether it be handing someone a glass of water or jointly moving a heavy object together. These sensorimotor interactions between humans typically rely on visual feedback and haptic feedback. Recent single-participant studies have highlighted that the unique noise and time delays of each sense must be considered to estimate the state, such as the position and velocity, of one’s own movement. However, we know little about how visual feedback and haptic feedback are used to estimate the state of another person. Here, we tested how humans utilize visual feedback and haptic feedback to estimate the state of their partner during a collaborative sensorimotor task. Across two experiments, we show that visual feedback dominated haptic feedback during collaboration. Specifically, we found that visual feedback led to comparatively lower task-relevant movement variability, smoother collaborative movements, and faster trial completion times. We also developed an optimal feedback controller that considered the noise and time delays of both visual feedback and haptic feedback to estimate the state of a partner. This model was able to capture both lower task-relevant movement variability and smoother collaborative movements. Taken together, our empirical and modeling results support the idea that visual accuracy is more important than haptic speed to perform state estimation of a partner during collaboration.

### 2023-07-13 papers/2020-25/2023_mckay_irsep.qmd
init

---
title: "The combination of reporting bias and underpowered study designs has substantially exaggerated the motor learning benefits of self-controlled practice and enhanced expectancies: A meta-analysis"
type: "article"
author: "McKay B., Bacelar MFB., Parma JO., Miller MW., & Carter, MJ."
year: "2023"
publication: "International Review of Sport and Exercise Psychology"
pdf: ""
doi: "https://doi.org/10.1080/1750984X.2023.2207255"
github: "https://github.com/cartermaclab/proj_sc-ee-optimal-theory"
materials: "https://osf.io/vfza7/"
#supplementary: ""
preprint: "https://psyarxiv.com/3nhtc/"
toc: false
---

## Citation

### APA 7th

> McKay, B., Bacelar, M. F. B., Parma, J. O., Miller, M. W., & Carter, M. J. (2023). The combination of reporting bias and underpowered study designs has substantially exaggerated the motor learning benefits of self-controlled practice and enhanced expectancies: A meta-analysis. *International Review of Sport and Exercise Psychology*, 0(0), 1–21. https://doi.org/10.1080/1750984X.2023.2207255

### Bibtex

<pre>
@article{,
  title = {The Combination of Reporting Bias and Underpowered Study Designs Has Substantially Exaggerated the Motor Learning Benefits of Self-Controlled Practice and Enhanced Expectancies: {{A}} Meta-Analysis},
  shorttitle = {The Combination of Reporting Bias and Underpowered Study Designs Has Substantially Exaggerated the Motor Learning Benefits of Self-Controlled Practice and Enhanced Expectancies},
  author = {McKay, Brad and Bacelar, Mariane F. B. and Parma, Juliana O. and Miller, Matthew W. and Carter, Michael J.},
  date = {2023-05-04},
  journaltitle = {International Review of Sport and Exercise Psychology},
  volume = {0},
  number = {0},
  pages = {1--21},
  publisher = {{Routledge}},
  issn = {1750-984X},
  doi = {10.1080/1750984X.2023.2207255},
  url = {https://doi.org/10.1080/1750984X.2023.2207255},
  urldate = {2023-07-13},
  keywords = {motivation,OPTIMAL theory,publication bias,roBMA,Z-curve}
}
</pre>

## Abstract

Enhanced expectancies and autonomy-support through self-controlled practice conditions form the motivation pillar of OPTIMAL theory [Wulf, G., & Lewthwaite, R. (2016). Optimizing performance through intrinsic motivation and attention for learning: The OPTIMAL theory of motor learning. *Psychonomic Bulletin & Review*, 23(5), 1382–1414. https://doi.org/10.3758/s13423-015-0999-9]. The influence of these practice variables on motor learning was recently evaluated in two separate meta-analyses. Both meta-analyses found that the published literature suggested a moderate and significant benefit on motor learning; however, evidence for reporting bias was found in both literatures. Although multiple bias-corrected estimates were reported in the self-controlled meta-analysis, there was no principled way to prefer one over the other. In the enhanced expectancies meta-analysis, the trim-and-fill-technique failed to correct the estimated effects. Here, we addressed these limitations by reanalyzing the data from both meta-analyses using robust Bayesian meta-analysis methods. Our reanalysis revealed that reporting bias substantially exaggerated the benefits of these practice variables in the original meta-analyses. The true effects appear small, uncertain, and potentially null. We found the estimated average statistical power among all studies from the original meta-analyses was 6% (95% confidence interval [5%, 13%]). These results provide compelling and converging evidence that strongly suggests the available literature is insufficient to support the motivation pillar of OPTIMAL theory. Our results highlight the need for adequately powered experimental designs if motor learning scientists want to make evidence-based recommendations.

### 2023-07-13 papers/2020-25/2023_mckay_metapsych.qmd
init

---
title: "A critical re-analysis of six implicit learning papers"
type: "article"
author: "McKay B. & Carter MJ."
year: "2023"
publication: "Meta-Psychology"
pdf: ""
doi: "https://doi.org/10.15626/MP.2021.2938"
github: "https://www.github.com/cartermaclab/comm_lola-tzetzis-data-irregularities"
materials: "https://osf.io/raz6q/"
#supplementary: ""
preprint: "https://psyarxiv.com/n8mab/"
toc: false
---

## Citation

### APA 7th

> McKay, B., & Carter, M. (2023). A critical re-analysis of six implicit learning papers. *Meta-Psychology*, 7. https://doi.org/10.15626/MP.2021.2938

### Bibtex

<pre>
@article{,
  title = {A Critical Re-Analysis of Six Implicit Learning Papers},
  author = {McKay, Brad and Carter, Michael},
  date = {2023-07-10},
  journaltitle = {Meta-Psychology},
  volume = {7},
  issn = {2003-2714},
  doi = {10.15626/MP.2021.2938},
  url = {https://open.lnu.se/index.php/metapsychology/article/view/2938},
  urldate = {2023-07-13},
  langid = {english},
  keywords = {Effect sizes,GRIMMER,Metascience,Perceptual motor learning}
}
</pre>

## Abstract

We present a critical re-analysis of six implicit learning papers published by the same authors between 2010 and 2021. We calculated effect sizes for each pairwise comparison reported in the papers using the data published in each article. We further identified mathematically impossible data reported in multiple papers, either with deductive logic or by conducting a GRIMMER analysis of reported means and standard deviations. We found the pairwise effect sizes were implausible in all six articles in question, with Cohen’s *d* values often exceeding 100 and sometimes exceeding 1000. In contrast, the largest effect size observed in a million simulated experiments with a true effect of *d* = 3 was *d* = 6.6. Impossible statistics were reported in four out of the six articles. Reported test statistics and $\eta^{2}$ values were also implausible, with several $\eta^{2}$ = .99 and even $\eta^{2}$ = 1.0 for between-subjects main effects. The results reported in the six articles in question are unreliable. Many of the problems we identified could be spotted without further analysis.

### 2023-07-13 papers/2020-25/2023_stgermain_pbr.qmd
init

---
title: "Exercising choice over feedback schedules during practice is not advantageous for motor learning"
type: "article"
author: "St. Germain L., McKay B., Poskus A., Williams A., Leshchyshen O., Feldman S., Cashaback JGA., & Carter MJ."
year: "2023"
publication: "Psychonomic Bulletin & Review"
pdf: ""
doi: "https://doi.org/10.3758/s13423-022-02170-5"
github: "https://github.com/cartermaclab/expt_sc-feedback-characteristics"
materials: ""
#supplementary: "https://static-content.springer.com/esm/art%3A10.3758%2Fs13423-022-02170-5/MediaObjects/13423_2022_2170_MOESM1_ESM.pdf"
preprint: "https://psyarxiv.com/n52pq/"
toc: false
---

## Citation

### APA 7th

> St. Germain, L., McKay, B., Poskus, A., Williams, A., Leshchyshen, O., Feldman, S., Cashaback, J. G. A., & Carter, M. J. (2023). Exercising choice over feedback schedules during practice is not advantageous for motor learning. *Psychonomic Bulletin & Review*, 30(2), 621–633. https://doi.org/10.3758/s13423-022-02170-5

### Bibtex

<pre>
@article{,
  title = {Exercising Choice over Feedback Schedules during Practice Is Not Advantageous for Motor Learning},
  author = {St. Germain, Laura and McKay, Brad and Poskus, Andrew and Williams, Allison and Leshchyshen, Olena and Feldman, Sherry and Cashaback, Joshua G. A. and Carter, Michael J.},
  date = {2023-04-01},
  journaltitle = {Psychonomic Bulletin \& Review},
  shortjournal = {Psychon Bull Rev},
  volume = {30},
  number = {2},
  pages = {621--633},
  issn = {1531-5320},
  doi = {10.3758/s13423-022-02170-5},
  url = {https://doi.org/10.3758/s13423-022-02170-5},
  urldate = {2023-07-13},
  langid = {english},
  keywords = {Knowledge of results,OPTIMAL theory,Retention,Self-controlled}
}
</pre>

## Abstract

he idea that there is a self-controlled learning advantage, where individuals demonstrate improved motor learning after exercising choice over an aspect of practice compared to no-choice groups, has different causal explanations according to the OPTIMAL theory or an information-processing perspective. Within OPTIMAL theory, giving learners choice is considered an autonomy-supportive manipulation that enhances expectations for success and intrinsic motivation. In the information-processing view, choice allows learners to engage in performance-dependent strategies that reduce uncertainty about task outcomes. To disentangle these potential explanations, we provided participants in choice and yoked groups with error or graded feedback (Experiment 1) and binary feedback (Experiment 2) while learning a novel motor task with spatial and timing goals. Across both experiments (N = 228 participants), we did not find any evidence to support a self-controlled learning advantage. Exercising choice during practice did not increase perceptions of autonomy, competence, or intrinsic motivation, nor did it lead to more accurate error estimation skills. Both error and graded feedback facilitated skill acquisition and learning, whereas no improvements from pre-test performance were found with binary feedback. Finally, the impact of graded and binary feedback on perceived competence highlights a potential dissociation of motivational and informational roles of feedback. Although our results regarding self-controlled practice conditions are difficult to reconcile with either the OPTIMAL theory or the information-processing perspective, they are consistent with a growing body of evidence that strongly suggests self-controlled conditions are not an effective approach to enhance motor performance and learning.

### 2023-07-13 papers/2020-25/2023a_mckay_jmld.qmd
init

---
title: "Low prevalence of a priori power analyses in motor behavior research"
type: "article"
author: "McKay B., Corson A., Vinh M., Jeyarajan G., Tandon C., Brooks H., Hubley J., & Carter MJ."
year: "2023"
publication: "Journal of Motor Learning and Development"
pdf: ""
doi: "https://doi.org/10.1123/jmld.2022-0042"
github: "https://github.com/cartermaclab/proj_power-motor-behaviour"
materials: "https://osf.io/wsdpv/"
#supplementary: ""
preprint: "https://doi.org/10.51224/SRXIV.175"
toc: false
---

## Citation

### APA 7th

> McKay, B., Corson, A., Vinh, M.-A., Jeyarajan, G., Tandon, C., Brooks, H., Hubley, J., & Carter, M. J. (2023). Low prevalence of a priori power analyses in motor behavior research. *Journal of Motor Learning and Development*, 11(1), 15–28. https://doi.org/10.1123/jmld.2022-0042

### Bibtex

<pre>
@article{,
  title = {Low Prevalence of a Priori Power Analyses in Motor Behavior Research},
  author = {McKay, Brad and Corson, Abbey and Vinh, Mary-Anne and Jeyarajan, Gianna and Tandon, Chitrini and Brooks, Hugh and Hubley, Julie and Carter, Michael J.},
  year = {2023},
  date = {2022-12-26},
  journaltitle = {Journal of Motor Learning and Development},
  volume = {11},
  number = {1},
  pages = {15--28},
  publisher = {{Human Kinetics}},
  issn = {2325-3193, 2325-3215},
  doi = {10.1123/jmld.2022-0042},
  url = {https://journals.humankinetics.com/view/journals/jmld/11/1/article-p15.xml},
  urldate = {2023-07-13},
  langid = {english}
}
</pre>

## Abstract

A priori power analyses can ensure studies are unlikely to miss interesting effects. Recent metascience has suggested that kinesiology research may be underpowered and selectively reported. Here, we examined whether power analyses are being used to ensure informative studies in motor behavior. We reviewed every article published in three motor behavior journals between January 2019 and June 2021. Power analyses were reported in 13% of studies (*k* = 636) that tested a hypothesis. No study targeted the smallest effect size of interest. Most studies with a power analysis relied on estimates from previous experiments, pilot studies, or benchmarks to determine the effect size of interest. Studies without a power analysis reported support for their main hypothesis 85% of the time, while studies with a power analysis found support 76% of the time. The median sample sizes were *n* = 17.5 without a power analysis and *n* = 16 with a power analysis, suggesting the typical study design was underpowered for all but the largest plausible effect size. At present, power analyses are not being used to optimize the informativeness of motor behavior research. Adoption of this widely recommended practice may greatly enhance the credibility of the motor behavior literature.

### 2023-07-13 papers/2020-25/2023b_mckay_jmld.qmd
init

---
title: "On the reproducibility of power analyses in motor behavior research"
type: "article"
author: "McKay B., Bacelar MFB., & Carter MJ."
year: "2023"
publication: "Journal of Motor Learning and Development"
pdf: ""
doi: "https://doi.org/10.1123/jmld.2022-0061"
github: "https://github.com/cartermaclab/proj_power-reproducibility-motor-behaviour"
materials: "https://osf.io/9a6m8/"
#supplementary: ""
preprint: "https://doi.org/10.51224/SRXIV.184"
toc: false
---

## Citation

### APA 7th

> McKay, B., Bacelar, M. F. B., & Carter, M. J. (2023). On the reproducibility of power analyses in motor behavior research. *Journal of Motor Learning and Development*, 11(1), 29–44. https://doi.org/10.1123/jmld.2022-0061

### Bibtex

<pre>
@article{,
  title = {On the Reproducibility of Power Analyses in Motor Behavior Research},
  author = {McKay, Brad and Bacelar, Mariane F. B. and Carter, Michael J.},
  date = {2023-03-03},
  journaltitle = {Journal of Motor Learning and Development},
  volume = {11},
  number = {1},
  pages = {29--44},
  publisher = {{Human Kinetics}},
  issn = {2325-3193, 2325-3215},
  doi = {10.1123/jmld.2022-0061},
  url = {https://journals.humankinetics.com/view/journals/jmld/11/1/article-p29.xml},
  urldate = {2023-07-13},
  langid = {english}
}
</pre>

## Abstract

Recent metascience suggests that motor behavior research may be underpowered, on average. Researchers can perform a priori power analyses to ensure adequately powered studies. However, there are common pitfalls that can result in underestimating the required sample size for a given design and effect size of interest. Critical evaluation of power analyses requires successful analysis reproduction, which is conditional on the reporting of sufficient information. Here, we attempted to reproduce every power analysis reported in articles (*k* = 84/635) in three motor behavior journals between January 2019 and June 2021. We reproduced 7% of analyses using the reported information, which increased to 43% when we assumed plausible values for missing parameters. Among studies that reported sufficient information to evaluate, 63% reported using the same statistical test in the power analysis as in the study itself, and in 77%, the test addressed at least one of the identified hypotheses. Overall, power analyses were not commonly reported with sufficient information to ensure reproducibility. A nontrivial number of power analyses were also affected by common pitfalls. There is substantial opportunity to address the issue of underpowered research in motor behavior by increasing adoption of power analyses and ensuring reproducible reporting practices.

### 2023-07-13 papers/preprints/debrouwer_pdf.qmd
init

---
title: "Gaze behaviour reveals flexible encoding of competing reach goals under conditions of target uncertainty"
type: "article"
author: "de Brouwer AJ., Carter MJ., Smail LC., Wolpert DM., Gallivan JP., & Flanagan JR."
year: "2020"
publication: "bioR&#43859;iv"
pdf: ""
doi: "https://doi.org/10.1101/2020.09.02.279414"
github: ""
materials: ""
preprint: ""
toc: false
---

## Citation

### APA 7th

> Brouwer, A. J. de, Carter, M. J., Smail, L. C., Wolpert, D. M., Gallivan, J. P., & Flanagan, J. R. (2020). Gaze behaviour reveals flexible encoding of competing reach goals under conditions of target uncertainty. *bioRxiv*. https://doi.org/10.1101/2020.09.02.279414

### Bibtex

<pre>
@article{,
  title = {Gaze Behaviour Reveals Flexible Encoding of Competing Reach Goals under Conditions of Target Uncertainty},
  author = {{de Brouwer}, Anouk J., and Carter, Michael J. and Smail, Lauren C. and Wolpert, Daniel M. and Gallivan, Jason P. and Flanagan, J. Randall},
  date = {2020-09-03},
  eprinttype = {bioRxiv},
  eprintclass = {New Results},
  pages = {2020.09.02.279414},
  doi = {10.1101/2020.09.02.279414},
  url = {https://www.biorxiv.org/content/10.1101/2020.09.02.279414v1},
  urldate = {2023-07-13},
  langid = {english},
  pubstate = {preprint}
}
</pre>

## Abstract

In daily tasks, we are often confronted with competing potential targets and must select one to act on. It has been suggested that, prior to target selection, the human brain encodes the motor goals of multiple, potential targets. However, this view remains controversial and it has been argued that only a single motor goal is encoded, or that motor goals are only specified after target selection. To investigate this issue, we measured participants’ gaze behaviour while viewing two potential reach targets, one of which was cued after a preview period. We applied visuomotor rotations to dissociate each visual target location from its corresponding motor goal location; i.e., the location participants needed to aim their hand toward to bring the rotated cursor to the target. During the preview period, participants most often fixated both motor goals but also frequently fixated one, or neither, motor goal location. Further gaze analysis revealed that on trials in which both motor goals were fixated, both locations were held in memory simultaneously. These findings show that, at the level of single trials, the brain most often encodes multiple motor goals prior to target selection, but may also encode either one or no motor goals. This result may help reconcile a key debate concerning the specification of motor goals in cases of target uncertainty.

### 2023-07-13 papers/preprints/mckay_foa-meta.qmd
init

---
title: "Reporting bias, not external focus: A robust Bayesian meta-analysis of the attentional focus literature"
type: "article"
author: "McKay B., Corson AE., Seedu J., De Faveri, CS., Hasan, H., Arnold, K., Adams, FC., & Carter, MJ."
year: "2023"
publication: "SportR&#43859;iv"
pdf: ""
doi: "https://doi.org/10.51224/SRXIV.304"
github: "https://github.com/cartermaclab/proj_foa-optimal-theory"
materials: ""
preprint: ""
toc: false
---

## Citation

### APA 7th

> McKay, B., Corson, A., Seedu, J., Faveri, C. D., Hasan, H., Arnold, K., Adams, F., & Carter, M. (2023). Reporting bias, not external focus: A robust Bayesian meta-analysis of the attentional focus literature. *SportRxiv*. https://doi.org/10.51224/SRXIV.304

### Bibtex

<pre>
@article{,
  title = {Reporting Bias, Not External Focus: {{A}} Robust {{Bayesian}} Meta-Analysis of the Attentional Focus Literature},
  shorttitle = {Reporting Bias, Not External Focus},
  author = {McKay, Brad and Corson, Abbey and Seedu, Jeswende and Faveri, Celeste De and Hasan, Hibaa and Arnold, Kristen and Adams, Faith and Carter, Michael},
  date = {2023-06-20},
  eprinttype = {SportRxiv},
  doi = {10.51224/SRXIV.304},
  url = {https://sportrxiv.org/index.php/server/preprint/view/304},
  urldate = {2023-07-13},
  langid = {english},
  pubstate = {preprint},
  keywords = {Heterogeneity,Metascience,OPTIMAL theory,Skill acquisition,Sport science}
}
</pre>

## Abstract

Evidence has ostensibly been accumulating over the past two decades suggesting that an external focus of attention is superior to an internal focus for the performance and learning of motor skills. Seven previous meta-studies have all reported evidence of external focus superiority---the most comprehensive of which concluded the benefits apply to motor skill (a) retention, (b) transfer, and (c) performance; results in (d) reduced electromyographic activity during performance, and that (e) more distal external foci are superior to proximal external foci for performance. Here, we re-analyzed these data using robust Bayesian meta-analysis methods that included several plausible models of publication bias. We found moderate to strong evidence of publication bias for all five analyses. After correcting for publication bias, estimated mean effects were negligible: *g* = .01 (performance), *g* = .15 (retention), *g* = .09 (transfer), *g* = .06 (electromyography), and *g* = -.01 (distance effect). Bayes factors indicated data favored the null for each analysis, ranging from BF~01~ = 1.3 (retention) to 5.74 (performance). Further, we found clear evidence of heterogeneity in each analysis, suggesting the impact of attentional focus depends on yet unknown contextual factors. Our results contradict the existing consensus that an external focus is always more effective than an internal focus. Instead, focus of attention appears to have a variety of effects that we cannot account for, and on average those effects are small to nil. These results parallel previous metascience suggesting publication bias has obfuscated the motor learning literature.

### 2023-07-13 papers/preprints/roth_reinforcement.qmd
init

---
title: "Reinforcement-based processes actively regulate motor exploration along redundant solution manifolds"
type: "article"
author: "Roth AM., Calalo JA., Lokesh R., Sullivan SR., Grill S., Jeka JJ., van der Kooij K., Carter MJ., & Cashaback JGA."
year: "2023"
publication: "bioR&#43859;iv"
pdf: ""
doi: "https://doi.org/10.1101/2023.02.08.527668"
github: ""
materials: ""
#supplementary: ""
preprint: ""
toc: false
---

## Citation

### APA 7th

> Roth, A. M., Calalo, J. A., Lokesh, R., Sullivan, S. R., Grill, S., Jeka, J. J., Kooij, K. van der, Carter, M. J., & Cashaback, J. G. A. (2023). Reinforcement-based processes actively regulate motor exploration along redundant solution manifolds. *bioRxiv*. https://doi.org/10.1101/2023.02.08.527668

### Bibtex

<pre>
@preprint{roth2023,
  title = {Reinforcement-Based Processes Actively Regulate Motor Exploration along Redundant Solution Manifolds},
  author = {Roth, Adam M. and Calalo, Jan A. and Lokesh, Rakshith and Sullivan, Seth R. and Grill, Stephen and Jeka, John J. and family=Kooij, given=Katinka, prefix=van der, useprefix=false and Carter, Michael J. and Cashaback, Joshua G. A.},
  date = {2023-02-22},
  eprinttype = {bioRxiv},
  eprintclass = {New Results},
  pages = {2023.02.08.527668},
  doi = {10.1101/2023.02.08.527668},
  url = {https://www.biorxiv.org/content/10.1101/2023.02.08.527668v2},
  urldate = {2023-07-13},
  langid = {english},
  pubstate = {preprint}
}
</pre>

## Abstract

From a baby’s babbling to a songbird practicing a new tune, exploration is critical to motor learning. A hallmark of exploration is the emergence of random walk behaviour along solution manifolds, where successive motor actions are not independent but rather become serially dependent. Such exploratory random walk behaviour is ubiquitous across species, neural firing, gait patterns, and reaching behaviour. Past work has suggested that exploratory random walk behaviour arises from an accumulation of movement variability and a lack of error-based corrections. Here we test a fundamentally different idea—that reinforcement-based processes regulate random walk behaviour to promote continual motor exploration to maximize success. Across three human reaching experiments we manipulated the size of both the visually displayed target and an unseen reward zone, as well as the probability of reinforcement feedback. Our empirical and modelling results parsimoniously support the notion that exploratory random walk behaviour emerges by utilizing knowledge of movement variability to update intended reach aim towards recently reinforced motor actions. This mechanism leads to active and continuous exploration of the solution manifold, currently thought by prominent theories to arise passively. The ability to continually explore muscle, joint, and task redundant solution manifolds is beneficial while acting in uncertain environments, during motor development, or when recovering from a neurological disorder to discover and learn new motor actions.

### 2023-07-13 papers/preprints/stgermain_phd3.qmd
init

---
title: "Autonomy-supportive instructional language does not enhance skill acquisition compared to controlling instructional language"
type: "article"
author: "St. Germain L., McKay B., Tandon C., Seedu J., Barbera L., Carrillo C., Brown D.M.Y., & Carter, MJ."
year: "2023"
publication: "SportR&#43859;iv"
pdf: ""
doi: "https://doi.org/10.51224/SRXIV.298"
github: "https://github.com/cartermaclab/expt_instructional-language"
materials: ""
preprint: ""
toc: false
---

## Citation

### APA 7th

> St. Germain, L., McKay, B., Tandon, C., Seedu, J., Barbera, L., Carrillo, C., Brown, D., & Carter, M. (2023). Autonomy-supportive instructional language does not enhance skill acquisition compared to controlling instructional language. *SportRxiv*. https://doi.org/10.51224/SRXIV.298

### Bibtex

<pre>
@article{,
  title = {Autonomy-Supportive Instructional Language Does Not Enhance Skill Acquisition Compared to Controlling Instructional Language},
  author = {St. Germain, Laura and McKay, Brad and Tandon, Chitrini and Seedu, Jeswende and Barbera, Lidia and Carrillo, Chantal and Brown, Denver and Carter, Michael},
  date = {2023-05-19},
  eprinttype = {SportRxiv},
  doi = {10.51224/SRXIV.298},
  url = {https://sportrxiv.org/index.php/server/preprint/view/298},
  urldate = {2023-07-13},
  langid = {english},
  pubstate = {preprint},
  keywords = {Motor learning,OPTIMAL theory,Pre-registered,Retention}
}
</pre>

## Abstract

Instructional language is one of three possible techniques in OPTIMAL theory that can be manipulated to foster an autonomy-supportive practice environment to enhance motor performance and learning. While autonomy-supportive language has been shown to be beneficial in educational psychology, coaching, and health settings, the wording of task instructions has received minimal attention in the motor learning literature to date. Here, we investigated the influence of different instructional language styles on skill acquisition in a pre-registered experiment. Participants (*N* = 156) learned a speed cup stacking task and received instructions throughout practice that used either autonomy-supportive or controlling language. Although the autonomy-supportive instructions resulted in higher perceptions of autonomy, we did not find any group differences for motor performance in acquisition or in a delayed retention test. Perceptions of competence were higher at the end of acquisition following autonomy-supportive instructions, but this effect was transient as it disappeared before the delayed retention test. Interestingly, intrinsic motivation was lower before retention than after acquisition for the participants that received autonomy-supportive instructions. These data are difficult to reconcile with key predictions in OPTIMAL theory regarding a direct and causal influence of motivational factors on performance and learning. However, our equivalence test suggests these effects on skill acquisition may be smaller than what we were powered to detect. Nevertheless, this is consistent with a growing body of evidence highlighting the need for much larger *N* experiments in motor learning research.

### 2023-07-13 research.qmd
init

---
title: "Research"
pagetitle: "CarterLab | Research"
toc: true
---

Our research is supported by the [Natural Sciences and Engineering Research Council of Canada](https://www.nserc-crsng.gc.ca/), the [Canadian Foundation for Innovation](https://www.innovation.ca/), and the [Ontario Research Fund](https://www.ontario.ca/page/ontario-research-fund-research-infrastructure).

## Current projects

### Decision-making for action

Real-world action tasks involve a sequence of decision-making processes that determine, based on information extracted during the unfolding task, which movement to make next and when to make it. This complex interplay between decision-making and action is essential for understanding how people learn to make optimal choices, develop and learn skilled actions, and for elucidating how motor disorders (e.g., Parkinson's, Alzheimer's, etc) impact cognition in order to develop novel and more effective neurorehabilitation protocols. We are currently conducting experiments to better understand a) how individuals invest their time when learning multiple skills with the goal of maximize overall proficieny, and b) how individuals select and specify actions with multiple potential goals and/or sequential goals.

### Sensorimotor interactions

Our lives are filled with sensorimotor interactions between two or more people, from dancing to sports to receiving rehabilitation from a physical therapist. Sensorimotor neuroscience has largely focused on how a single person controls their movement. Yet our own evolution, survival, and neural hardwiring have been shaped by our ability to compete and collaborate with others. We are currently conducting experiments to better understand a) how the assignment of errors is used to adapt one's behaviour during multi-agent learning (e.g., virtual partner or another human), b) how we utilize online bidirectional sensorimotor information---vision and/or haptics---to make rapid decisions and jointly select actions together, and c) how different factors (e.g., individual, task, environment, socio-cultural) drive our decision to perform tasks alone or with a partner.

### Motor learning metascience

In recent years, there has been a lot of discussion about the replication crisis in psychology, neuroscience, and medical research to name just a few. Much of this is likely attributed to questionable research practices such as, but not limited to, *p*-hacking, HARKing (or Hypothesizing After Results are Known), publication bias, and a flawed incentive structure within academia. Metascience is the field of research on the scientific process itself and has been effective in advancing our understanding of how science (should) work and why it sometimes fails. We are interested in applying meta-research techniques to better understand the state of motor behaviour research in particular, but also more generally the field of kinesiology and sport science.

<!-- ### Many motor labs -->

<!-- ### Aging, disease, and motor control and learning -->

<!-- Although motor performance tends to decline as we age, our capacity to learn new skills remains intact. The significance of our ability to perform skilled actions and activities of daily living across the lifespan is exemplified by the many cases of individuals living with a neurological disease (e.g., Alzheimer’s, Parkinson’s) or stroke. These individuals experience long-term movement-related and cognitive deficits that can greatly reduce their functional independence and quality of life. We are interested in identifying the practice factors the supporting motor learning in healthy aging populations, as well as those that can help maintain functional independence in individuals living with mild cognitive impairment and/or Alzheimer’s disease. -->

### 2023-07-13 teaching.qmd
init

---
title: "Teaching"
pagetitle: "CarterLab | Teaching"
toc: false
---

Updates in progress...

### 2023-07-13 team.qmd
init

---
title: "Meet the team"
toc: false
listing:
  - id: senior
    contents: "team/senior/*.qmd"
    type: grid
    image-height: 225px
    grid-columns: 3
    fields: 
      - image
      - title
      - subtitle
    sort: sortby
    field-display-names: 
      started: "Started"
  - id: junior
    contents: "team/junior/*.qmd"
    type: grid
    image-height: 225px
    grid-columns: 3
    fields: 
      - image
      - title
      - subtitle
    sort: sortby
    field-display-names: 
      started: "Started"
---

## Senior members

:::{#senior}
:::

## Junior members

**Hibaa Hasan**, Undergraduate thesis student (Psychology, Neuroscience, and Behaviour)  
**Lidia Barbera**, Undergraduate thesis student (Life Sciences)  
**Ola Schwarzenberg**, Undergraduate thesis student (Life Sciences - Sensory Motor Systems specialization)  
**Enuri Dissanayake**, Undergraduate practicum student (Life Sciences - Sensory Motor Systems specialization)

<!-- :::{#junior} -->
<!-- ::: -->

## Collaborators

The lab maintains active and extensive research collaborations with:  
[Joshua Cashaback](https://joshcashaback.weebly.com/) | Department of Biomedical Engineering, University of Delaware  
[Brad Mckay](https://bradmckay-motor-meta.netlify.app/) | Milwaukee Brewers

Some of our other collaborators include:  
[Keith Lohse](https://sites.google.com/site/lohsekr/) | Department of Neurology, Washington University School of Medicine in Saint Louis  
[Matthew Miller](http://www.education.auburn.edu/initiatives/performance-exercise-psychophysiology-lab-pep-matt-miller-ph-d/) | School of Kinesiology, Auburn University  
[Mariane Bacelar](https://www.boisestate.edu/kinesiology/faculty-and-staff-mariane-bacelar-phd/) | Department of Kinesiology, Boise State University

## Alumni

Former lab members and what they did after leaving the lab or what they are currently doing (if known).

### Post-doctoral fellows

**Brad McKay** (2021-23); *Senior Strategist of Training Design, Milwaukee Brewers*

### Graduate students

**Laura St. Germain**, Ph.D. Kinesiology (2018-23); *Research and Data Specialist at Sheridan College*  
**Mirette Mounir**, M.Sc. Kinesiology (2019-21); *Dentistry at Western University*  
**Rajbir Sihu**, M.Sc. Kinesiology (2019-21); *Dentistry at the University of Toronto*

### Undergraduate students

#### Honours thesis

Chitrini Tandon (2021-23); Alyssa Skouros (2022-23); Kiana Masoudi (2022-23); Raika Bourmand (2021-22); Armin Sariaslani (2021-22); Katharine (Katie) Douglas (2021-22); Thinzar Soe (2021-22); Julianna Marfisi (2020-21); Matthew Tobis (2020-21); Andrew Poskus (2020-21); Sherry Feldman (2019-20); Olena Leshchyshen (2019-20); Noura Balbaa (2019-20)

#### Research practicum / project

Jeswende Seedu (2022-23); Vivian Li (2022); Caroline Jarvi (2022); Gurlal Gill (2021); Anita Chaseendran (2021); Gianna Jeyarajan (2021); Mackenzie (Kenzie) Bell (2021); Ashton Yuen (2021); Charlie Violin (2021); Ammaar Jan (2020); Faran Chaudhry (2020); Yu (Sarah) Fu (2020); Andrew Poskus (2019); Maya El-Zahed (2019); Grant Yang (2019); Olena Leshchyshen (2019); Rita Waseem (2019); Christian Kleiser (2018); Christopher Li (2018); Faryal Zahir (2018)

#### Research assistants

Elizabeth Mitchell (2020-23); Celeste de Faveri (2021-23); Lidia Barbera (2022-23); Hibaa Hasan (2022-23); Faith Adams (2022); Chitrini Tandon (2021-22); Kristen Arnold (2021-22); Alison Williams (2018-20); Andrew Poskus (2019); Kevin Gilotra (2019); Ashton Yuen (2019); Mackenzie (Kenzie) Bell (2019-21); Olena Leshchyshen (2018-19); Yu (Sarah) Fu (2018-19)

### 2023-07-13 team/senior/mikayla-lalli.qmd
init

---
title: "Mikayla Lalli"
subtitle: "M.Sc. Candidate"
image: mikayla-lalli.jpg
sortby: 2
started: "September 2022"
about:
  id: hero-heading
  template: solana
  links:
    - icon: github
      text: github
      href: https://www.github.com/mikaylalalli
---

:::{#hero-heading}

I joined the lab in September 2022 after completing my undergraduate studies at McMaster University in the School of Interdisciplinary Science. I am interested in motor cognition, specifically understanding the underlying cognitive mechanisms of motor interactions between multiple agents. My research focuses on decision making in collaborative human-human interactions. In my free time I enjoy playing the drums and teaching the lab about Harry Styles.

## Education

**McMaster University** | Hamilton, ON, Canada  
M.Sc in Kinesiology, Department of Kinesiology  
2022--Present

**McMaster University** | Hamilton, ON, Canada  
B.Sc. (Honours) in Life Sciences (Minor in Psychology), School of Interdisciplinary Science  
2018--22

:::

### 2023-07-13 team/senior/mike-carter.qmd
init

---
title: "Michael Carter"
subtitle: "Principal Investigator"
image: mike-carter.jpg
sortby: 1
started: "July 2017"
#resources:
  #- "carter_cv.pdf"
about:
  id: hero-heading
  template: solana
  links:
    #- icon: file-earmark-text
    #  text: vitae
    #  href: ./team/senior/carter_cv.pdf
    - icon: mortarboard
      text: scholar
      href: https://scholar.google.com/citations?user=9FY5gBwAAAAJ
    - icon: github
      text: github
      href: https://www.github.com/carterjmike
    - icon: twitter
      text: twitter
      href: https://www.twitter.com/carterjmike
---

:::{#hero-heading}

I am broadly interested in how the brain controls and learns skilled actions, as well as how we can improve the replicability and reproducibility of kinesiology and sport science research. This work relies on an interdisciplinary blend of theory, behaviour experimentation, and computational approaches from psychology, neuroscience, engineering, computer science, and statistics.

I completed my doctoral training under the supervision of [Dr. Diane Ste-Marie](https://www.uottawa.ca/faculty-health-sciences/human-kinetics/our-professors/diane-ste-marie) (Emeritus Professor) at the University of Ottawa where I studied the cognitive processes underlying self-controlled practice. During this time, I also worked closely with [Dr. Tony Carlsen](https://neuromotor.ca/) on projects related to bimanual coordination and motor preparation. I then completed a one-year postdoctoral fellowship in the Centre for Neuroscience Studies at Queen's University under the mentorship of [Dr. Randy Flanagan](https://www.flanganlab.com) and [Dr. Jason Gallivan](https://www.gallivanmaplab.com).

I am currently an Assistant Professor in the Department of Kinesiology (joined in 2017) at McMaster University, where I direct the Action, Cognition, and Metascience Lab. I teach undergraduate and graduate courses in the areas of motor control and learning, neurorehabilitation and robotics, statistics, and scientific computing. I currently serve as a Section Editor (Sensorimotor Control) for the journal Communications in Kinesiology, which is the flagship journal for the [Society of Transparency, Openness, and Replication in Kinesiology](http://www.storkinesiology.org/) (STORK). I also currently serve as the Chair of STORK.

## Education

**Queen's University** | Kingston, ON, Canada  
Postdoctoral Fellow, Centre for Neuroscience Studies  
2016--17

**University of Ottawa** | Ottawa, ON, Canada  
Ph.D. in Human Kinetics, School of Human Kinetics  
2011--16

**Brock University** | St. Catharines, ON, Canada  
M.Sc. in Kinesiology, Department of Kinesiology
2008--10

**Brock University** | St. Catharines, ON, Canada  
Bachelor of Physical Education (Honours), Department of Kinesiology
2004--08

:::

### 2023-07-13 team/senior/nour-alafif.qmd
init

---
title: "Nour Al Afif"
subtitle: "M.Sc. Candidate"
image: nour-alafif.jpg
sortby: 3
started: "September 2022"
about:
  id: hero-heading
  template: solana
  links:
    - icon: github
      text: github
      href: https://www.github.com/NourAlAfif19
---

:::{#hero-heading}

I joined the lab in September 2022 after completing my undergraduate studies at McMaster University in the Department of Psychology, Neuroscience, and Behaviour. My research interests include sensorimotor interactions (e.g., human-agent and human-human) and how different partners and forms of interaction influence motor learning. Other things I contribute to the lab include attempting to help with code and also making everyone feel better about themselves by being impressively bad at bowling.

## Education

**McMaster University** | Hamilton, ON, Canada  
M.Sc in Kinesiology, Department of Kinesiology  
2022--Present

**McMaster University** | Hamilton, ON, Canada  
B.Sc. (Honours) in Psychology, Neuroscience, & Behaviour (Minor in Biology), Department of Psychology, Neuroscience, & Behaviour  
2018--22

:::

### 2023-08-29 index.qmd
add news items and fix a description

@@
 
-<font color="#d08770">[June 28 2023].</font> **New award**. Congratulations Dr. Laura St. Germain on a successfully defending your doctoral work.
+<font color="#d08770">[August 28 2023].</font> **New members**.
+Welcome to Daniel Deletsu and Jiaqiao (Jack) Tang.
+Daniel will be starting his M.Sc in the lab and Jack will be starting his Ph.D in the lab.
+
+<font color="#d08770">[June 28 2023].</font> **New milestone**. Congratulations Dr. Laura St. Germain on a successfully defending your doctoral work.
 

### 2023-08-29 research.qmd
fix typo

@@
 This complex interplay between decision-making and action is essential for understanding how people learn to make optimal choices, develop and learn skilled actions, and for elucidating how motor disorders (e.g., Parkinson's, Alzheimer's, etc) impact cognition in order to develop novel and more effective neurorehabilitation protocols.
-We are currently conducting experiments to better understand a) how individuals invest their time when learning multiple skills with the goal of maximize overall proficieny, and b) how individuals select and specify actions with multiple potential goals and/or sequential goals.
+We are currently conducting experiments to better understand a) how individuals invest their time when learning multiple skills with the goal of maximize overall proficiency, and b) how individuals select and specify actions with multiple potential goals and/or sequential goals.
 

### 2023-08-29 team/senior/mikayla-lalli.qmd
reinit to new quarto version

@@
 image: mikayla-lalli.jpg
-sortby: 2
+sortby: 3
 started: "September 2022"

### 2023-08-29 team/senior/nour-alafif.qmd
reinit to new quarto version

@@
 image: nour-alafif.jpg
-sortby: 3
+sortby: 4
 started: "September 2022"

### 2023-08-29 team/senior/daniel-deletsu.qmd
init

---
title: "Daniel Deletsu"
subtitle: "M.Sc. Student"
image: daniel-deletsu.jpg
sortby: 5
started: "September 2023"
about:
  id: hero-heading
  template: solana
---

:::{#hero-heading}

I joined the lab in September 2023 after completing my undergraduate studies at Queen’s University where I majored in Life Sciences. I am interested in exploring the how sensory, motor, and cognitive processes are affected in healthy aging and in neurological disorders such as Alzheimer's disease. Outside of the lab, you are most likely to find me in a gym or on a basketball court.

## Education

**McMaster University** | Hamilton, ON, Canada  
M.Sc in Kinesiology, Department of Kinesiology  
2023--Present

**Queen's University** | Kingston, ON, Canada  
B.Sc. (Honours) in Life Sciences, Faculty of Health Sciences  
2019--23

:::

### 2023-08-29 team/senior/jack-tang.qmd
init

---
title: "Jiaqiao (Jack) Tang"
subtitle: "Ph.D. Student"
image: jack-tang.jpg
sortby: 2
started: "September 2023"
about:
  id: hero-heading
  template: solana
---

:::{#hero-heading}

I joined the lab in September 2023 after completing my Master of Science in Physical Therapy at the University of Toronto. Prior to that, I completed an undergraduate degree here at McMaster University where I earned my Bachelor of Science in Kinesiology. My research interests include the impact of exercise and/or physical activity on optimal aging, in particular cognition and mobility. My extracurricular interests include rock climbing and finding new places to eat!

## Education

**McMaster University** | Hamilton, ON, Canada  
Ph.D. in Kinesiology, Department of Kinesiology  
2022--Present

**University of Toronto** | Toronto, ON, Canada
M.Sc. in Physical Therapy, Department of Physical Therapy
2016--18

**McMaster University** | Hamilton, ON, Canada  
B.Sc. (Honours) in Kinesiology, Department of Kinesiology  
2011--15

:::

### 2023-09-06 index.qmd
update with new paper acceptance

@@
 #### Recent lab news ---------
+
+<font color="#d08770">[May 26 2023].</font> **Paper accepted**.
+Roth, A.M., Calalo, J.A., Lokesh, R., Sullivan, S.R., Grill, S., Jeka, J.J., van der Kooij, K., Carter, M.J, & Cashaback, J.G.A.
+Reinforcement-based processes actively regulate motor exploration along redundant solution manifolds.
+*Proceedings of the Royal Society B*.
 
@@
 doi: <https://doi.org/10.51224/SRXIV.304>
-
-<font color="#d08770">[May 26 2023].</font> **Paper accepted**.
-Lokesh, R., Sullivan, S.R., St.
-Germain, L., Roth, A.M., Calalo, J.A., Buggeln, J., Ngo, T., Marchhart, V.R.F., Carter, M.J, & Cashaback, J.G.A.
-Visual accuracy dominates over haptic speed for state estimation of a partner during collaborative sensorimotor interactions.
-*Journal of Neurophysiology*.

### 2023-09-22 team.qmd
update members on team page

@@
 
-**Hibaa Hasan**, Undergraduate thesis student (Psychology, Neuroscience, and Behaviour)  
-**Lidia Barbera**, Undergraduate thesis student (Life Sciences)  
-**Ola Schwarzenberg**, Undergraduate thesis student (Life Sciences - Sensory Motor Systems specialization)  
-**Enuri Dissanayake**, Undergraduate practicum student (Life Sciences - Sensory Motor Systems specialization)
+:::{#junior}
+:::
 
-<!-- :::{#junior} -->
-<!-- ::: -->
+<!-- **Hibaa Hasan**, Undergraduate thesis student (Psychology, Neuroscience, and Behaviour)   -->
+<!-- **Lidia Barbera**, Undergraduate thesis student (Life Sciences)   -->
+<!-- **Ola Schwarzenberg**, Undergraduate thesis student (Life Sciences - Sensory Motor Systems specialization)   -->
+<!-- **Enuri Dissanayake**, Undergraduate practicum student (Life Sciences - Sensory Motor Systems specialization)   -->
 

### 2023-09-22 team/junior/lidia-barbera.qmd
update members on team page

---
title: "Lidia Barbera"
subtitle: "Undergraduate thesis student"
image: lidia-barbera.jpg
sortby: 1
started: "September 2023"
about:
  id: hero-heading
  template: solana
---

:::{#hero-heading}

I first joined the lab in September 2022 as a volunteer research assistant during my third year of the Honours Life Sciences program. I am now completing my undergraduate thesis in the lab. My research interests include sensorimotor interactions and how the use of virtual partners can be beneficial for motor learning and rehabilitation. My experience working as a pilates instructor for clients undergoing physiotherapy has strengthened my interest in motor behaviour and has supported my passion for this area of research.

:::

### 2023-09-22 team/junior/ola-schwarzenberg.qmd
update members on team page

---
title: "Ola Schwarzenberg"
subtitle: "Undergraduate thesis student"
image: ola-schwarzenberg.jpg
sortby: 3
started: "September 2023"
about:
  id: hero-heading
  template: solana
---

:::{#hero-heading}

I joined the lab in September 2023 as an undergraduate thesis student and I am in the final year of my undergraduate degree in Life Sciences (Sensory Motor Systems specialization) with a minor in English and Cultural Studies. For my thesis work, I will be investigating cooperative decision-making. In my free time, I like to read, run, and play the piano.

:::

### 2023-09-22 index.qmd
fix date in news
update news feed

@@
 
-<font color="#d08770">[May 26 2023].</font> **Paper accepted**.
+<font color="#d08770">[September 22 2023].</font> **New award**.
+Congratulations to Daniel Deletsu who was awarded a 2-year Master's scholarship through an initiative from the Heart and Stroke Foundation of Canada, Brain Canada Foundation, and the Canadian Institutes of Health Research.
+
+<font color="#d08770">[September 6 2023].</font> **Paper accepted**.
 Roth, A.M., Calalo, J.A., Lokesh, R., Sullivan, S.R., Grill, S., Jeka, J.J., van der Kooij, K., Carter, M.J, & Cashaback, J.G.A.
@@
 Candidate) on winning the 2023 Franklin Henry Young Scientist Award in Motor Control and Learning from the Canadian Society for Psychomotor Learning and Sport Psychology.
-
-<font color="#d08770">[June 16 2023].</font> **New preprint**.
-McKay, B., Corson, A.E., Seedu, J., De Faveri, C.S., Hasan, H., Arnold, K., Adams, F.C., & Carter, M.J.
-Reporting bias, not external focus: A robust Bayesian meta-analysis of the attentional focus literature.
-*SportR*$\chi$*iv*.
-doi: <https://doi.org/10.51224/SRXIV.304>

### 2023-09-22 news.qmd
update with new paper acceptance
fix date in news
update news feed

@@
 ---
+
+<font color="#d08770">[September 22 2023].</font> **New award**.
+Congratulations to Daniel Deletsu who was awarded a 2-year Master's scholarship from the Heart and Stroke Foundation of Canada, Brain Canada Foundation, and the Canadian Institutes of Health Research.
+
+<font color="#d08770">[September 6 2023].</font> **Paper accepted**.
+Roth, A.M., Calalo, J.A., Lokesh, R., Sullivan, S.R., Grill, S., Jeka, J.J., van der Kooij, K., Carter, M.J, & Cashaback, J.G.A.
+Reinforcement-based processes actively regulate motor exploration along redundant solution manifolds.
+*Proceedings of the Royal Society B*.
 

### 2023-09-22 team/junior/mithun-manivannan.qmd
add new member

---
title: "Mithun Manivannan"
subtitle: "Undergraduate thesis student"
image: mithun-manivannan.jpg
sortby: 4
started: "September 2023"
about:
  id: hero-heading
  template: solana
---

:::{#hero-heading}

I joined the lab in September 2023 as an undergraduate thesis student and I am in my fourth year pursuing both a Honours Kinesiology and Mathematical Sciences Degree with a minor in Psychology. For my thesis work, I will be investigating sensorimotor human-human interactions and rehabilitation. Outside the lab, I enjoy playing the guitar, reading and staying active with friends.

:::

### 2023-09-23 team/junior/enuri-dissanayake.qmd
add new member

---
title: "Enuri Dissanayake"
subtitle: "Undergraduate thesis student"
image: enuri-dissanayake.jpg
sortby: 5
started: "September 2023"
about:
  id: hero-heading
  template: solana
---

:::{#hero-heading}

I joined the lab in September 2023 as a practicum student, and I am currently in my third year of my undergraduate degree in Life Sciences (Sensory Motor Systems). My research interests include motor learning and collaborative decision-making. Outside of the lab, I enjoy dragonboating, working out with friends, and finding new music!

:::

### 2023-09-23 team/junior/enuri-dissanayake.qmd
fix typo

@@
 title: "Enuri Dissanayake"
-subtitle: "Undergraduate thesis student"
+subtitle: "Undergraduate practicum student"
 image: enuri-dissanayake.jpg

### 2023-09-27 team/junior/jacqueline-zheng.qmd
add new members to team page

---
title: "Jacqueline Zheng"
subtitle: "Undergraduate practicum student"
image: jacqueline-zheng.jpg
sortby: 6
started: "September 2023"
about:
  id: hero-heading
  template: solana
---

:::{#hero-heading}

I joined the lab in September 2023 as a research practicum student and I am in my third year of the Honours Neuroscience program. My research interests include sensorimotor interactions and motor learning metascience. Outside of lab, I am a cat parent who loves food hunting in Hamilton and the GTA.

:::

### 2023-09-27 team/junior/vida-sussman.qmd
add new members to team page

---
title: "Vida Sussman"
subtitle: "Undergraduate research assistant"
image: vida-sussman.jpg
sortby: 6
started: "September 2023"
about:
  id: hero-heading
  template: solana
---

:::{#hero-heading}

I joined the lab as an undergraduate research assistant in March 2023. My research interests include investigating the neurological processes behind skill acquisition, as well as collaborative sensorimotor interactions involving two humans or a human and a virtual agent. Outside of the lab, I enjoy running with my dog, biking on trails that I definitely cannot handle, and going on hiking trips with friends!

:::

### 2023-10-18 papers/2020-25/2023_roth_rspb.qmd
update to published details

---
title: "Reinforcement-based processes actively regulate motor exploration along redundant solution manifolds"
type: "article"
author: "Roth AM., Calalo JA., Lokesh R., Sullivan SR., Grill S., Jeka JJ., van der Kooij K., Carter MJ., & Cashaback JGA."
year: "2023"
publication: "Proceedings of the Royal Society B"
pdf: ""
doi: "https://doi.org/10.1098/rspb.2023.1475"
github: "https://github.com/CashabackLab/Exploration-Along-Solution-Manifolds-Data"
materials: ""
#supplementary: "https://doi.org/10.6084/m9.figshare.c.6837535.v1"
preprint: "https://doi.org/10.1101/2023.02.08.527668"
toc: false
---

## Citation

### APA 7th

> Roth, A. M., Calalo, J. A., Lokesh, R., Sullivan, S. R., Grill, S., Jeka, J. J., Kooij, K. van der, Carter, M. J., & Cashaback, J. G. A. (2023). Reinforcement-based processes actively regulate motor exploration along redundant solution manifolds. *Proceedings of the Royal Society B*. https://doi.org/10.1098/rspb.2023.1475

### Bibtex

<pre>
@article{,
  title = {Reinforcement-Based Processes Actively Regulate Motor Exploration along Redundant Solution Manifolds},
  author = {Roth, Adam M. and Calalo, Jan A. and Lokesh, Rakshith and Sullivan, Seth R. and Grill, Stephen and Jeka, John J. and family=Kooij, given=Katinka, prefix=van der, useprefix=false and Carter, Michael J. and Cashaback, Joshua G. A.},
  date = {2023-02-22},
}
</pre>

## Abstract

From a baby's babbling to a songbird practising a new tune, exploration is critical to motor learning. A hallmark of exploration is the emergence of random walk behaviour along solution manifolds, where successive motor actions are not independent but rather become serially dependent. Such exploratory random walk behaviour is ubiquitous across species’ neural firing, gait patterns and reaching behaviour. The past work has suggested that exploratory random walk behaviour arises from an accumulation of movement variability and a lack of error-based corrections. Here, we test a fundamentally different idea---that reinforcement-based processes regulate random walk behaviour to promote continual motor exploration to maximize success. Across three human reaching experiments, we manipulated the size of both the visually displayed target and an unseen reward zone, as well as the probability of reinforcement feedback. Our empirical and modelling results parsimoniously support the notion that exploratory random walk behaviour emerges by utilizing knowledge of movement variability to update intended reach aim towards recently reinforced motor actions. This mechanism leads to active and continuous exploration of the solution manifold, currently thought by prominent theories to arise passively. The ability to continually explore muscle, joint and task redundant solution manifolds is beneficial while acting in uncertain environments, during motor development or when recovering from a neurological disorder to discover and learn new motor actions.

### 2024-01-21 papers/2020-25/2024_roth_neurosci.qmd
add new paper

---
title: "Punishment leads to greater sensorimotor learning but less movement variability compared to reward"
type: "article"
author: "Roth AM., Lokesh R., Tang J., Buggeln JH., Smith C., Calalo JA., Sullivan SR., Ngo T., St. Germain L., Carter MJ., & Cashaback JGA."
year: "2024"
publication: "Neurosicence"
pdf: ""
doi: "https://doi.org/10.1016/j.neuroscience.2024.01.004"
github: ""
materials: ""
#supplementary: "https://www.sciencedirect.com/science/article/pii/S0306452224000125#s0150"
preprint: ""
toc: false
---

## Citation

### APA 7th

> Roth, A.M., Lokesh, R., Tang, J., Buggeln, J.H., Smith, C., Calalo, J.A., Sullivan, S.R., Ngo, T., St. Germain, L., Carter, M.J., & Cashaback, J.G.A. (2024). Punishment leads to greater sensorimotor learning but less movement variability compared to reward. *Neuroscience*. https://doi.org/10.1016/j.neuroscience.2024.01.004

### Bibtex

<pre>
@article{,
  title = {Punishment leads to greater sensorimotor learning but less movement variability compared to reward},
  author = {Roth, Adam M. and Lokesh, Rakshith and Tang, Jiaqiao and Buggeln, John H. and Smith, Carly and Calalo, Jan A. and Sullivan, Seth R. and Ngo, Truc and St. Germain, Laura and Carter, Michael J. and Cashaback, Joshua G. A.},
  date = {2024},
}
</pre>

## Abstract

When a musician practices a new song, hitting a correct note sounds pleasant while striking an incorrect note sounds unpleasant. Such reward and punishment feedback has been shown to differentially influence the ability to learn a new motor skill. Recent work has suggested that punishment leads to greater movement variability, which causes greater exploration and faster learning. To further test this idea, we collected 102 participants over two experiments. Unlike previous work, in Experiment 1 we found that punishment did not lead to faster learning compared to reward (n = 68), but did lead to a greater extent of learning. Surprisingly, we also found evidence to suggest that punishment led to less movement variability, which was related to the extent of learning. We then designed a second experiment that did not involve adaptation, allowing us to further isolate the influence of punishment feedback on movement variability. In Experiment 2, we again found that punishment led to significantly less movement variability compared to reward (n = 34). Collectively our results suggest that punishment feedback leads to less movement variability. Future work should investigate whether punishment feedback leads to a greater knowledge of movement variability and or increases the sensitivity of updating motor actions.

### 2024-01-21 index.qmd
update news with new paper

@@
 
+<font color="#d08770">[January 22 2024].</font> **Paper accepted**.
+Roth, A.M., Lokesh, R., Tang, J., Buggeln, J.H., Smith, C., Calalo, J.A., Sullivan, S.R., Ngo, T., St.
+Germain, L., Carter, M.J., & Cashaback, J.G.A.
+Punishment leads to greater sensorimotor learning but less movement variability compared to reward.
+*Neuroscience*.
+<https://doi.org/10.1016/j.neuroscience.2024.01.004>
+
 <font color="#d08770">[September 22 2023].</font> **New award**.
@@
 *Proceedings of the Royal Society B*.
+<https://doi.org/10.1098/rspb.2023.1475>
 
@@
 <font color="#d08770">[June 28 2023].</font> **New milestone**. Congratulations Dr. Laura St. Germain on a successfully defending your doctoral work.
-
-<font color="#d08770">[June 20 2023].</font> **New award**.
-Congratulations to Laura St.
-Germain (Ph.D.
-Candidate) on winning the 2023 Franklin Henry Young Scientist Award in Motor Control and Learning from the Canadian Society for Psychomotor Learning and Sport Psychology.

### 2024-01-21 papers/2020-24/2021_mckay_cik.qmd
fix dir date range

---
title: "Expecting to teach a novel golf putting task did not enhance retention performance: A replication attempt of Daou and colleagues"
type: "article"
author: "McKay B., Hussien J., Carter MJ., Yantha ZD., & Ste-Marie DM."
year: "2021"
publication: "Communications in Kinesiology"
pdf: ""
doi: "https://doi.org/10.51224/cik.v1i2.39"
github: "https://github.com/cartermaclab/expt_expect-to-teach"
materials: "https://osf.io/r6z84/"
#supplementary: ""
preprint: "https://osf.io/preprints/sportrxiv/u897b/"
toc: false
---

## Citation

### APA 7th

> McKay, B., Hussien, J., Carter, M., Yantha, Z., & Ste-Marie, D. (2021). Expecting to teach a novel golf putting task did not enhance retention performance: A replication attempt of Daou and colleagues. *Communications in Kinesiology*, 1(2), Article 2. https://doi.org/10.51224/cik.v1i2.39

### Bibtex

<pre>
@article{,
  title = {Expecting to Teach a Novel Golf Putting Task Did Not Enhance Retention Performance: {{A}} Replication Attempt of {{Daou}} and Colleagues},
  shorttitle = {Expecting to Teach a Novel Golf Putting Task Did Not Enhance Retention Performance},
  author = {McKay, Brad and Hussien, Julia and Carter, Michael and Yantha, Zachary and Ste-Marie, Diane},
  date = {2021-09-03},
  journaltitle = {Communications in Kinesiology},
  volume = {1},
  number = {2},
  issn = {2767-0732},
  doi = {10.51224/cik.v1i2.39},
  url = {https://storkjournals.org/index.php/cik/article/view/39},
  urldate = {2023-07-13},
  issue = {2},
  langid = {english},
  keywords = {Motor learning,Preregistered,Sequential analysis,Two-one-sided-tests}
}
</pre>

## Abstract

While research has identified several practice variables that purportedly enhance motor learning, recent replication failures highlight the importance of conducting high-powered, pre-registered replications. The "expecting to teach" phenomenon was first reported in the motor learning literature by Daou and colleagues and suggested learners benefit from practicing with the understanding they will later need to teach the skill. The extant data have been mixed but generally positive. While expecting to teach has been shown to enhance motor learning of a golf putt, the mechanisms linked with this benefit are yet to be determined. As such, this study sought to replicate the expecting to teach effect and to extend those findings by exploring participants’ thought processes. Participants (*N* = 76) were randomly assigned to one of two groups in which they were told that they were learning a golf putt in order to 1) be tested on the skill or 2) teach the skill to another individual. On Day 1, participants completed pre-test putts, a pre-acquisition intrinsic motivation inventory (IMI), a 2-minute study of an instructional booklet, 50 practice putts and a post-acquisition IMI. During practice, participants were also afforded opportunities to continue studying the booklet and to complete additional putts. Participants returned 24 hours later to complete a retention, a transfer (50-cm longer golf-putt), and a free recall test, as well as a post-study survey to reveal thoughts they engaged in after practice but before (or during) the retention test. Similar to Daou et al., no significant differences were found with study time, number of acquisition putts, or motivation. However, golf-putting performance during retention resulted in no differences for radial error, *g* = -0.13 (95% C.I. [-0.55, 0.29]), between the two groups and no differences were shown for the recall test. The present study fails to replicate the benefits reported in the original experiments.

### 2024-01-21 papers/2020-24/2022_lokesh_scirep.qmd
fix dir date range

---
title: "Humans utilize sensory evidence of others’ intended action to make online decisions"
type: "article"
author: "Lokesh R., Sullivan S., Calalo JA., Roth A., Swanik B., Carter MJ., & Cashaback JGA."
year: "2022"
publication: "Scientific Reports"
pdf: ""
doi: "https://doi.org/10.1038/s41598-022-12662-y"
github: ""
materials: "https://osf.io/bgf7t/"
#supplementary: "https://static-content.springer.com/esm/art%3A10.1038%2Fs41598-022-12662-y/MediaObjects/41598_2022_12662_MOESM1_ESM.pdf"
preprint: ""
toc: false
---

## Citation

### APA 7th

> Lokesh, R., Sullivan, S., Calalo, J. A., Roth, A., Swanik, B., Carter, M. J., & Cashaback, J. G. A. (2022). Humans utilize sensory evidence of others’ intended action to make online decisions. *Scientific Reports*, 12(1), Article 1. https://doi.org/10.1038/s41598-022-12662-y

### Bibtex

<pre>
@article{,
  title = {Humans Utilize Sensory Evidence of Others’ Intended Action to Make Online Decisions},
  author = {Lokesh, Rakshith and Sullivan, Seth and Calalo, Jan A. and Roth, Adam and Swanik, Brenden and Carter, Michael J. and Cashaback, Joshua G. A.},
  date = {2022-05-25},
  journaltitle = {Scientific Reports},
  shortjournal = {Sci Rep},
  volume = {12},
  number = {1},
  pages = {8806},
  publisher = {{Nature Publishing Group}},
  issn = {2045-2322},
  doi = {10.1038/s41598-022-12662-y},
  url = {https://www.nature.com/articles/s41598-022-12662-y},
  urldate = {2023-07-13},
  issue = {1},
  langid = {english},
  keywords = {Decision,Dynamical systems,Human behaviour,Reward,Social behaviour}
}
</pre>

## Abstract

We often acquire sensory information from another person’s actions to make decisions on how to move, such as when walking through a crowded hallway. Past interactive decision-making research has focused on cognitive tasks that did not allow for sensory information exchange between humans prior to a decision. Here, we test the idea that humans accumulate sensory evidence of another person’s intended action to decide their own movement. In a competitive sensorimotor task, we show that humans exploit time to accumulate sensory evidence of another’s intended action and utilize this information to decide how to move. We captured this continuous interactive decision-making behaviour with a drift-diffusion model. Surprisingly, aligned with a ‘paralysis-by-analysis’ phenomenon, we found that humans often waited too long to accumulate sensory evidence and failed to make a decision. Understanding how humans engage in interactive and online decision-making has broad implications that spans sociology, athletics, interactive technology, and economics.

### 2024-01-21 papers/2020-24/2022_mckay_metapsych.qmd
fix dir date range

---
title: "Meta-analytic findings of the self-controlled motor learning literature: Underpowered, biased, and lacking evidential value"
type: "article"
author: "McKay B., Yantha ZD., Hussein J., Carter MJ., Ste-Marie DM."
year: "2022"
publication: "Meta-Psychology"
pdf: ""
doi: "https://doi.org/10.15626/MP.2021.2803"
github: "https://github.com/cartermaclab/proj_sc-meta-analysis"
materials: "https://osf.io/qbg69"
#supplementary: ""
preprint: "https://psyarxiv.com/8d3nb/"
toc: false
---

## Citation

### APA 7th

> McKay, B., Yantha, Z., Hussien, J., Carter, M., & Ste-Marie, D. (2022). Meta-analytic findings of the self-controlled motor learning literature: Underpowered, biased, and lacking evidential value. *Meta-Psychology*, 6. https://doi.org/10.15626/MP.2021.2803

### Bibtex

<pre>
@article{,
  title = {Meta-Analytic Findings of the Self-Controlled Motor Learning Literature: {{Underpowered}}, Biased, and Lacking Evidential Value},
  shorttitle = {Meta-{{Analytic Findings}} of the {{Self-Controlled Motor Learning Literature}}},
  author = {McKay, Brad and Yantha, Zachary and Hussien, Julia and Carter, Michael and Ste-Marie, Diane},
  date = {2022-11-08},
  journaltitle = {Meta-Psychology},
  volume = {6},
  issn = {2003-2714},
  doi = {10.15626/MP.2021.2803},
  url = {https://open.lnu.se/index.php/metapsychology/article/view/2803},
  urldate = {2023-07-13},
  langid = {english},
  keywords = {Choice,Meta-Analysis,Motor Learning,OPTIMAL Theory,p-curve,Publication Bias,Retention}
}
</pre>

## Abstract

The self-controlled motor learning literature consists of experiments that compare a group of learners who are provided with a choice over an aspect of their practice environment to a group who are yoked to those choices. A qualitative review of the literature suggests an unambiguous benefit from self-controlled practice. A meta-analysis was conducted on the effects of self-controlled practice on retention test performance measures with a focus on assessing and potentially correcting for selection bias in the literature, such as publication bias and p-hacking. First, a naïve random effects model was fit to the data and a moderate benefit of self-controlled practice, *g* = .44 (*k* = 52, *N* = 2061, 95% CI [.31, .56]), was found. Second, publication status was added to the model as a potential moderator, revealing a significant difference between published and unpublished findings, with only the former reporting a benefit of self-controlled practice. Third, to investigate and adjust for the impact of selectively reporting statistically significant results, a weight-function model was fit to the data with a one-tailed p-value cutpoint of .025. The weight-function model revealed substantial selection bias and estimated the true average effect of self- controlled practice as *g* = .107 (95% CI [.047, .18]). *P*-curve analyses were conducted on the statistically significant results published in the literature and the outcome suggested a lack of evidential value. Fourth, a suite of sensitivity analyses were conducted to evaluate the robustness of these results, all of which converged on trivially small effect estimates. Overall, our results suggest the benefit of self-controlled practice on motor learning is small and not currently distinguishable from zero.

### 2024-01-21 papers.qmd
update date range on page
change dir date

@@
   - id: papers2020
-    contents: "papers/2020-25/*.qmd"
+    contents: "papers/2020-24/*.qmd"
     template: papers.ejs
@@
 
-## 2020--23
+## 2020--24
 

### 2024-01-23 index.qmd
fix link behaviour

@@
 We also conduct metascience research to gain important insights into research practices within kinesiology and sport science.
-We are located in the Ivor Wynne Centre, which is home to the [Department of Kinesiology](https://www.science.mcmaster.ca/kinesiology/) within the [Faculty of Science](https://www.science.mcmaster.ca/) at [McMaster University](https://www.mcmaster.ca/).
+We are located in the Ivor Wynne Centre, which is home to the [Department of Kinesiology](https://www.science.mcmaster.ca/kinesiology/){target="_blank"} within the [Faculty of Science](https://www.science.mcmaster.ca/){target="_blank"} at [McMaster University](https://www.mcmaster.ca/){target="_blank"}.
 
@@
 *Neuroscience*.
-<https://doi.org/10.1016/j.neuroscience.2024.01.004>
+[https://doi.org/10.1016/j.neuroscience.2024.01.004](https://doi.org/10.1016/j.neuroscience.2024.01.004){target="_blank"}
 
@@
 *Proceedings of the Royal Society B*.
-<https://doi.org/10.1098/rspb.2023.1475>
+[https://doi.org/10.1098/rspb.2023.1475](https://doi.org/10.1098/rspb.2023.1475){target="_blank"}
 

### 2024-01-23 news.qmd
update news with new paper
fix link behaviour

@@
 ---
+
+<font color="#d08770">[January 22 2024].</font> **Paper accepted**.
+Roth, A.M., Lokesh, R., Tang, J., Buggeln, J.H., Smith, C., Calalo, J.A., Sullivan, S.R., Ngo, T., St.
+Germain, L., Carter, M.J., & Cashaback, J.G.A.
+Punishment leads to greater sensorimotor learning but less movement variability compared to reward.
+*Neuroscience*.
+[https://doi.org/10.1016/j.neuroscience.2024.01.004](https://doi.org/10.1016/j.neuroscience.2024.01.004){target="_blank"}
 
@@
 *Proceedings of the Royal Society B*.
+[https://doi.org/10.1098/rspb.2023.1475](https://doi.org/10.1098/rspb.2023.1475){target="_blank"}
 
@@
 *SportR*$\chi$*iv*.
-doi: <https://doi.org/10.51224/SRXIV.304>
+[https://doi.org/10.51224/SRXIV.304](https://doi.org/10.51224/SRXIV.304){target="_blank"}
 
@@
 *Journal of Neurophysiology*.
+[https://doi.org/10.1152/jn.00053.2023](https://doi.org/10.1152/jn.00053.2023){target="_blank"}
 
@@
 *SportR*$\chi$*iv*.
-doi: <https://doi.org/10.51224/SRXIV.298>
+[https://doi.org/10.51224/SRXIV.298](https://doi.org/10.51224/SRXIV.298){target="_blank"}
 
@@
 *International Review of Sport and Exercise Psychology*.
+[https://doi.org/10.1080/1750984X.2023.2207255](https://doi.org/10.1080/1750984X.2023.2207255){target="_blank"}

### 2024-01-23 research.qmd
fix link behaviour

@@
 
-Our research is supported by the [Natural Sciences and Engineering Research Council of Canada](https://www.nserc-crsng.gc.ca/), the [Canadian Foundation for Innovation](https://www.innovation.ca/), and the [Ontario Research Fund](https://www.ontario.ca/page/ontario-research-fund-research-infrastructure).
+Our research is supported by the [Natural Sciences and Engineering Research Council of Canada](https://www.nserc-crsng.gc.ca/){target="_blank"}, the [Canadian Foundation for Innovation](https://www.innovation.ca/){target="_blank"}, and the [Ontario Research Fund](https://www.ontario.ca/page/ontario-research-fund-research-infrastructure){target="_blank"}.
 

### 2024-01-23 join.qmd
add info about applying to lab

@@
 
-Updates in progress...
+## Undergraduate student opportunities
+
+Undergraduate students are vital to the lab’s success and we love working with students from different academic programs and backgrounds.
+Undergraduate students will have the opportunity to work in the lab as part of their undergraduate degree requirements (e.g., research practicums, honour’s thesis, etc) or to explore an interest in sensorimotor neuroscience by gaining experience as a volunteer research assistant.
+You will have the opportunity to contribute to all stages of the research process, with the goal of disseminating your findings at an academic conference and/or in a peer-reviewed journal.
+There is also the possibility of paid summer positions depending on your experience and the availability of funds; however, these positions are generally given to students who have already worked in the lab.
+
+If you are interested in joining the team, please email your completed [application form](https://raw.githubusercontent.com/cartermaclab/lab-website/master/files/2024_carterlab_undergraduate-application-form.pdf){target="_blank"}, an up-to-date curriculum vitae, and unofficial transcripts to motorlab@mcmaster.ca.
+
+**The application period for practicum, project, and thesis courses for the 2024-25 academic year is now open.**
+
+- Applications will be received until Friday, March 1, 2024
+- Applicants selected for an interview will be notified by Friday, March 8, 2024
+- Interviews will take place in mid-to-late March
+- Offers for a practicum, project, or thesis position in the lab will be sent to selected students by Friday, March 29, 2024
+
+Please be aware that volunteer research assistant positions are filled on a rolling basis and as needed.
+
+## Graduate student opportunities
+
+The study of sensorimotor behaviour is multidisciplinary so students with backgrounds in the areas of, but not limited to, kinesiology, neuroscience, psychology, life or health sciences, engineering, or computer science are encouraged to apply.
+There are a limited number of graduate student positions in the lab at any given time.
+This approach allows for a more individualized training environment for each student, larger research stipends/bursaries, and the option to attend 1-2 academic conferences each year.
+Students interested in completing their M.Sc or Ph.D studies in the lab are encouraged to consult the relevant information pertaining to graduate studies in the [Department of Kinesiology](https://www.science.mcmaster.ca/kinesiology/graduate/graduate-studies.html){target="_blank"} and the [School of Graduate Studies](https://gs.mcmaster.ca/){target="_blank"}.
+
+### M.Sc and Ph.D applicants
+
+If you are interested in completing your M.Sc or Ph.D in the lab, please email Dr.
+Carter (cartem11@mcmaster.ca) an up-to-date curriculum vitae, unofficial academic transcripts, and a 1-page statement of research interests.

### 2024-02-06 team/junior/francesca-caputo.qmd
add new members

---
title: "Francesca Caputo"
subtitle: "Undergraduate practicum student"
image: francesca-caputo.png
sortby: 6
started: "January 2024"
about:
  id: hero-heading
  template: solana
---

:::{#hero-heading}

I joined the lab in January 2024 as a practicum student. I am currently in the third year of my undergraduate degree in the Biology Research Specialization. My research interests include motor learning and the dynamics of neural circuits. Outside of the lab, I enjoy testing out new recipes, going on adventures with my friends, and playing the guitar!

:::

### 2024-02-06 team/junior/jil-soni.qmd
add new members

---
title: "Jil Soni"
subtitle: "Undergraduate practicum student"
image: jil-soni.png
sortby: 6
started: "January 2024"
about:
  id: hero-heading
  template: solana
---

:::{#hero-heading}

I joined the lab in January 2024 as a research practicum student. I am in my third year of Life Sciences (Sensory Motor Systems specialization) with a minor in Statistics. My research interests include sensorimotor interactions and cooperative decision-making. Outside of the lab, I enjoy reading a good book, painting, and going on hikes!

:::

### 2024-02-06 team/junior/michael-croteau.qmd
add new members

---
title: "Michael Croteau"
subtitle: "Undergraduate practicum student"
image: michael-croteau.jpg
sortby: 6
started: "January 2024"
about:
  id: hero-heading
  template: solana
---

:::{#hero-heading}

I joined the lab in January 2024 as a practicum student. I am in my third year as an undergraduate neuroscience student. My research interests include investigating somatosensory and motor systems, and I also enjoy learning about computer science and organic chemistry on the side. In my spare time I like to rock climb, work out, read (mostly sci-fi and fantasy), and play video games and sports.

:::

### 2024-04-12 team/junior/jacqueline-zheng.qmd
update team page

@@
 title: "Jacqueline Zheng"
-subtitle: "Undergraduate practicum student"
+subtitle: "Undergraduate research assistant"
 image: jacqueline-zheng.jpg

### 2024-04-12 team/junior/michael-croteau.qmd
update team page

@@
 title: "Michael Croteau"
-subtitle: "Undergraduate practicum student"
+subtitle: "Undergraduate research assistant"
 image: michael-croteau.jpg

### 2024-04-12 team.qmd
update team page

@@
 
-<!-- **Hibaa Hasan**, Undergraduate thesis student (Psychology, Neuroscience, and Behaviour)   -->
-<!-- **Lidia Barbera**, Undergraduate thesis student (Life Sciences)   -->
-<!-- **Ola Schwarzenberg**, Undergraduate thesis student (Life Sciences - Sensory Motor Systems specialization)   -->
-<!-- **Enuri Dissanayake**, Undergraduate practicum student (Life Sciences - Sensory Motor Systems specialization)   -->
-
 ## Collaborators
@@
 
-Chitrini Tandon (2021-23); Alyssa Skouros (2022-23); Kiana Masoudi (2022-23); Raika Bourmand (2021-22); Armin Sariaslani (2021-22); Katharine (Katie) Douglas (2021-22); Thinzar Soe (2021-22); Julianna Marfisi (2020-21); Matthew Tobis (2020-21); Andrew Poskus (2020-21); Sherry Feldman (2019-20); Olena Leshchyshen (2019-20); Noura Balbaa (2019-20)
+Lidia Barbera (2023-24); Hibaa Hasan (2023-24); Ola Schwarzenberg (2023-24); Mithun Manivannan (2023-24); Chitrini Tandon (2021-23); Alyssa Skouros (2022-23); Kiana Masoudi (2022-23); Raika Bourmand (2021-22); Armin Sariaslani (2021-22); Katharine (Katie) Douglas (2021-22); Thinzar Soe (2021-22); Julianna Marfisi (2020-21); Matthew Tobis (2020-21); Andrew Poskus (2020-21); Sherry Feldman (2019-20); Olena Leshchyshen (2019-20); Noura Balbaa (2019-20)
 
@@
 
-Jeswende Seedu (2022-23); Vivian Li (2022); Caroline Jarvi (2022); Gurlal Gill (2021); Anita Chaseendran (2021); Gianna Jeyarajan (2021); Mackenzie (Kenzie) Bell (2021); Ashton Yuen (2021); Charlie Violin (2021); Ammaar Jan (2020); Faran Chaudhry (2020); Yu (Sarah) Fu (2020); Andrew Poskus (2019); Maya El-Zahed (2019); Grant Yang (2019); Olena Leshchyshen (2019); Rita Waseem (2019); Christian Kleiser (2018); Christopher Li (2018); Faryal Zahir (2018)
+Jacqueline Zheng (2023-24); Abby Girouard (2023-24); Michael Croteau (2024); Aditya Trivedi (2024); Navishka Brahmbhatt (2024); Francesca Caputo (2024); Jil Soni (2024); Enuri Dissanayake (2023); Jeswende Seedu (2022-23); Vivian Li (2022); Caroline Jarvi (2022); Gurlal Gill (2021); Anita Chaseendran (2021); Gianna Jeyarajan (2021); Mackenzie (Kenzie) Bell (2021); Ashton Yuen (2021); Charlie Violin (2021); Ammaar Jan (2020); Faran Chaudhry (2020); Yu (Sarah) Fu (2020); Andrew Poskus (2019); Maya El-Zahed (2019); Grant Yang (2019); Olena Leshchyshen (2019); Rita Waseem (2019); Christian Kleiser (2018); Christopher Li (2018); Faryal Zahir (2018)
 

### 2024-04-12 index.qmd
change landing page image back to iwc
new paper accepted as news

@@
 
-![](images/uni-hall-front.jpg)
+![](images/iwc-front.jpg)
 
@@
 #### Recent lab news ---------
+
+<font color="#d08770">[April 12 2024].</font> **Paper accepted**.
+McKay, B., Corson, A.E., Seedu, J., De Faveri, C.S., Hasan, H., Arnold, K., Adams, F.C., & Carter, M.J.
+Reporting bias, not external focus: A robust Bayesian meta-analysis and systematic review of the attentional focus literature.
+*Psychological Bulletin*.
 
@@
 Daniel will be starting his M.Sc in the lab and Jack will be starting his Ph.D in the lab.
-
-<font color="#d08770">[June 28 2023].</font> **New milestone**. Congratulations Dr. Laura St. Germain on a successfully defending your doctoral work.

### 2024-04-24 join.qmd
remove information about applying for 2024-25 academic year

@@
 
-**The application period for practicum, project, and thesis courses for the 2024-25 academic year is now open.**
-
-- Applications will be received until Friday, March 1, 2024
-- Applicants selected for an interview will be notified by Friday, March 8, 2024
-- Interviews will take place in mid-to-late March
-- Offers for a practicum, project, or thesis position in the lab will be sent to selected students by Friday, March 29, 2024
+**The application period for practicum, project, and thesis courses for the 2024-25 academic year is now closed.**
 

### 2024-05-10 papers/2020-24/2024_roth_neurosci.qmd
fix typo

--- 2024-01-21 papers/2020-25/2024_roth_neurosci.qmd
@@
 year: "2024"
-publication: "Neurosicence"
+publication: "Neuroscience"
 pdf: ""

### 2024-05-17 team/junior/eleanore-wu.qmd
add new member

---
title: "Eleanore Wu"
subtitle: "Undergraduate research assistant"
image: eleanore-wu.png
sortby: 6
started: "May 2024"
about:
  id: hero-heading
  template: solana
---

:::{#hero-heading}

I joined the lab as an undergraduate research assistant in May 2024. My research interests include human-agent and human-human interactions, as well as investigating how these factors could affect motor learning. Outside of the lab, I enjoy playing badminton and volleyball, baking, and drinking bubble tea.

:::

### 2024-05-31 team/junior/eshaa-tariq.qmd
update team page

---
title: "Eshaa Tariq"
subtitle: "Undergraduate research assistant"
image: eshaa-tariq.jpg
sortby: 6
started: "May 2024"
about:
  id: hero-heading
  template: solana
---

:::{#hero-heading}

I joined the lab in May 2024 as an undergraduate research assistant. I am currently enrolled in the Honours Kinesiology program at McMaster. My research interests include proprioception and how it particularly relates to sensorimotor interactions. Outside of the lab, I enjoy playing volleyball, reading fictional novels, and watching true crime and horror shows.

:::

### 2024-10-02 index.qmd
update news

--- 2024-01-23 index.qmd
@@
 
-<font color="#d08770">[January 22 2024].</font> **Paper accepted**.
-Roth, A.M., Lokesh, R., Tang, J., Buggeln, J.H., Smith, C., Calalo, J.A., Sullivan, S.R., Ngo, T., St.
-Germain, L., Carter, M.J., & Cashaback, J.G.A.
-Punishment leads to greater sensorimotor learning but less movement variability compared to reward.
-*Neuroscience*.
-[https://doi.org/10.1016/j.neuroscience.2024.01.004](https://doi.org/10.1016/j.neuroscience.2024.01.004){target="_blank"}
+<font color="#d08770">[September 18 2024].</font> **Paper accepted**.
+Roth, A.M., Buggeln, J.H., Hoh, J., Woods, J.M., Sullivan, S.R., Ngo, T., Calalo, J.A., Lokesh, R., Morton, S.M., Grill, S., Jeka, J.J., Carter, M.J., & Cashaback, J.G.A.
+Roles and interplay of reinforcement-based and error-based processes during reaching and gait in neurotypical adults and individuals with Parkinson's disease.
+*PLoS Computational Biology*.
 
-<font color="#d08770">[September 22 2023].</font> **New award**.
-Congratulations to Daniel Deletsu who was awarded a 2-year Master's scholarship through an initiative from the Heart and Stroke Foundation of Canada, Brain Canada Foundation, and the Canadian Institutes of Health Research.
+<font color="#d08770">[September 05 2023].</font> **New milestone**.
+Congratulations to Mikayla Lalli on successfully defending her MSc work.
+We are excited that Mikayla is staying in the lab for her doctoral studies.
 
-<font color="#d08770">[September 6 2023].</font> **Paper accepted**.
-Roth, A.M., Calalo, J.A., Lokesh, R., Sullivan, S.R., Grill, S., Jeka, J.J., van der Kooij, K., Carter, M.J, & Cashaback, J.G.A.
-Reinforcement-based processes actively regulate motor exploration along redundant solution manifolds.
-*Proceedings of the Royal Society B*.
-[https://doi.org/10.1098/rspb.2023.1475](https://doi.org/10.1098/rspb.2023.1475){target="_blank"}
+<font color="#d08770">[September 03 2024].</font> **Paper accepted**.
+St.
+Germain, L., McKay, B., Barbera, L., Tandon, C., Seedu, J., Carrillo, C., Brown, B.M.Y., & Carter, M.J.
+Autonomy-supportive instructional language does not enhance skill acquisition compared to controlling instructional language.
+*Psychological Research*.
 
-<font color="#d08770">[August 28 2023].</font> **New members**.
-Welcome to Daniel Deletsu and Jiaqiao (Jack) Tang.
-Daniel will be starting his M.Sc in the lab and Jack will be starting his Ph.D in the lab.
-
-<font color="#d08770">[June 28 2023].</font> **New milestone**. Congratulations Dr. Laura St. Germain on a successfully defending your doctoral work.
+<font color="#d08770">[August 20 2024].</font> **New Preprint**.
+Calalo, J.A., Ngo, T.T., Sullivan, S.R., Strand, K., Buggeln, J.H., Lokesh, R., Roth, A.M., Carter, M.J, Kurtzer, I.L., & Cashaback, J.G.A.
+Online movements reflect ongoing deliberation.
+*bioR$\chi$iv*.
+[https://doi.org/10.1101/2024.08.19.608669](https://doi.org/10.1101/2024.08.19.608669){target="_blank"}

### 2024-10-02 join.qmd
update news

@@
 
-If you are interested in joining the team, please email your completed [application form](https://raw.githubusercontent.com/cartermaclab/lab-website/master/files/2024_carterlab_undergraduate-application-form.pdf){target="_blank"}, an up-to-date curriculum vitae, and unofficial transcripts to motorlab@mcmaster.ca.
+If you are interested in joining the team, please email your completed [application form](https://raw.githubusercontent.com/cartermaclab/lab-website/master/files/2024_carterlab_undergraduate-application-form.pdf){target="_blank"}, an up-to-date curriculum vitae, and unofficial transcripts to cartem11@mcmaster.ca.
 

### 2024-10-02 news.qmd
new paper accepted as news
update news

@@
 ---
+
+<font color="#d08770">[September 18 2024].</font> **Paper accepted**.
+Roth, A.M., Buggeln, J.H., Hoh, J., Woods, J.M., Sullivan, S.R., Ngo, T., Calalo, J.A., Lokesh, R., Morton, S.M., Grill, S., Jeka, J.J., Carter, M.J., & Cashaback, J.G.A.
+Roles and interplay of reinforcement-based and error-based processes during reaching and gait in neurotypical adults and individuals with Parkinson's disease.
+*PLoS Computational Biology*.
+
+<font color="#d08770">[September 05 2023].</font> **New milestone**.
+Congratulations to Mikayla Lalli on successfully defending her MSc work.
+We are excited that Mikayla is staying in the lab for her doctoral studies.
+
+<font color="#d08770">[September 03 2024].</font> **Paper accepted**.
+St.
+Germain, L., McKay, B., Barbera, L., Tandon, C., Seedu, J., Carrillo, C., Brown, B.M.Y., & Carter, M.J.
+Autonomy-supportive instructional language does not enhance skill acquisition compared to controlling instructional language.
+*Psychological Research*.
+
+<font color="#d08770">[August 20 2024].</font> **New Preprint**.
+Calalo, J.A., Ngo, T.T., Sullivan, S.R., Strand, K., Buggeln, J.H., Lokesh, R., Roth, A.M., Carter, M.J, Kurtzer, I.L., & Cashaback, J.G.A.
+Online movements reflect ongoing deliberation.
+*bioR$\chi$iv*.
+[https://doi.org/10.1101/2024.08.19.608669](https://doi.org/10.1101/2024.08.19.608669){target="_blank"}
+
+<font color="#d08770">[April 12 2024].</font> **Paper accepted**.
+McKay, B., Corson, A.E., Seedu, J., De Faveri, C.S., Hasan, H., Arnold, K., Adams, F.C., & Carter, M.J.
+Reporting bias, not external focus: A robust Bayesian meta-analysis and systematic review of the attentional focus literature.
+*Psychological Bulletin*.
 

### 2024-11-20 index.qmd
update news

@@
 
+<font color="#d08770">[October 21 2024].</font> **New milestone**.
+Congratulations to Nour Al Afif on successfully defending her MSc work.
+We are excited that Nour is staying in the lab for her doctoral studies.
+
 <font color="#d08770">[September 18 2024].</font> **Paper accepted**.
@@
 
-<font color="#d08770">[September 05 2023].</font> **New milestone**.
+<font color="#d08770">[September 05 2024].</font> **New milestone**.
 Congratulations to Mikayla Lalli on successfully defending her MSc work.
@@
 *Psychological Research*.
-
-<font color="#d08770">[August 20 2024].</font> **New Preprint**.
-Calalo, J.A., Ngo, T.T., Sullivan, S.R., Strand, K., Buggeln, J.H., Lokesh, R., Roth, A.M., Carter, M.J, Kurtzer, I.L., & Cashaback, J.G.A.
-Online movements reflect ongoing deliberation.
-*bioR$\chi$iv*.
-[https://doi.org/10.1101/2024.08.19.608669](https://doi.org/10.1101/2024.08.19.608669){target="_blank"}

### 2025-01-17 index.qmd
site and layout updates

@@
 
-The **Action, Cognition, and Metascience Lab** is an interdisciplinary research team investigating basic scientific questions about how the human brain controls and learns skilled actions.
-We study decision-making for action and practice factors supporting skill acquisition and maintenance in single- and multi-agent scenarios.
-We also conduct metascience research to gain important insights into research practices within kinesiology and sport science.
-We are located in the Ivor Wynne Centre, which is home to the [Department of Kinesiology](https://www.science.mcmaster.ca/kinesiology/){target="_blank"} within the [Faculty of Science](https://www.science.mcmaster.ca/){target="_blank"} at [McMaster University](https://www.mcmaster.ca/){target="_blank"}.
+The **Action, Cognition, and Metascience Lab** is an interdisciplinary research team interested in how the human brain controls and learns skilled actions in healthy and clinical populations.
+We also conduct metascience research to gain insights into research practices within kinesiology and related areas.
+The lab is located in the Ivor Wynne Centre, which is home to the [Department of Kinesiology](https://www.science.mcmaster.ca/kinesiology/){target="_blank"} within the [Faculty of Science](https://www.science.mcmaster.ca/){target="_blank"} at [McMaster University](https://www.mcmaster.ca/){target="_blank"}.
 

### 2025-01-17 papers.qmd
site and layout updates

@@
 toc-title: "Jump to..."
-listing:
-  - id: preprints
-    contents: "papers/preprints/*.qmd"
-    template: papers.ejs
-    sort:
-      - "year desc"
-      - "author"
-  - id: papers2020
-    contents: "papers/2020-24/*.qmd"
-    template: papers.ejs
-    sort:
-      - "year desc"
-      - "author"
-  - id: papers2015
-    contents: "papers/2015-19/*.qmd"
-    template: papers.ejs
-    sort:
-      - "year desc"
-      - "author"
-  - id: papers2010
-    contents: "papers/2010-14/*.qmd"
-    template: papers.ejs
-    sort:
-      - "year desc"
-      - "author"
 ---
@@
 
-:::{#preprints}
-:::
+- Calalo JA., Ngo TT., Sullivan SR., Strand K., Buggeln JH., Lokesh R., Roth AM., Carter MJ., Kurtzer IL., & Cashaback JGA. (2024). Online movements reflect ongoing deliberation. *bioR$\chi$iv*. ---
+[{{< ai doi >}}](https://doi.org/10.1101/2024.08.19.608669){target="_blank" style="color: inherit;"}
 
-## 2020--24
+- de Brouwer AJ., Carter MJ., Smail LC., Wolpert DM., Gallivan JP., & Flanagan JR.
+(2020).
+Gaze behaviour reveals flexible encoding of competing reach goals under conditions of target uncertainty.
+*bioR$\chi$iv*.
+---
+[{{< ai doi >}}](https://doi.org/10.1101/2020.09.02.279414){target="_blank" style="color: inherit;"}
 
-:::{#papers2020}
-:::
+## 2025
 
-## 2015--19
+- St.
+Germain L., McKay B., Tandon C., Seedu J., Barbera L., Carrillo C., Brown D.M.Y., & Carter, MJ.
+(2025).
+Autonomy-supportive instructional language does not enhance skill acquisition compared to controlling instructional language.
+*Psychological Research*.
+---
+[{{< ai doi >}}](https://doi.org/10.1007/s00426-024-02059-z){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2025_st-germain-etal_autonomy-supportive-instructional-language-does-not-enhance-skill-acquisition-compared-to-controlling-instructional-language.pdf){target="_blank" style="color: inherit;"}
+[{{< fa brands github >}}](https://github.com/cartermaclab/expt_instructional-language){target="_blank" style="color: inherit;"}
 
-:::{#papers2015}
-:::
+## 2024
 
-## 2010--14
+- McKay B., Corson AE., Seedu J., De Faveri CS., Hasan H., Arnold K., Adams FC., & Carter MJ.
+(2024).
+Reporting bias, not external focus: A robust Bayesian meta-analysis and systematic review of the external focus of attention literature.
+*Psychological Bulletin*.
+---
+[{{< ai doi >}}](https://doi.org/10.1037/bul0000451){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2024_mckay-etal_reporting-bias-not-external-focus-a-robust-bayesian-meta-analysis-and-systematic-review-of-the-external-focus-of-attention.pdf){target="_blank" style="color: inherit;"}
+[{{< fa brands github >}}](https://github.com/cartermaclab/proj_foa-optimal-theory){target="_blank" style="color: inherit;"}
 
-:::{#papers2010}
-:::
+- Roth AM., Buggeln JH., Hoh JE., Wood JM., Sullivan SR., Ngo TT., Calalo JA., Lokesh R., Morton SM., Grill S., Jeka JJ., Carter MJ., & Cashaback JGA.
+(2024).
+Roles and interplay of reinforcement-based and error-based processes during reaching and gait in neurotypical adults and individuals with Parkinson’s disease *PLoS Computational Biology*.
+---
+[{{< ai doi >}}](https://doi.org/10.1371/journal.pcbi.1012474){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2024_roth-etal_roles-and-interplay-of-reinforcement-based-and-error-based-processes-during-reaching-and-gait-in-neurotypical-adults-and-indi.pdf){target="_blank" style="color: inherit;"}
+[{{< fa brands github >}}](https://github.com/CashabackLab/Roles_and_Interplay_of_Reinforcement_and_Error){target="_blank" style="color: inherit;"}
+
+- Roth AM., Lokesh R., Tang J., Buggeln JH., Smith C., Calalo JA., Sullivan SR., Ngo T., St.
+Germain L., Carter MJ., & Cashaback JGA.
+(2024).
+Punishment leads to greater sensorimotor learning but less movement variability compared to reward.
+*Neuroscience*.
+---
+[{{< ai doi >}}](https://doi.org/10.1016/j.neuroscience.2024.01.004){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2024_roth-etal_punishment-leads-to-greater-sensorimotor-learning-but-less-movement-variability-compared-to-reward.pdf){target="_blank" style="color: inherit;"}
+
+## 2023
+
+- McKay B., Bacelar MFB., Parma JO., Miller MW., & Carter, MJ.
+(2023).
+The combination of reporting bias and underpowered study designs has substantially exaggerated the motor learning benefits of self-controlled practice and enhanced expectancies: A meta-analysis.
+*International Review of Sport and Exercise Psychology*.
+---
+[{{< ai doi >}}](https://doi.org/10.1080/1750984X.2023.2207255){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2023_mckay-etal_the-combination-of-reporting-bias-and-underpowered-study-designs-has-substantially-exaggerated-the-motor-learning-benefits-of.pdf){target="_blank" style="color: inherit;"}
+[{{< fa brands github >}}](https://github.com/cartermaclab/proj_sc-ee-optimal-theory){target="_blank" style="color: inherit;"}
+
+- McKay B., Corson A., Vinh M., Jeyarajan G., Tandon C., Brooks H., Hubley J., & Carter MJ.
+(2023).
+Low prevalence of a priori power analyses in motor behavior research.
+*Journal of Motor Learning and Development*.
+---
+[{{< ai doi >}}](https://doi.org/10.1123/jmld.2022-0042){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2023_mckay-etal_low-prevalence-of-a-priori-power-analyses-in-motor-behavior-research.pdf){target="_blank" style="color: inherit;"}
+[{{< fa brands github >}}](https://github.com/cartermaclab/proj_power-motor-behaviour){target="_blank" style="color: inherit;"}
+
+- McKay B., Bacelar MFB., & Carter MJ. (2023). On the reproducibility of power analyses in motor behavior research. *Journal of Motor Learning and Development*. ---
+[{{< ai doi >}}](https://doi.org/10.1123/jmld.2022-0061){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2023_mckay-etal_on-the-reproducibility-of-power-analyses-in-motor-behavior-research.pdf){target="_blank" style="color: inherit;"}
+[{{< fa brands github >}}](https://github.com/cartermaclab/proj_power-reproducibility-motor-behaviour){target="_blank" style="color: inherit;"}
+
+- Lokesh R., Sullivan SR., St.
+Germain L., Roth AM., Calalo JA., Buggeln J., Ngo T., Marchhart VRF., Carter MJ., & Cashaback JGA.
+(2023).
+Visual accuracy dominates over haptic speed for state estimation of a partner during collaborative sensorimotor interactions.
+*Journal of Neurophysiology*.
+---
+[{{< ai doi >}}](https://doi.org/10.1152/jn.00053.2023){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2023_lokesh-etal_visual-accuracy-dominates-over-haptic-speed-for-state-estimation-of-a-partner-during-collaborative-sensorimotor-interactions.pdf){target="_blank" style="color: inherit;"}
+[{{< fa brands github >}}](https://github.com/CashabackLab/VisionHaptics_Collab_OFCModel){target="_blank" style="color: inherit;"}
+
+- McKay B. & Carter MJ. (2023). A critical re-analysis of six implicit learning papers. *Meta-Psychology*. ---
+[{{< ai doi >}}](https://doi.org/10.15626/MP.2021.2938){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2023_mckay-carter_a-critical-re-analysis-of-six-implicit-learning-papers.pdf){target="_blank" style="color: inherit;"}
+[{{< fa brands github >}}](https://github.com/cartermaclab/comm_lola-tzetzis-data-irregularities){target="_blank" style="color: inherit;"}
+
+- Roth AM., Calalo JA., Lokesh R., Sullivan SR., Grill S., Jeka JJ., van der Kooij K., Carter MJ., & Cashaback JGA.
+(2023).
+Reinforcement-based processes actively regulate motor exploration along redundant solution manifolds.
+*Proceedings of the Royal Society B*.
+---
+[{{< ai doi >}}](https://doi.org/10.1098/rspb.2023.1475){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2023_roth-etal_reinforcement-based-processes-actively-regulate-motor-exploration-along-redundant-solution-manifolds.pdf){target="_blank" style="color: inherit;"}
+[{{< fa brands github >}}](https://github.com/CashabackLab/Exploration-Along-Solution-Manifolds-Data){target="_blank" style="color: inherit;"}
+
+- St.
+Germain L., McKay B., Poskus A., Williams A., Leshchyshen O., Feldman S., Cashaback JGA., & Carter MJ.
+(2023).
+Exercising choice over feedback schedules during practice is not advantageous for motor learning.
+*Psychonomic Bulletin & Review*.
+---
+[{{< ai doi >}}](https://doi.org/10.3758/s13423-022-02170-5){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2023_st-germain-etal_exercising-choice-over-feedback-schedules-during-practice-is-not-advantageous-for-motor-learning.pdf){target="_blank" style="color: inherit;"}
+[{{< fa brands github >}}](https://github.com/cartermaclab/expt_sc-feedback-characteristics){target="_blank" style="color: inherit;"}
+
+## 2022
+
+*Note. Parental leave May 2022 to Dec 2022*
+
+- McKay B., Yantha ZD., Hussein J., Carter MJ., Ste-Marie DM.
+(2022).
+Meta-analytic findings of the self-controlled motor learning literature: Underpowered, biased, and lacking evidential value.
+*Meta-Psychology*.
+---
+[{{< ai doi >}}](https://doi.org/10.15626/MP.2021.2803){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2022_mckay-etal_meta-analytic-findings-of-the-self-controlled-motor-learning-literature-underpowered-biased-and-lacking-evidential-value.pdf){target="_blank" style="color: inherit;"}
+[{{< fa brands github >}}](https://github.com/cartermaclab/proj_sc-meta-analysis){target="_blank" style="color: inherit;"}
+
+- Lokesh R., Sullivan S., Calalo JA., Roth A., Swanik B., Carter MJ., & Cashaback JGA.
+(2022).
+Humans utilize sensory evidence of others’ intended action to make online decisions.
+*Scientific Reports*.
+---
+[{{< ai doi >}}](https://doi.org/10.1038/s41598-022-12662-y){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2022_lokesh-etal_humans-utilize-sensory-evidence-of-others-intended-action-to-make-online-decisions.pdf){target="_blank" style="color: inherit;"}
+[{{< ai osf >}}](https://osf.io/bgf7t/){target="_blank" style="color: inherit;"}
+
+- St.
+Germain L., Williams A., Balbaa N., Poskus A., Leshchyshen O., Lohse KR., & Carter MJ.
+(2022).
+Increased perceptions of autonomy through choice fail to enhance motor skill retention.
+*Journal of Experimental Psychology: Human Perception and Performance*.
+---
+[{{< ai doi >}}](){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/){target="_blank" style="color: inherit;"}
+[{{< fa brands github >}}](){target="_blank" style="color: inherit;"}
+
+## 2021
+
+*Note. Parental leave January 2021 to August 2021*
+
+- McKay B., Hussien J., Carter MJ., Yantha ZD., & Ste-Marie DM.
+(2021).
+Expecting to teach a novel golf putting task did not enhance retention performance: A replication attempt of Daou and colleagues.
+*Communications in Kinesiology*.
+---
+[{{< ai doi >}}](https://doi.org/10.51224/cik.v1i2.39){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2021_mckay-etal_expecting-to-teach-a-novel-golf-putting-task-did-not-enhance-retention-performance-a-replication-attempt-of-daou-and-colleag.pdf){target="_blank" style="color: inherit;"}
+[{{< fa brands github >}}](https://github.com/cartermaclab/expt_expect-to-teach){target="_blank" style="color: inherit;"}
+
+## 2020
+
+*Note. Lab shutdown from COVID-19 pandemic*
+
+## 2019
+
+- Ste-Marie DM., Carter MJ., & Yantha ZD.
+(2020).
+Self-controlled learning: Current findings, theoretical perspectives, and future directions.
+In N.J.
+Hodges & A.M.
+Williams (Eds.), *Skill Acquisition in Sport: Research, theory, and practice* (3rd ed.).
+Routledge.
+---
+[{{< ai doi >}}](https://doi.org/10.4324/9781351189750-7){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2019_ste-marie-etal_self-controlled-learning.pdf){target="_blank" style="color: inherit;"}
+
+- Barros JAC., Yantha ZD., Carter MJ., Hussien J., & Ste-Marie DM. (2019). Examining the impact of error estimation on the effects of self-controlled feedback. *Human Movement Science*. ---
+[{{< ai doi >}}](https://doi.org/10.1016/j.humov.2018.12.002){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2019_barros-etal_examining-the-impact-of-error-estimation-on-the-effects-of-self-controlled-feedback.pdf){target="_blank" style="color: inherit;"}
+
+## 2018
+
+- Carter MJ., Smith V., Carlsen AN., & Ste-Marie DM.
+(2018).
+Anodal transcranial direct current stimulation over the primary motor cortex does not enhance the learning benefits of self-controlled feedback schedules.
+*Psychological Research*.
+---
+[{{< ai doi >}}](https://doi.org/10.1007/s00426-017-0846-x){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2018_carter-etal_anodal-transcranial-direct-current-stimulation-over-the-primary-motor-cortex-does-not-enhance-the-learning-benefits-of-self-c.pdf){target="_blank" style="color: inherit;"}
+
+## 2017
+
+- Carter MJ., & Ste-Marie DM. (2017). Not all choices are created equal: Task-relevant choices enhance motor learning compared to task-irrelevant choices. *Psychonomic Bulletin & Review*. ---
+[{{< ai doi >}}](https://doi.org/10.3758/s13423-017-1250-7){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2017_carter-ste-marie_not-all-choices-are-created-equal-task-relevant-choices-enhance-motor-learning-compared-to-task-irrelevant-choices.pdf){target="_blank" style="color: inherit;"}
+
+- Carter MJ., & Ste-Marie DM.
+(2017).
+An interpolated activity during the knowledge-of-results delay interval eliminates the learning advantages of self-controlled feedback schedules.
+*Psychological Research*.
+---
+[{{< ai doi >}}](https://doi.org/10.1007/s00426-016-0757-2){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2017_carter-ste-marie_an-interpolated-activity-during-the-knowledge-of-results-delay-interval-eliminates-the-learning-advantages-of-self-controlled.pdf){target="_blank" style="color: inherit;"}
+
+- Carter MJ., & Maslovat D., & Carlsen AN.
+(2017).
+Intentional switches between coordination patterns are faster following anodal-tDCS applied over the supplementary motor area.
+*Brain Stimulation*.
+---
+[{{< ai doi >}}](https://doi.org/10.1016/j.brs.2016.11.002){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2017_carter-etal_intentional-switches-between-coordination-patterns-are-faster-following-anodal-tdcs-applied-over-the-supplementary-motor-area.pdf){target="_blank" style="color: inherit;"}
+
+- Maslovat D., Carter MJ., & Carlsen AN. (2017). Response preparation and execution during intentional bimanual pattern switching. *Journal of Neurophysiology*. ---
+[{{< ai doi >}}](2017_maslovat-etal_response-preparation-and-execution-during-intentional-bimanual-pattern-switching.pdf){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2017_maslovat-etal_response-preparation-and-execution-during-intentional-bimanual-pattern-switching.pdf){target="_blank" style="color: inherit;"}
+
+## 2016
+
+- Carter MJ., Smith V., & Ste-Marie DM.
+(2016).
+Judgments of learning are significantly higher following feedback on relatively good versus relatively poor trials despite no actual learning differences.
+*Human Movement Science*.
+---
+[{{< ai doi >}}](https://doi.org/10.1016/j.humov.2015.11.006){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2016_carter-etal_judgments-of-learning-are-significantly-higher-following-feedback-on-relatively-good-versus-relatively-poor-trials-despite-no.pdf){target="_blank" style="color: inherit;"}
+
+- Carter MJ., Rathwell S., & Ste-Marie DM.
+(2016).
+Motor skill retention is modulated by strategy choice during self-controlled knowledge of results schedules.
+*Journal of Motor Learning and Development*.
+---
+[{{< ai doi >}}](https://doi.org/10.1123/jmld.2015-0023){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2016_carter-etal_motor-skill-retention-is-modulated-by-strategy-choice-during-self-controlled-knowledge-of-results-schedules.pdf){target="_blank" style="color: inherit;"}
+
+- Martini R., Carter MJ., Yoxon E., Cumming J., & Ste-Marie DM. (2016). Development and validation of the Movement Imagery Questionnaire for Children (MIQ-C). *Psychology of Sport and Exercise*. ---
+[{{< ai doi >}}](https://doi.org/10.1016/j.psychsport.2015.08.008){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2016_martini-etal_development-and-validation-of-the-movement-imagery-questionnaire-for-children-miq-c.pdf){target="_blank" style="color: inherit;"}
+
+- Patterson JT., Hart A., Hansen S., Carter MJ., & Ditor D.
+(2016).
+Measuring investment in learning: Can electrocardiogram provide an indication of cognitive effort during learning?.
+*Perceptual and Motor Skills*.
+---
+[{{< ai doi >}}](https://doi.org/10.1177/0031512516633348){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2016_patterson-etal_measuring-investment-in-learning-can-electrocardiogram-provide-an-indication-of-cognitive-effort-during-learning.pdf){target="_blank" style="color: inherit;"}
+
+- Ste-Marie DM., Carter MJ., Law B., Vertes K., & Smith V.
+(2016).
+Self-controlled learning benefits: exploring contributions of self-efficacy and intrinsic motivation via path analysis.
+*Journal of Sports Sciences*.
+---
+[{{< ai doi >}}](https://doi.org/10.1080/02640414.2015.1130236){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2016_ste-marie-etal_self-controlled-learning-benefits-exploring-contributions-of-self-efficacy-and-intrinsic-motivation-via-path-analysis.pdf){target="_blank" style="color: inherit;"}
+
+## 2015
+
+- Carter MJ., Maslovat D., & Carlsen AN.
+(2015).
+Anodal transcranial direct current stimulation applied over the supplementary motor area delays spontaneous antiphase-to-in-phase transitions.
+*Journal of Neurophysiology*.
+---
+[{{< ai doi >}}](https://doi.org/10.1152/jn.00662.2014){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2015_carter-etal_anodal-transcranial-direct-current-stimulation-applied-over-the-supplementary-motor-area-delays-spontaneous-antiphase-to-in-p.pdf){target="_blank" style="color: inherit;"}
+
+- Maslovat D., Drummond NM., Carter MJ., & Carlsen AN. (2015). Reduced motor preparation during dual-task performance: Evidence from startle. *Experimental Brain Research*. ---
+[{{< ai doi >}}](https://doi.org/10.1007/s00221-015-4340-7){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2015_maslovat-etal_reduced-motor-preparation-during-dual-task-performance-evidence-from-startle.pdf){target="_blank" style="color: inherit;"}
+
+- Maslovat D., Drummond NM., Carter MJ., & Carlsen AN. (2015). Startle activation is additive with voluntary cortical activation irrespective of stimulus modality. *Neuroscience Letters*. ---
+[{{< ai doi >}}](https://doi.org/10.1016/j.neulet.2015.08.053){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2015_maslovat-etal_startle-activation-is-additive-with-voluntary-cortical-activation-irrespective-of-stimulus-modality.pdf){target="_blank" style="color: inherit;"}
+
+## 2014
+
+- Carter MJ., Carlsen AN., & Ste-Marie DM.
+(2014).
+Self-controlled feedback is effective if it is based on the learner’s performance: a replication and extension of Chiviacowsky and Wulf (2005).
+*Frontiers in Psychology*.
+---
+[{{< ai doi >}}](https://doi.org/10.3389/fpsyg.2014.01325){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2014_carter-etal_self-controlled-feedback-is-effective-if-it-is-based-on-the-learners-performance-a-replication-and-extension-of-chiviacow.pdf){target="_blank" style="color: inherit;"}
+
+- Maslovat D., Carter MJ., Kennefick M., & Carlsen AN. (2014). Startle neural activity is additive with normal cortical initiation-related activation. *Neuroscience Letters*. ---
+[{{< ai doi >}}](https://doi.org/10.1016/j.neulet.2013.11.009){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2014_maslovat-etal_startle-neural-activity-is-additive-with-normal-cortical-initiation-related-activation.pdf){target="_blank" style="color: inherit;"}
+
+## 2013
+
+- Bajema MC., MacKinnon CD., Carter MJ., Kennefick M., Perlmutter S., & Carlsen AN. (2013). Pause time alters the preparation of two-component movements. *Experimental Brain Research*. ---
+[{{< ai doi >}}](https://doi.org/10.1007/s00221-013-3670-6){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2013_bajema-etal_pause-time-alters-the-preparation-of-two-component-movements.pdf){target="_blank" style="color: inherit;"}
+
+- Patterson JT., Carter MJ., & Hansen S. (2013). Self-controlled KR schedules: Does repetition order matter?. *Human Movement Science*. ---
+[{{< ai doi >}}](https://doi.org/10.1016/j.humov.2013.03.005){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2013_patterson-etal_self-controlled-kr-schedules-does-repetition-order-matter.pdf){target="_blank" style="color: inherit;"}
+
+## 2012
+
+- Carter MJ. & Patterson JT. (2012). Self-controlled knowledge of results: Age-related differences in motor learning, strategies, and error detection. *Human Movement Science*. ---
+[{{< ai doi >}}](https://doi.org/10.1016/j.humov.2012.07.008){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2012_carter-patterson_self-controlled-knowledge-of-results-age-related-differences-in-motor-learning,-strategies,-and-error-detection.pdf){target="_blank" style="color: inherit;"}
+
+## 2011
+
+- Patterson JT., Carter MJ., & Sanli E.
+(2011).
+Decreasing the proportion of self-control trials during the acquisition period does not compromise the learning advantages in a self-controlled context.
+*Research Quarterly for Exercise and Sport*.
+---
+[{{< ai doi >}}](https://doi.org/10.1080/02701367.2011.10599799){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2011_patterson-etal_decreasing-the-proportion-of-self-control-trials-during-the-acquisition-period-does-not-compromise-t.pdf){target="_blank" style="color: inherit;"}
+
+## 2010
+
+- Patterson JT. & Carter MJ. (2010). Learner regulated knowledge of results during the acquisition of multiple timing goals. *Human Movement Science*. ---
+[{{< ai doi >}}](https://doi.org/10.1016/j.humov.2009.12.003){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2010_patterson-carter_learner-regulated-knowledge-of-results-during-the-acquisition-of-multiple-timing-goals.pdf){target="_blank" style="color: inherit;"}

### 2025-01-17 team.qmd
site and layout updates

@@
 toc: false
-listing:
-  - id: senior
-    contents: "team/senior/*.qmd"
-    type: grid
-    image-height: 225px
-    grid-columns: 3
-    fields: 
-      - image
-      - title
-      - subtitle
-    sort: sortby
-    field-display-names: 
-      started: "Started"
-  - id: junior
-    contents: "team/junior/*.qmd"
-    type: grid
-    image-height: 225px
-    grid-columns: 3
-    fields: 
-      - image
-      - title
-      - subtitle
-    sort: sortby
-    field-display-names: 
-      started: "Started"
 ---
 
-## Senior members
+<style>
+.team-member {
+  display: flex;
+  align-items: center;
+  padding: 20px; /* Add padding around each team member */
+  border: 1px solid #ddd; /* Optional: Add a border for better visual separation */
+  margin-bottom: 20px; /* Add space between each team member */
+}
 
-:::{#senior}
-:::
+.team-img {
+  margin-right: 20px;
+  width: 175px; /* Set the desired width */
+  height: 175px; /* Set the desired height */
+  border-radius: 50%; /* Make the image rounded */
+  object-fit: cover; /* Ensure the image covers the area */
+}
 
-## Junior members
+.team-info {
+  display: flex;
+  flex-direction: column;
+}
+</style>
 
-:::{#junior}
-:::
+<div class="team-member">
+  <img src="images/mike-carter.jpg" alt="images/mike-carter.jpg" class="team-img">
+  <div class="team-info">
+  <h4> Mike Carter, Ph.D. </h4>
+  <p> Assistant Professor | Principal Investigator </p>
+  <p> cartem11 [at] mcmaster [dot] ca </p>
+  </div>
+</div>
+
+<div class="team-member">
+  <img src="images/jack-tang.jpg" alt="images/jack-tang.jpg" class="team-img">
+  <div class="team-info">
+  <h4> Jiaqiao Tang, M.Sc.PT </h4>
+  <p> Ph.D. Student </p>
+  <p> tangj24 [at] mcmaster [dot] ca</p>
+  </div>
+</div>
+
+<div class="team-member">
+  <img src="images/mikayla-lalli.jpg" alt="images/mikayla-lalli.jpg" class="team-img">
+  <div class="team-info">
+  <h4> Mikayla Lalli, M.Sc. </h4>
+  <p> Ph.D. Student </p>
+  <p> lallim1 [at] mcmaster [dot] ca </p>
+  </div>
+</div>
+
+<div class="team-member">
+  <img src="images/nour-al-afif.jpg" alt="images/nour-al-afif.jpg" class="team-img">
+  <div class="team-info">
+  <h4> Nour Al Afif, M.Sc. </h4>
+  <p> Ph.D. Student </p>
+  <p> alafin1 [at] mcmaster [dot] ca </p>
+  </div>
+</div>
+
+<div class="team-member">
+  <img src="images/daniel-deletsu.jpg" alt="images/nour-alfif.jpg" class="team-img">
+  <div class="team-info">
+  <h4> Daniel Deletsu, B.Sc. </h4>
+  <p> M.Sc. Student </p>
+  <p> deletsud [at] mcmaster [dot] ca </p>
+  </div>
+</div>
 
@@
 
+**Mikayla Lalli**, M.Sc. Kinesiology (2022-24); *Ph.D. student in the lab*.  
+**Nour Al Afif**, M.Sc. Kinesiology (2022-24); *Ph.D. student in the lab*  
 **Laura St. Germain**, Ph.D. Kinesiology (2018-23); *Research and Data Specialist at Sheridan College*  

### 2025-01-19 team.qmd
update team info

@@
   align-items: center;
-  padding: 20px; /* Add padding around each team member */
-  border: 1px solid #ddd; /* Optional: Add a border for better visual separation */
-  margin-bottom: 20px; /* Add space between each team member */
+  padding: 20px; 
+  border: 1px solid #ddd;
+  margin-bottom: 20px;
 }
@@
   margin-right: 20px;
-  width: 175px; /* Set the desired width */
-  height: 175px; /* Set the desired height */
-  border-radius: 50%; /* Make the image rounded */
-  object-fit: cover; /* Ensure the image covers the area */
+  width: 175px;
+  height: 175px;
+  border-radius: 50%;
+  object-fit: cover;
 }
@@
 <div class="team-member">
-  <img src="images/daniel-deletsu.jpg" alt="images/nour-alfif.jpg" class="team-img">
+  <img src="images/daniel-deletsu.jpg" alt="images/daniel-deletsu.jpg" class="team-img">
   <div class="team-info">
@@
   <p> deletsud [at] mcmaster [dot] ca </p>
+  </div>
+</div>
+
+<div class="team-member">
+  <img src="images/lab-logo.png" alt="images/" class="team-img">
+  <div class="team-info">
+  <h4> Andrea Albert Pravin </h4>
+  <p> Undergraduate thesis student </p>
+  <p> BIOLOGY 4C12 </p>
+  </div>
+</div>
+
+<div class="team-member">
+  <img src="images/lab-logo.png" alt="images/" class="team-img">
+  <div class="team-info">
+  <h4> Faris Almoni </h4>
+  <p> Undergraduate practicum student </p>
+  <p> LIFESCI 4A03 </p>
+  </div>
+</div>
+
+<div class="team-member">
+  <img src="images/lab-logo.png" alt="images/" class="team-img">
+  <div class="team-info">
+  <h4> Gaile Cheng </h4>
+  <p> Undergraduate practicum student </p>
+  <p> SCIENCE 2RP3 </p>
+  </div>
+</div>
+
+<div class="team-member">
+  <img src="images/michael-croteau.jpg" alt="images/michael-croteau.jpg" class="team-img">
+  <div class="team-info">
+  <h4> Michael Croteau </h4>
+  <p> Undergraduate thesis student </p>
+  <p> NEUROSCI 4L12 A/B </p>
+  </div>
+</div>
+
+<div class="team-member">
+  <img src="images/lab-logo.png" alt="images/" class="team-img">
+  <div class="team-info">
+  <h4> Enuri Dissanayake </h4>
+  <p> Undergraduate thesis student </p>
+  <p> LIFESCI 4C12 </p>
+  </div>
+</div>
+
+<div class="team-member">
+  <img src="images/lab-logo.png" alt="images/" class="team-img">
+  <div class="team-info">
+  <h4> Leo Ducharme </h4>
+  <p> Undergraduate thesis student </p>
+  <p> PNB 4D06 </p>
+  </div>
+</div>
+
+<div class="team-member">
+  <img src="images/lab-logo.png" alt="images/" class="team-img">
+  <div class="team-info">
+  <h4> Tara Esbati </h4>
+  <p> Undergraduate project student </p>
+  <p> PNB 3QQ3 </p>
+  </div>
+</div>
+
+<div class="team-member">
+  <img src="images/lab-logo.png" alt="images/" class="team-img">
+  <div class="team-info">
+  <h4> Shiuli Khanna </h4>
+  <p> Undergraduate thesis student </p>
+  <p> NEUROSCI 4L12 A/B </p>
+  </div>
+</div>
+
+<div class="team-member">
+  <img src="images/lab-logo.png" alt="images/" class="team-img">
+  <div class="team-info">
+  <h4> Linsea Martin </h4>
+  <p> Undergraduate project student </p>
+  <p> PNB 3QQ3 </p>
+  </div>
+</div>
+
+<div class="team-member">
+  <img src="images/courtney-nguyen.jpg" alt="images/" class="team-img">
+  <div class="team-info">
+  <h4> Courtney Nguyen </h4>
+  <p> Undergraduate thesis student </p>
+  <p> HTHSCI 4A15 </p>
+  </div>
+</div>
+
+<div class="team-member">
+  <img src="images/shiv-peshwa.jpg" alt="images/" class="team-img">
+  <div class="team-info">
+  <h4> Shiv Peshwa </h4>
+  <p> Undergraduate practicum student </p>
+  <p> KINESIOL 3RP3 </p>
+  </div>
+</div>
+
+<div class="team-member">
+  <img src="images/lab-logo.png" alt="images/" class="team-img">
+  <div class="team-info">
+  <h4> Dana Rugole </h4>
+  <p> Undergraduate research assistant </p>
+  <p> Volunteer (Biochemistry) </p>
+  </div>
+</div>
+
+<div class="team-member">
+  <img src="images/lab-logo.png" alt="images/" class="team-img">
+  <div class="team-info">
+  <h4> Nicole Su </h4>
+  <p> Undergraduate thesis student </p>
+  <p> BIOLOGY 4C12 </p>
+  </div>
+</div>
+
+<div class="team-member">
+  <img src="images/vida-sussman.jpg" alt="images/" class="team-img">
+  <div class="team-info">
+  <h4> Vida Sussman </h4>
+  <p> Undergraduate project student </p>
+  <p> PNB 3QQ3 </p>
+  </div>
+</div>
+
+<div class="team-member">
+  <img src="images/eshaa-tariq.jpg" alt="images/" class="team-img">
+  <div class="team-info">
+  <h4> Eshaa Tariq </h4>
+  <p> Undergraduate research assistant </p>
+  <p> Volunteer (Kinesiology) </p>
+  </div>
+</div>
+
+<div class="team-member">
+  <img src="images/eleanore-wu.png" alt="images/" class="team-img">
+  <div class="team-info">
+  <h4> Eleanore Wu </h4>
+  <p> Undergraduate research assistant </p>
+  <p> Volunteer (Kinesiology) </p>
+  </div>
+</div>
+
+<div class="team-member">
+  <img src="images/jacqueline-zheng.jpg" alt="images/" class="team-img">
+  <div class="team-info">
+  <h4> Jacqueline Zheng </h4>
+  <p> Undergraduate thesis student </p>
+  <p> NEUROSCI 4L09 </p>
+  </div>
+</div>
+
+<div class="team-member">
+  <img src="images/headshot_duck-bryan.jpg" alt="images/headshot_duck-bryan.jpg" class="team-img">
+  <div class="team-info">
+  <h4> Duck Bryan </h4>
+  <p> Lab duck </p>
+  </div>
+</div>
+
+<div class="team-member">
+  <img src="images/headshot_duck-joy.jpg" alt="images/headshot_duck-joy.jpg" class="team-img">
+  <div class="team-info">
+  <h4> Duck Joy </h4>
+  <p> Lab duck </p>
+  </div>
+</div>
+
+<div class="team-member">
+  <img src="images/headshot_duck-norris.jpg" alt="images/headshot_duck-norris.jpg" class="team-img">
+  <div class="team-info">
+  <h4> Duck Norris </h4>
+  <p> Lab duck </p>
+  </div>
+</div>
+
+<div class="team-member">
+  <img src="images/headshot_ducky-parton.jpg" alt="images/headshot_ducky-parton.jpg" class="team-img">
+  <div class="team-info">
+  <h4> Ducky Parton </h4>
+  <p> Lab duck </p>
+  </div>
+</div>
+
+<div class="team-member">
+  <img src="images/headshot_lil-quack.jpg" alt="images/headshot_lil-quack.jpg" class="team-img">
+  <div class="team-info">
+  <h4> Lil Quack </h4>
+  <p> Lab duck </p>
   </div>
@@
 [Brad Mckay](https://bradmckay-motor-meta.netlify.app/) | Milwaukee Brewers  
+[Jonathan Cannon](https://metre.mcmaster.ca/) | Department of Psychology, Neuroscience, and Behaviour, McMaster University
 
@@
 
-Jacqueline Zheng (2023-24); Abby Girouard (2023-24); Michael Croteau (2024); Aditya Trivedi (2024); Navishka Brahmbhatt (2024); Francesca Caputo (2024); Jil Soni (2024); Enuri Dissanayake (2023); Jeswende Seedu (2022-23); Vivian Li (2022); Caroline Jarvi (2022); Gurlal Gill (2021); Anita Chaseendran (2021); Gianna Jeyarajan (2021); Mackenzie (Kenzie) Bell (2021); Ashton Yuen (2021); Charlie Violin (2021); Ammaar Jan (2020); Faran Chaudhry (2020); Yu (Sarah) Fu (2020); Andrew Poskus (2019); Maya El-Zahed (2019); Grant Yang (2019); Olena Leshchyshen (2019); Rita Waseem (2019); Christian Kleiser (2018); Christopher Li (2018); Faryal Zahir (2018)
+Aashna Gujral (2024); Dami Alabi Benson (2024); Jacqueline Zheng (2023-24); Abby Girouard (2023-24); Michael Croteau (2024); Aditya Trivedi (2024); Navishka Brahmbhatt (2024); Francesca Caputo (2024); Jil Soni (2024); Enuri Dissanayake (2023); Jeswende Seedu (2022-23); Vivian Li (2022); Caroline Jarvi (2022); Gurlal Gill (2021); Anita Chaseendran (2021); Gianna Jeyarajan (2021); Mackenzie (Kenzie) Bell (2021); Ashton Yuen (2021); Charlie Violin (2021); Ammaar Jan (2020); Faran Chaudhry (2020); Yu (Sarah) Fu (2020); Andrew Poskus (2019); Maya El-Zahed (2019); Grant Yang (2019); Olena Leshchyshen (2019); Rita Waseem (2019); Christian Kleiser (2018); Christopher Li (2018); Faryal Zahir (2018)
 

### 2025-01-20 team.qmd
upload headshots

@@
 <div class="team-member">
-  <img src="images/lab-logo.png" alt="images/" class="team-img">
+  <img src="images/tara-esbati.jpg" alt="images/tara-esbati.jpg" class="team-img">
   <div class="team-info">
@@
 <div class="team-member">
-  <img src="images/lab-logo.png" alt="images/" class="team-img">
+  <img src="images/nicole-su.jpg" alt="images/nicole-su.jpg" class="team-img">
   <div class="team-info">
@@
 
-Aashna Gujral (2024); Dami Alabi Benson (2024); Jacqueline Zheng (2023-24); Abby Girouard (2023-24); Michael Croteau (2024); Aditya Trivedi (2024); Navishka Brahmbhatt (2024); Francesca Caputo (2024); Jil Soni (2024); Enuri Dissanayake (2023); Jeswende Seedu (2022-23); Vivian Li (2022); Caroline Jarvi (2022); Gurlal Gill (2021); Anita Chaseendran (2021); Gianna Jeyarajan (2021); Mackenzie (Kenzie) Bell (2021); Ashton Yuen (2021); Charlie Violin (2021); Ammaar Jan (2020); Faran Chaudhry (2020); Yu (Sarah) Fu (2020); Andrew Poskus (2019); Maya El-Zahed (2019); Grant Yang (2019); Olena Leshchyshen (2019); Rita Waseem (2019); Christian Kleiser (2018); Christopher Li (2018); Faryal Zahir (2018)
+Aashna Gujral (2024); Dami Alabi Benson (2024); Michael Croteau (2024); Francesca Caputo (2024); Jil Soni (2024); Navishka Brahmbhatt (2024); Aditya Trivedi (2024); Jacqueline Zheng (2023-24); Abby Girouard (2023-24); Michael Croteau (2024); Aditya Trivedi (2024); Navishka Brahmbhatt (2024); Francesca Caputo (2024); Jil Soni (2024); Enuri Dissanayake (2023); Jeswende Seedu (2022-23); Vivian Li (2022); Caroline Jarvi (2022); Gurlal Gill (2021); Anita Chaseendran (2021); Gianna Jeyarajan (2021); Mackenzie (Kenzie) Bell (2021); Ashton Yuen (2021); Charlie Violin (2021); Ammaar Jan (2020); Faran Chaudhry (2020); Yu (Sarah) Fu (2020); Andrew Poskus (2019); Maya El-Zahed (2019); Grant Yang (2019); Olena Leshchyshen (2019); Rita Waseem (2019); Christian Kleiser (2018); Christopher Li (2018); Faryal Zahir (2018)
 
@@
 
-Elizabeth Mitchell (2020-23); Celeste de Faveri (2021-23); Lidia Barbera (2022-23); Hibaa Hasan (2022-23); Faith Adams (2022); Chitrini Tandon (2021-22); Kristen Arnold (2021-22); Alison Williams (2018-20); Andrew Poskus (2019); Kevin Gilotra (2019); Ashton Yuen (2019); Mackenzie (Kenzie) Bell (2019-21); Olena Leshchyshen (2018-19); Yu (Sarah) Fu (2018-19)
+Vida Sussman (2022-24); Elizabeth Mitchell (2020-23); Celeste de Faveri (2021-23); Lidia Barbera (2022-23); Hibaa Hasan (2022-23); Faith Adams (2022); Chitrini Tandon (2021-22); Kristen Arnold (2021-22); Alison Williams (2018-20); Andrew Poskus (2019); Kevin Gilotra (2019); Ashton Yuen (2019); Mackenzie (Kenzie) Bell (2019-21); Olena Leshchyshen (2018-19); Yu (Sarah) Fu (2018-19)

### 2025-01-20 index.qmd
open application period

@@
 
-<font color="#d08770">[October 21 2024].</font> **New milestone**.
-Congratulations to Nour Al Afif on successfully defending her MSc work.
-We are excited that Nour is staying in the lab for her doctoral studies.
-
-<font color="#d08770">[September 18 2024].</font> **Paper accepted**.
-Roth, A.M., Buggeln, J.H., Hoh, J., Woods, J.M., Sullivan, S.R., Ngo, T., Calalo, J.A., Lokesh, R., Morton, S.M., Grill, S., Jeka, J.J., Carter, M.J., & Cashaback, J.G.A.
-Roles and interplay of reinforcement-based and error-based processes during reaching and gait in neurotypical adults and individuals with Parkinson's disease.
-*PLoS Computational Biology*.
-
-<font color="#d08770">[September 05 2024].</font> **New milestone**.
-Congratulations to Mikayla Lalli on successfully defending her MSc work.
-We are excited that Mikayla is staying in the lab for her doctoral studies.
-
-<font color="#d08770">[September 03 2024].</font> **Paper accepted**.
-St.
-Germain, L., McKay, B., Barbera, L., Tandon, C., Seedu, J., Carrillo, C., Brown, B.M.Y., & Carter, M.J.
-Autonomy-supportive instructional language does not enhance skill acquisition compared to controlling instructional language.
-*Psychological Research*.
+<font color="#d08770">[January 20 2025].</font> **Announcement**.
+The application period is now open for students interested in a practicum, project, thesis, or volunteer position in the lab for the 2025-26 academic year.
+Please see [https://cartermaclab.org/join](https://cartermaclab.org/join) for details.

### 2025-01-20 join.qmd
open application period

@@
 
-If you are interested in joining the team, please email your completed [application form](https://raw.githubusercontent.com/cartermaclab/lab-website/master/files/2024_carterlab_undergraduate-application-form.pdf){target="_blank"}, an up-to-date curriculum vitae, and unofficial transcripts to cartem11@mcmaster.ca.
+If you are interested in joining the team, please email your completed [application form](https://raw.githubusercontent.com/cartermaclab/lab-website/master/files/2024_carterlab_undergraduate-application-form.pdf){target="_blank"}, an up-to-date curriculum vitae, and unofficial transcripts to motorlab [at] mcmaster [dot] ca.
 
-**The application period for practicum, project, and thesis courses for the 2024-25 academic year is now closed.**
+<font color="#d08770">**The application period is now open for students interested in a practicum, project, thesis, or volunteer position in the lab for the 2025-26 academic year.**</font>
 
-Please be aware that volunteer research assistant positions are filled on a rolling basis and as needed.
+- Applications will be received until Friday, February 28, 2025
+- Applicants selected for an interview will be notified by Friday, March 7, 2025
+- Interviews will take place in mid-to-late March
+- Offers for a practicum, project, or thesis position in the lab will be sent to selected students by Monday, March 31, 2025
+
+Please be aware that volunteer research assistant positions are also filled on a rolling basis and as needed.
 
@@
 If you are interested in completing your M.Sc or Ph.D in the lab, please email Dr.
-Carter (cartem11@mcmaster.ca) an up-to-date curriculum vitae, unofficial academic transcripts, and a 1-page statement of research interests.
+Carter (cartem11 [at] mcmaster [dot] ) an up-to-date curriculum vitae, unofficial academic transcripts, and a 1-page statement of research interests.

### 2025-01-21 join.qmd
change text placement
change contact email

@@
 
-If you are interested in joining the team, please email your completed [application form](https://raw.githubusercontent.com/cartermaclab/lab-website/master/files/2024_carterlab_undergraduate-application-form.pdf){target="_blank"}, an up-to-date curriculum vitae, and unofficial transcripts to motorlab [at] mcmaster [dot] ca.
-
 <font color="#d08770">**The application period is now open for students interested in a practicum, project, thesis, or volunteer position in the lab for the 2025-26 academic year.**</font>
@@
 - Offers for a practicum, project, or thesis position in the lab will be sent to selected students by Monday, March 31, 2025
+
+If you are interested in joining the team, please email your completed [application form](https://raw.githubusercontent.com/cartermaclab/lab-website/master/files/2024_carterlab_undergraduate-application-form.pdf){target="_blank"}, an up-to-date curriculum vitae, and unofficial transcripts to cartem11 [at] mcmaster [dot] ca.
+Incomplete applications will not be reviewed.
 

### 2025-01-21 join.qmd
fix contact and add general inquiry info

--- 2025-01-20 join.qmd
@@
 
-Please be aware that volunteer research assistant positions are also filled on a rolling basis and as needed.
+If you are interested in joining the team, please email your completed [application form](https://raw.githubusercontent.com/cartermaclab/lab-website/master/files/2024_carterlab_undergraduate-application-form.pdf){target="_blank"}, an up-to-date curriculum vitae, and unofficial transcripts to motorlab [at] mcmaster [dot] ca.
+*Incomplete applications will not be reviewed.*
+
+General inquiries regarding undergraduate opportunities in the lab can be sent to cartem11 [at] mcmaster [dot] ca.
 
@@
 
-If you are interested in completing your M.Sc or Ph.D in the lab, please email Dr.
-Carter (cartem11 [at] mcmaster [dot] ) an up-to-date curriculum vitae, unofficial academic transcripts, and a 1-page statement of research interests.
+If you are interested in completing your M.Sc or Ph.D in the lab, please send 1) an up-to-date curriculum vitae, 2) unofficial academic transcripts, and 3) a 1-page statement of research interests to cartem11 [at] mcmaster [dot] ca.

### 2025-01-21 join.qmd
add summer award opportunities

@@
 
-General inquiries regarding undergraduate opportunities in the lab can be sent to cartem11 [at] mcmaster [dot] ca.
+General inquiries regarding other undergraduate opportunities in the lab such as NSERC USRA, Kinesiology Summer Research Award, MIRA Summer Research Fellowship, etc can be sent to cartem11 [at] mcmaster [dot] ca.
 

### 2025-01-27 papers.qmd
fix typos and add in press heading

@@
 
+## In Press
+
+- McKay B., Bacelar MFB., Parma JO., Miller MW., & Carter, MJ.
+(2023).
+The combination of reporting bias and underpowered study designs has substantially exaggerated the motor learning benefits of self-controlled practice and enhanced expectancies: A meta-analysis.
+*International Review of Sport and Exercise Psychology*.
+---
+[{{< ai doi >}}](https://doi.org/10.1080/1750984X.2023.2207255){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2023_mckay-etal_the-combination-of-reporting-bias-and-underpowered-study-designs-has-substantially-exaggerated-the-motor-learning-benefits-of.pdf){target="_blank" style="color: inherit;"}
+[{{< fa brands github >}}](https://github.com/cartermaclab/proj_sc-ee-optimal-theory){target="_blank" style="color: inherit;"}
+
 ## 2025
@@
 - St.
-Germain L., McKay B., Tandon C., Seedu J., Barbera L., Carrillo C., Brown D.M.Y., & Carter, MJ.
+Germain L., McKay B., Tandon C., Seedu J., Barbera L., Carrillo C., Brown DMY., & Carter, MJ.
 (2025).
@@
 (2024).
-Roles and interplay of reinforcement-based and error-based processes during reaching and gait in neurotypical adults and individuals with Parkinson’s disease *PLoS Computational Biology*.
+Roles and interplay of reinforcement-based and error-based processes during reaching and gait in neurotypical adults and individuals with Parkinson’s disease.
+*PLoS Computational Biology*.
 ---
@@
 ## 2023
-
-- McKay B., Bacelar MFB., Parma JO., Miller MW., & Carter, MJ.
-(2023).
-The combination of reporting bias and underpowered study designs has substantially exaggerated the motor learning benefits of self-controlled practice and enhanced expectancies: A meta-analysis.
-*International Review of Sport and Exercise Psychology*.
----
-[{{< ai doi >}}](https://doi.org/10.1080/1750984X.2023.2207255){target="_blank" style="color: inherit;"}
-[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2023_mckay-etal_the-combination-of-reporting-bias-and-underpowered-study-designs-has-substantially-exaggerated-the-motor-learning-benefits-of.pdf){target="_blank" style="color: inherit;"}
-[{{< fa brands github >}}](https://github.com/cartermaclab/proj_sc-ee-optimal-theory){target="_blank" style="color: inherit;"}
 
@@
 - Ste-Marie DM., Carter MJ., & Yantha ZD.
-(2020).
+(2019).
 Self-controlled learning: Current findings, theoretical perspectives, and future directions.

### 2025-01-27 team.qmd
update images

@@
 <div class="team-member">
-  <img src="images/lab-logo.png" alt="images/" class="team-img">
+  <img src="images/leo-ducharme.jpg" alt="images/leo-ducharme.jpg" class="team-img">
   <div class="team-info">
@@
 <div class="team-member">
-  <img src="images/lab-logo.png" alt="images/" class="team-img">
+  <img src="images/linsea-martin.jpg" alt="images/linsea-martin.jpg" class="team-img">
   <div class="team-info">
@@
 <div class="team-member">
-  <img src="images/lab-logo.png" alt="images/" class="team-img">
+  <img src="images/dana-rugole.jpg" alt="images/dana-rugole.jpg" class="team-img">
   <div class="team-info">

### 2025-02-04 team.qmd
minor updates

@@
 <div class="team-member">
-  <img src="images/lab-logo.png" alt="images/" class="team-img">
+  <img src="images/andrea-albert-pravin.jpg" alt="images/andrea-albert-pravin.jpg" class="team-img">
   <div class="team-info">
@@
 <div class="team-member">
-  <img src="images/lab-logo.png" alt="images/" class="team-img">
+  <img src="images/faris-almoni.jpg" alt="images/faris-almoni.jpg" class="team-img">
   <div class="team-info">
@@
 <div class="team-member">
-  <img src="images/lab-logo.png" alt="images/" class="team-img">
+  <img src="images/shiuli-khanna.jpg" alt="images/shiuli-khanna.jpg" class="team-img">
   <div class="team-info">

### 2025-03-26 index.qmd
render site

@@
 
+<font color="#d08770">[March 03 2025].</font> **New Preprint**.
+Lalli, M., Al Afif, N., Tang, J., Hasan, H., Dissanayake, E., Sussman, V., Lokesh, R., Rathwell, S., Cashaback, J.G.A., & Carter, M.J.
+Preferences for costly cooperation are highly individualized.
+*PsyAr$\chi$iv*.
+[https://doi.org/10.31234/osf.io/3qaeu_v3](https://doi.org/10.31234/osf.io/3qaeu_v3){target="_blank"}
+
 <font color="#d08770">[January 20 2025].</font> **Announcement**.

### 2025-03-26 news.qmd
open application period
render site

@@
 ---
-title: "Lab News"
+title: "Past Lab News"
 pagetitle: "CarterLab | News"
@@
 ---
+
+<font color="#d08770">[March 03 2025].</font> **New Preprint**.
+Lalli, M., Al Afif, N., Tang, J., Hasan, H., Dissanayake, E., Sussman, V., Lokesh, R., Rathwell, S., Cashaback, J.G.A., & Carter, M.J.
+Preferences for costly cooperation are highly individualized.
+*PsyAr$\chi$iv*.
+[https://doi.org/10.31234/osf.io/3qaeu_v3](https://doi.org/10.31234/osf.io/3qaeu_v3){target="_blank"}
+
+<font color="#d08770">[January 20 2025].</font> **Announcement**.
+The application period is now open for students interested in a practicum, project, thesis, or volunteer position in the lab for the 2025-26 academic year.
+Please see [https://cartermaclab.org/join](https://cartermaclab.org/join) for details.
 

### 2025-04-22 index.qmd
update ugrad positions

@@
 
+<font color="#d08770">[April 22 2025].</font> **Announcement**. The application period for practicum, project, or thesis positions in the lab for the 2025-26 academic year is now closed.
+
 <font color="#d08770">[March 03 2025].</font> **New Preprint**.
@@
 [https://doi.org/10.31234/osf.io/3qaeu_v3](https://doi.org/10.31234/osf.io/3qaeu_v3){target="_blank"}
-
-<font color="#d08770">[January 20 2025].</font> **Announcement**.
-The application period is now open for students interested in a practicum, project, thesis, or volunteer position in the lab for the 2025-26 academic year.
-Please see [https://cartermaclab.org/join](https://cartermaclab.org/join) for details.

### 2025-04-22 join.qmd
update ugrad positions

@@
 
-<font color="#d08770">**The application period is now open for students interested in a practicum, project, thesis, or volunteer position in the lab for the 2025-26 academic year.**</font>
+<font color="#d08770">**The application period is for practicum, project, or thesis positions in the lab for the 2025-26 academic year is now closed.**</font>
 
-- Applications will be received until Friday, February 28, 2025
-- Applicants selected for an interview will be notified by Friday, March 7, 2025
-- Interviews will take place in mid-to-late March
-- Offers for a practicum, project, or thesis position in the lab will be sent to selected students by Monday, March 31, 2025
-
+<!--
 If you are interested in joining the team, please email your completed [application form](https://raw.githubusercontent.com/cartermaclab/lab-website/master/files/2024_carterlab_undergraduate-application-form.pdf){target="_blank"}, an up-to-date curriculum vitae, and unofficial transcripts to motorlab [at] mcmaster [dot] ca.
 *Incomplete applications will not be reviewed.*
+-->
 

### 2025-05-14 index.qmd
updates to multiple pages

@@
 
+<font color="#d08770">[May 14 2024].</font> **Paper accepted**.
+Sullivan SR, Lokesh R, Peters CS, Calalo J, Roth AR, Buggeln JH, Ngo TT, Carter MJ, & Cashaback JGA.
+(Accepted).
+Indecision under time pressure arises from suboptimal switching behaviour.
+*Journal of Neurophysiology*.
+
 <font color="#d08770">[April 22 2025].</font> **Announcement**. The application period for practicum, project, or thesis positions in the lab for the 2025-26 academic year is now closed.
@@
 <font color="#d08770">[March 03 2025].</font> **New Preprint**.
-Lalli, M., Al Afif, N., Tang, J., Hasan, H., Dissanayake, E., Sussman, V., Lokesh, R., Rathwell, S., Cashaback, J.G.A., & Carter, M.J.
+Lalli M, Al Afif N, Tang J, Hasan H, Dissanayake E, Sussman V, Lokesh R, Rathwell S, Cashaback JGA, & Carter MJ.
 Preferences for costly cooperation are highly individualized.

### 2025-05-14 papers.qmd
minor updates
render site
updates to multiple pages

@@
 ---
-title: "Papers"
+title: ""
 pagetitle: "CarterLab | Papers"
@@
 ## Preprints
+
+- Lalli, M., Al Afif, N., Tang, J., Hasan, H., Dissanayake, E., Sussman, V., Lokesh, R., Rathwell, S., Cashaback, JGA., & Carter, MJ.
+Preferences for costly cooperation are highly individualized.
+*PsyAr$\chi$iv*.
+--- [{{< ai doi >}}](https://doi.org/10.31234/osf.io/3qaeu_v3){target="_blank" style="color: inherit;"}
 
@@
 - McKay B., Bacelar MFB., Parma JO., Miller MW., & Carter, MJ.
-(2023).
 The combination of reporting bias and underpowered study designs has substantially exaggerated the motor learning benefits of self-controlled practice and enhanced expectancies: A meta-analysis.

### 2025-05-14 teaching.qmd
updates to multiple pages

@@
 ---
-title: "Teaching"
+title: ""
 pagetitle: "CarterLab | Teaching"
@@
 
-Updates in progress...
+```{r}
+#| echo: false
+
+library(markdown)
+library(tinytable)
+
+tibble::tibble(
+    `FALL 2025` = c(
+        "Motor Control and Learning (KINESIOL 2MC3)...*Coming soon*",
+        "Neurorehabilitation and Robotics (KINESIOL 4TT3)...*Coming soon*",
+        "Scientific Computing for Reproducible Science (KINESIOL 736)...*Coming soon*"
+        )
+) |> 
+    tt(width = 1) |> 
+    group_tt(i = list(
+        "Undergraduate courses" = 1,
+        "Graduate courses" = 3
+    )) |> 
+    format_tt(j = 1, markdown = TRUE) |> 
+    style_tt(i = 0, background = "#0077bb", color = "white") |> 
+    style_tt(i = c(1,4), background = "#eceff4", bold = TRUE)
+```

### 2025-05-14 team.qmd
updates to multiple pages

--- 2025-01-20 team.qmd
@@
   <h4> Daniel Deletsu, B.Sc. </h4>
-  <p> M.Sc. Student </p>
+  <p> M.Sc. Candidate </p>
   <p> deletsud [at] mcmaster [dot] ca </p>
-  </div>
-</div>
-
-<div class="team-member">
-  <img src="images/lab-logo.png" alt="images/" class="team-img">
-  <div class="team-info">
-  <h4> Andrea Albert Pravin </h4>
-  <p> Undergraduate thesis student </p>
-  <p> BIOLOGY 4C12 </p>
-  </div>
-</div>
-
-<div class="team-member">
-  <img src="images/lab-logo.png" alt="images/" class="team-img">
-  <div class="team-info">
-  <h4> Faris Almoni </h4>
-  <p> Undergraduate practicum student </p>
-  <p> LIFESCI 4A03 </p>
-  </div>
-</div>
-
-<div class="team-member">
-  <img src="images/lab-logo.png" alt="images/" class="team-img">
-  <div class="team-info">
-  <h4> Gaile Cheng </h4>
-  <p> Undergraduate practicum student </p>
-  <p> SCIENCE 2RP3 </p>
   </div>
@@
   <h4> Michael Croteau </h4>
-  <p> Undergraduate thesis student </p>
-  <p> NEUROSCI 4L12 A/B </p>
+  <p> M.Sc. Student </p>
+  <p> croteaum [at] mcmaster [dot] ca </p>
   </div>
@@
   <div class="team-info">
-  <h4> Enuri Dissanayake </h4>
-  <p> Undergraduate thesis student </p>
-  <p> LIFESCI 4C12 </p>
-  </div>
-</div>
-
-<div class="team-member">
-  <img src="images/lab-logo.png" alt="images/" class="team-img">
-  <div class="team-info">
-  <h4> Leo Ducharme </h4>
-  <p> Undergraduate thesis student </p>
-  <p> PNB 4D06 </p>
-  </div>
-</div>
-
-<div class="team-member">
-  <img src="images/tara-esbati.jpg" alt="images/tara-esbati.jpg" class="team-img">
-  <div class="team-info">
-  <h4> Tara Esbati </h4>
-  <p> Undergraduate project student </p>
-  <p> PNB 3QQ3 </p>
-  </div>
-</div>
-
-<div class="team-member">
-  <img src="images/lab-logo.png" alt="images/" class="team-img">
-  <div class="team-info">
-  <h4> Shiuli Khanna </h4>
-  <p> Undergraduate thesis student </p>
-  <p> NEUROSCI 4L12 A/B </p>
-  </div>
-</div>
-
-<div class="team-member">
-  <img src="images/lab-logo.png" alt="images/" class="team-img">
-  <div class="team-info">
-  <h4> Linsea Martin </h4>
-  <p> Undergraduate project student </p>
-  <p> PNB 3QQ3 </p>
-  </div>
-</div>
-
-<div class="team-member">
-  <img src="images/courtney-nguyen.jpg" alt="images/" class="team-img">
-  <div class="team-info">
-  <h4> Courtney Nguyen </h4>
-  <p> Undergraduate thesis student </p>
-  <p> HTHSCI 4A15 </p>
-  </div>
-</div>
-
-<div class="team-member">
-  <img src="images/shiv-peshwa.jpg" alt="images/" class="team-img">
-  <div class="team-info">
-  <h4> Shiv Peshwa </h4>
-  <p> Undergraduate practicum student </p>
-  <p> KINESIOL 3RP3 </p>
-  </div>
-</div>
-
-<div class="team-member">
-  <img src="images/lab-logo.png" alt="images/" class="team-img">
-  <div class="team-info">
-  <h4> Dana Rugole </h4>
-  <p> Undergraduate research assistant </p>
-  <p> Volunteer (Biochemistry) </p>
-  </div>
-</div>
-
-<div class="team-member">
-  <img src="images/nicole-su.jpg" alt="images/nicole-su.jpg" class="team-img">
-  <div class="team-info">
-  <h4> Nicole Su </h4>
-  <p> Undergraduate thesis student </p>
-  <p> BIOLOGY 4C12 </p>
-  </div>
-</div>
-
-<div class="team-member">
-  <img src="images/vida-sussman.jpg" alt="images/" class="team-img">
-  <div class="team-info">
-  <h4> Vida Sussman </h4>
-  <p> Undergraduate project student </p>
-  <p> PNB 3QQ3 </p>
-  </div>
-</div>
-
-<div class="team-member">
-  <img src="images/eshaa-tariq.jpg" alt="images/" class="team-img">
-  <div class="team-info">
-  <h4> Eshaa Tariq </h4>
-  <p> Undergraduate research assistant </p>
-  <p> Volunteer (Kinesiology) </p>
-  </div>
-</div>
-
-<div class="team-member">
-  <img src="images/eleanore-wu.png" alt="images/" class="team-img">
-  <div class="team-info">
-  <h4> Eleanore Wu </h4>
-  <p> Undergraduate research assistant </p>
-  <p> Volunteer (Kinesiology) </p>
-  </div>
-</div>
-
-<div class="team-member">
-  <img src="images/jacqueline-zheng.jpg" alt="images/" class="team-img">
-  <div class="team-info">
-  <h4> Jacqueline Zheng </h4>
-  <p> Undergraduate thesis student </p>
-  <p> NEUROSCI 4L09 </p>
+  <h4> Maria Alex </h4>
+  <p> Undergraduate Research Assistant </p>
+  <p> McMaster Institute for Research on Aging 2025 Summer Research Fellowship Winner </p>
   </div>
@@
 
-Lidia Barbera (2023-24); Hibaa Hasan (2023-24); Ola Schwarzenberg (2023-24); Mithun Manivannan (2023-24); Chitrini Tandon (2021-23); Alyssa Skouros (2022-23); Kiana Masoudi (2022-23); Raika Bourmand (2021-22); Armin Sariaslani (2021-22); Katharine (Katie) Douglas (2021-22); Thinzar Soe (2021-22); Julianna Marfisi (2020-21); Matthew Tobis (2020-21); Andrew Poskus (2020-21); Sherry Feldman (2019-20); Olena Leshchyshen (2019-20); Noura Balbaa (2019-20)
+Shiuli Khanna (2024-25); Michael Croteau (2024-25); Enuri Dissanayake (2024-25); Nicole Su (2024-25); Courtney Nguyen (2024-25); Leo Ducharm (2024-25); Andrea Albert Pravin (2024-25); Jacqueline Zhang (2024-25); Lidia Barbera (2023-24); Hibaa Hasan (2023-24); Ola Schwarzenberg (2023-24); Mithun Manivannan (2023-24); Chitrini Tandon (2021-23); Alyssa Skouros (2022-23); Kiana Masoudi (2022-23); Raika Bourmand (2021-22); Armin Sariaslani (2021-22); Katharine (Katie) Douglas (2021-22); Thinzar Soe (2021-22); Julianna Marfisi (2020-21); Matthew Tobis (2020-21); Andrew Poskus (2020-21); Sherry Feldman (2019-20); Olena Leshchyshen (2019-20); Noura Balbaa (2019-20)
 
@@
 
-Aashna Gujral (2024); Dami Alabi Benson (2024); Michael Croteau (2024); Francesca Caputo (2024); Jil Soni (2024); Navishka Brahmbhatt (2024); Aditya Trivedi (2024); Jacqueline Zheng (2023-24); Abby Girouard (2023-24); Michael Croteau (2024); Aditya Trivedi (2024); Navishka Brahmbhatt (2024); Francesca Caputo (2024); Jil Soni (2024); Enuri Dissanayake (2023); Jeswende Seedu (2022-23); Vivian Li (2022); Caroline Jarvi (2022); Gurlal Gill (2021); Anita Chaseendran (2021); Gianna Jeyarajan (2021); Mackenzie (Kenzie) Bell (2021); Ashton Yuen (2021); Charlie Violin (2021); Ammaar Jan (2020); Faran Chaudhry (2020); Yu (Sarah) Fu (2020); Andrew Poskus (2019); Maya El-Zahed (2019); Grant Yang (2019); Olena Leshchyshen (2019); Rita Waseem (2019); Christian Kleiser (2018); Christopher Li (2018); Faryal Zahir (2018)
+Vida Sussman (2024-25); Tara Esbati (2024-25); Shiv Peshwa (2025); Linsea Martin (2024-25); Faris Almoni (2025); Gaile Cheng (2025); Aashna Gujral (2024); Dami Alabi Benson (2024); Michael Croteau (2024); Francesca Caputo (2024); Jil Soni (2024); Navishka Brahmbhatt (2024); Aditya Trivedi (2024); Jacqueline Zheng (2023-24); Abby Girouard (2023-24); Michael Croteau (2024); Aditya Trivedi (2024); Navishka Brahmbhatt (2024); Francesca Caputo (2024); Jil Soni (2024); Enuri Dissanayake (2023); Jeswende Seedu (2022-23); Vivian Li (2022); Caroline Jarvi (2022); Gurlal Gill (2021); Anita Chaseendran (2021); Gianna Jeyarajan (2021); Mackenzie (Kenzie) Bell (2021); Ashton Yuen (2021); Charlie Violin (2021); Ammaar Jan (2020); Faran Chaudhry (2020); Yu (Sarah) Fu (2020); Andrew Poskus (2019); Maya El-Zahed (2019); Grant Yang (2019); Olena Leshchyshen (2019); Rita Waseem (2019); Christian Kleiser (2018); Christopher Li (2018); Faryal Zahir (2018)
 
@@
 
-Vida Sussman (2022-24); Elizabeth Mitchell (2020-23); Celeste de Faveri (2021-23); Lidia Barbera (2022-23); Hibaa Hasan (2022-23); Faith Adams (2022); Chitrini Tandon (2021-22); Kristen Arnold (2021-22); Alison Williams (2018-20); Andrew Poskus (2019); Kevin Gilotra (2019); Ashton Yuen (2019); Mackenzie (Kenzie) Bell (2019-21); Olena Leshchyshen (2018-19); Yu (Sarah) Fu (2018-19)
+Eshaa Tariq (2024-25); Eleanore Wu (2024-25); Shiv Peshwa (2024); Dana Rugole (2025); Vida Sussman (2022-24); Elizabeth Mitchell (2020-23); Celeste de Faveri (2021-23); Lidia Barbera (2022-23); Hibaa Hasan (2022-23); Faith Adams (2022); Chitrini Tandon (2021-22); Kristen Arnold (2021-22); Alison Williams (2018-20); Andrew Poskus (2019); Kevin Gilotra (2019); Ashton Yuen (2019); Mackenzie (Kenzie) Bell (2019-21); Olena Leshchyshen (2018-19); Yu (Sarah) Fu (2018-19)

### 2025-05-14 team.qmd
update team page

@@
 <div class="team-member">
-  <img src="images/lab-logo.png" alt="images/" class="team-img">
+  <img src="images/maria-alex.png" alt="images/" class="team-img">
   <div class="team-info">

### 2025-05-17 news.qmd
updates to multiple pages
add DOI

@@
 ---
+
+<font color="#d08770">[May 14 2024].</font> **Paper accepted**. Sullivan SR, Lokesh R, Peters CS, Calalo J, Roth AR, Buggeln JH, Ngo TT, Carter MJ, &
+Cashaback JGA.
+(In Press).
+Indecision under time pressure arises from suboptimal switching behaviour.
+*Journal of Neurophysiology*.
+[https://doi.org/10.1152/jn.00563.2024](https://doi.org/10.1152/jn.00563.2024){target="_blank"}
 

### 2025-05-17 papers.qmd
add DOI

@@
 
-- McKay B., Bacelar MFB., Parma JO., Miller MW., & Carter, MJ.
+- Sullivan SR., Lokesh R., Peters CS., Calalo J., Roth AR., Buggeln JH., Ngo TT., Carter MJ., & Cashaback JGA.
+(In Press).
+Indecision under time pressure arises from suboptimal switching behaviour.
+*Journal of Neurophysiology*.
+---
+[{{< ai doi >}}](https://doi.org/10.1152/jn.00563.2024){target="_blank" style="color: inherit;"}
+
+- McKay B., Bacelar MFB., Parma JO., Miller MW., & Carter MJ.
+(In Press).
 The combination of reporting bias and underpowered study designs has substantially exaggerated the motor learning benefits of self-controlled practice and enhanced expectancies: A meta-analysis.
@@
 - St.
-Germain L., McKay B., Tandon C., Seedu J., Barbera L., Carrillo C., Brown DMY., & Carter, MJ.
+Germain L., McKay B., Tandon C., Seedu J., Barbera L., Carrillo C., Brown DMY., & Carter MJ.
 (2025).

### 2025-05-28 papers.qmd
update paper info

@@
 
+## 2025
+
 - McKay B., Bacelar MFB., Parma JO., Miller MW., & Carter MJ.
-(In Press).
+(2025).
 The combination of reporting bias and underpowered study designs has substantially exaggerated the motor learning benefits of self-controlled practice and enhanced expectancies: A meta-analysis.
@@
 [{{< ai doi >}}](https://doi.org/10.1080/1750984X.2023.2207255){target="_blank" style="color: inherit;"}
-[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2023_mckay-etal_the-combination-of-reporting-bias-and-underpowered-study-designs-has-substantially-exaggerated-the-motor-learning-benefits-of.pdf){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2025_mckay-etal_the-combination-of-reporting-bias-and-underpowered-study-designs-has-substantially-exaggerated-the-motor-learning-benefits-of.pdf){target="_blank" style="color: inherit;"}
 [{{< fa brands github >}}](https://github.com/cartermaclab/proj_sc-ee-optimal-theory){target="_blank" style="color: inherit;"}
-
-## 2025
 

### 2025-06-24 papers.qmd
update and add link to file

@@
 
-- Calalo JA., Ngo TT., Sullivan SR., Strand K., Buggeln JH., Lokesh R., Roth AM., Carter MJ., Kurtzer IL., & Cashaback JGA. (2024). Online movements reflect ongoing deliberation. *bioR$\chi$iv*. ---
-[{{< ai doi >}}](https://doi.org/10.1101/2024.08.19.608669){target="_blank" style="color: inherit;"}
-
 - de Brouwer AJ., Carter MJ., Smail LC., Wolpert DM., Gallivan JP., & Flanagan JR.
@@
 
-## In Press
+## Accepted or In Press
+
+- Calalo JA, Ngo T, Sullivan S, Roth A, Lokesh R, Buggeln JH, Strand K, Marchhart V, Carter MJ, Kurtzer I, & Cashaback JGA.
+(Accepted).
+Online movements reflect ongoing deliberation.
+*Journal of Neuroscience*.
+
+## 2025
 
 - Sullivan SR., Lokesh R., Peters CS., Calalo J., Roth AR., Buggeln JH., Ngo TT., Carter MJ., & Cashaback JGA.
-(In Press).
+(2025).
 Indecision under time pressure arises from suboptimal switching behaviour.
@@
 [{{< ai doi >}}](https://doi.org/10.1152/jn.00563.2024){target="_blank" style="color: inherit;"}
-
-## 2025
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2025_sullivan-etal_indecision-under-time-pressure-arises-from-suboptimal-switching-behavior.pdf){target="_blank" style="color: inherit;"}
 

### 2025-07-03 index.qmd
add DOI
add new paper acceptance
add doi for jneurosci paper

@@
 
+<font color="#d08770">[June 13 2024].</font> **Paper accepted**.
+Calalo JA, Ngo T, Sullivan S, Roth A, Lokesh R, Buggeln JH, Strand K, Marchhart V, Carter MJ, Kurtzer I, & Cashaback JGA.
+(Accepted).
+Online movements reflect ongoing deliberation.
+*Journal of Neuroscience*.
+[https://doi.org/10.1523/JNEUROSCI.1913-24.2025](https://doi.org/10.1523/JNEUROSCI.1913-24.2025){target="_blank"}
+
 <font color="#d08770">[May 14 2024].</font> **Paper accepted**.
 Sullivan SR, Lokesh R, Peters CS, Calalo J, Roth AR, Buggeln JH, Ngo TT, Carter MJ, & Cashaback JGA.
-(Accepted).
+(In Press).
 Indecision under time pressure arises from suboptimal switching behaviour.
 *Journal of Neurophysiology*.
+[https://doi.org/10.1152/jn.00563.2024](https://doi.org/10.1152/jn.00563.2024){target="_blank"}
 

### 2025-07-21 team.qmd
update team page

@@
   <h4> Jiaqiao Tang, M.Sc.PT </h4>
-  <p> Ph.D. Student </p>
+  <p> Ph.D. Candidate </p>
   <p> tangj24 [at] mcmaster [dot] ca</p>
@@
 <div class="team-member">
-  <img src="images/daniel-deletsu.jpg" alt="images/daniel-deletsu.jpg" class="team-img">
-  <div class="team-info">
-  <h4> Daniel Deletsu, B.Sc. </h4>
-  <p> M.Sc. Candidate </p>
-  <p> deletsud [at] mcmaster [dot] ca </p>
-  </div>
-</div>
-
-<div class="team-member">
   <img src="images/michael-croteau.jpg" alt="images/michael-croteau.jpg" class="team-img">
@@
   <h4> Michael Croteau </h4>
-  <p> M.Sc. Student </p>
+  <p> Incoming M.Sc. Student - Fall 2025 </p>
   <p> croteaum [at] mcmaster [dot] ca </p>
@@
   <p> McMaster Institute for Research on Aging 2025 Summer Research Fellowship Winner </p>
+  </div>
+</div>
+
+<div class="team-member">
+  <img src="images/lab-logo.png" alt="images/" class="team-img">
+  <div class="team-info">
+  <h4> Kaylen Rathwell </h4>
+  <p> Lab Technician </p>
+  <p> motorlab [at] mcmaster [dot] ca </p>
   </div>
@@
 
-<div class="team-member">
-  <img src="images/headshot_lil-quack.jpg" alt="images/headshot_lil-quack.jpg" class="team-img">
-  <div class="team-info">
-  <h4> Lil Quack </h4>
-  <p> Lab duck </p>
-  </div>
-</div>
-
 ## Collaborators
@@
 
-**Mikayla Lalli**, M.Sc. Kinesiology (2022-24); *Ph.D. student in the lab*.  
+**Daniel Deletsu**, M.Sc. Kinesiology (2023-25); *Medical School at Western University*  
+**Mikayla Lalli**, M.Sc. Kinesiology (2022-24); *Ph.D. student in the lab*  
 **Nour Al Afif**, M.Sc. Kinesiology (2022-24); *Ph.D. student in the lab*  

### 2025-07-29 index.qmd
fix author orderings

@@
 <font color="#d08770">[June 13 2024].</font> **Paper accepted**.
-Calalo JA, Ngo T, Sullivan S, Roth A, Lokesh R, Buggeln JH, Strand K, Marchhart V, Carter MJ, Kurtzer I, & Cashaback JGA.
+Calalo JA, Ngo T, Sullivan S, Strand K, Buggeln JH, Lokesh R, Roth A, Carter MJ, Kurtzer IL, & Cashaback JGA.
 (Accepted).
@@
 <font color="#d08770">[May 14 2024].</font> **Paper accepted**.
-Sullivan SR, Lokesh R, Peters CS, Calalo J, Roth AR, Buggeln JH, Ngo TT, Carter MJ, & Cashaback JGA.
+Sullivan SR, Lokesh R, Calalo J, Ngo TT, Buggeln JH, Roth AR, Peters CS, Kurtzer IL, Carter MJ, & Cashaback JGA.
 (In Press).

### 2025-07-29 papers.qmd
add doi for jneurosci paper
fix author orderings

@@
 
-- Calalo JA, Ngo T, Sullivan S, Roth A, Lokesh R, Buggeln JH, Strand K, Marchhart V, Carter MJ, Kurtzer I, & Cashaback JGA.
+- Calalo JA., Ngo T., Sullivan S., Strand K., Buggeln JH., Lokesh R., Roth A., Carter MJ., Kurtzer IL., & Cashaback JGA..
 (Accepted).
@@
 *Journal of Neuroscience*.
+---
+[{{< ai doi >}}](https://doi.org/10.1523/JNEUROSCI.1913-24.2025){target="_blank" style="color: inherit;"}
 
@@
 
-- Sullivan SR., Lokesh R., Peters CS., Calalo J., Roth AR., Buggeln JH., Ngo TT., Carter MJ., & Cashaback JGA.
+- Sullivan SR., Lokesh R., Calalo J., Ngo TT., Buggeln JH., Roth AR., Peters CS., Kurtzer IL., Carter MJ., & Cashaback JGA.
 (2025).

### 2025-07-31 papers.qmd
update papers

@@
 
-## Accepted or In Press
+<!-- ## Accepted or In Press -->
+
+## 2025
 
 - Calalo JA., Ngo T., Sullivan S., Strand K., Buggeln JH., Lokesh R., Roth A., Carter MJ., Kurtzer IL., & Cashaback JGA..
-(Accepted).
+(2025).
 Online movements reflect ongoing deliberation.
@@
 [{{< ai doi >}}](https://doi.org/10.1523/JNEUROSCI.1913-24.2025){target="_blank" style="color: inherit;"}
-
-## 2025
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2025_calalo-etal_online-movements-reflect-ongoing-deliberation.pdf){target="_blank" style="color: inherit;"}
 

### 2025-08-01 index.qmd
add new preprint info

@@
 
+<font color="#d08770">[July 31 2025].</font> **New Preprint**.
+Sullivan SR, Buggeln JH, Calalo JA, Ngo TT, Semrau JA, Carter MJ, & Cashaback JGA.
+Involuntary feedback responses reflect a representation of partner actions.
+*bioR$\chi$iv*.
+[https://doi.org/10.1101/2025.07.29.667240](https://doi.org/10.1101/2025.07.29.667240){target="_blank"}
+
 <font color="#d08770">[June 13 2024].</font> **Paper accepted**.
@@
 [https://doi.org/10.1152/jn.00563.2024](https://doi.org/10.1152/jn.00563.2024){target="_blank"}
-
-<font color="#d08770">[April 22 2025].</font> **Announcement**. The application period for practicum, project, or thesis positions in the lab for the 2025-26 academic year is now closed.
-
-<font color="#d08770">[March 03 2025].</font> **New Preprint**.
-Lalli M, Al Afif N, Tang J, Hasan H, Dissanayake E, Sussman V, Lokesh R, Rathwell S, Cashaback JGA, & Carter MJ.
-Preferences for costly cooperation are highly individualized.
-*PsyAr$\chi$iv*.
-[https://doi.org/10.31234/osf.io/3qaeu_v3](https://doi.org/10.31234/osf.io/3qaeu_v3){target="_blank"}

### 2025-08-01 papers.qmd
add new preprint info

@@
 
-- Lalli, M., Al Afif, N., Tang, J., Hasan, H., Dissanayake, E., Sussman, V., Lokesh, R., Rathwell, S., Cashaback, JGA., & Carter, MJ.
+- Sullivan SR., Buggeln JH., Calalo JA., Ngo TT., Semrau JA., Carter MJ., & Cashaback JGA..
+Involuntary feedback responses reflect a representation of partner actions.
+*bioR$\chi$iv*.
+--- [{{< ai doi >}}](https://doi.org/10.1101/2025.07.29.667240){target="_blank" style="color: inherit;"}
+
+- Lalli, M., Al Afif, N., Tang J., Hasan H., Dissanayake E., Sussman V., Lokesh R., Rathwell S., Cashaback JGA., & Carter MJ.
 Preferences for costly cooperation are highly individualized.

### 2025-08-26 index.qmd
add lab manual link

@@
 
+<font color="#d08770">[August 26 2025].</font> **New member**.
+Welcome to Michael Croteau, who is starting his M.Sc studies.
+Michael previously completed his undergraduate project and thesis courses in the lab.
+
 <font color="#d08770">[July 31 2025].</font> **New Preprint**.
@@
 [https://doi.org/10.1523/JNEUROSCI.1913-24.2025](https://doi.org/10.1523/JNEUROSCI.1913-24.2025){target="_blank"}
-
-<font color="#d08770">[May 14 2024].</font> **Paper accepted**.
-Sullivan SR, Lokesh R, Calalo J, Ngo TT, Buggeln JH, Roth AR, Peters CS, Kurtzer IL, Carter MJ, & Cashaback JGA.
-(In Press).
-Indecision under time pressure arises from suboptimal switching behaviour.
-*Journal of Neurophysiology*.
-[https://doi.org/10.1152/jn.00563.2024](https://doi.org/10.1152/jn.00563.2024){target="_blank"}

### 2025-08-26 news.qmd
add new paper acceptance
add doi for jneurosci paper
add lab manual link

@@
 ---
+
+<font color="#d08770">[August 26 2025].</font> **New member**.
+Welcome to Michael Croteau, who is starting his M.Sc studies.
+Michael previously completed his undergraduate project and thesis courses in the lab.
+
+<font color="#d08770">[July 31 2025].</font> **New Preprint**.
+Sullivan SR, Buggeln JH, Calalo JA, Ngo TT, Semrau JA, Carter MJ, & Cashaback JGA.
+Involuntary feedback responses reflect a representation of partner actions.
+*bioR$\chi$iv*.
+[https://doi.org/10.1101/2025.07.29.667240](https://doi.org/10.1101/2025.07.29.667240){target="_blank"}
+
+<font color="#d08770">[June 13 2024].</font> **Paper accepted**.
+Calalo JA, Ngo T, Sullivan S, Roth A, Lokesh R, Buggeln JH, Strand K, Marchhart V, Carter MJ, Kurtzer I, & Cashaback JGA.
+(Accepted).
+Online movements reflect ongoing deliberation.
+*Journal of Neuroscience*.
+[https://doi.org/10.1523/JNEUROSCI.1913-24.2025](https://doi.org/10.1523/JNEUROSCI.1913-24.2025){target="_blank"}
 

### 2025-08-26 team.qmd
update team page
add lab manual link

@@
   <h4> Mikayla Lalli, M.Sc. </h4>
-  <p> Ph.D. Student </p>
+  <p> Ph.D. Candidate </p>
   <p> lallim1 [at] mcmaster [dot] ca </p>
@@
   <h4> Nour Al Afif, M.Sc. </h4>
-  <p> Ph.D. Student </p>
+  <p> Ph.D. Candidate </p>
   <p> alafin1 [at] mcmaster [dot] ca </p>
@@
   <h4> Michael Croteau </h4>
-  <p> Incoming M.Sc. Student - Fall 2025 </p>
+  <p> M.Sc. Student </p>
   <p> croteaum [at] mcmaster [dot] ca </p>
-  </div>
-</div>
-
-<div class="team-member">
-  <img src="images/maria-alex.png" alt="images/" class="team-img">
-  <div class="team-info">
-  <h4> Maria Alex </h4>
-  <p> Undergraduate Research Assistant </p>
-  <p> McMaster Institute for Research on Aging 2025 Summer Research Fellowship Winner </p>
-  </div>
-</div>
-
-<div class="team-member">
-  <img src="images/lab-logo.png" alt="images/" class="team-img">
-  <div class="team-info">
-  <h4> Kaylen Rathwell </h4>
-  <p> Lab Technician </p>
-  <p> motorlab [at] mcmaster [dot] ca </p>
   </div>

### 2025-09-08 teaching.qmd
minor changes and add 2mc3 link

--- 2023-07-13 teaching.qmd
@@
 
-Updates in progress...
+<style>
+.course-listing {
+  display: flex;
+  align-items: center;
+  padding: 20px; 
+  border: 1px solid #ddd;
+  margin-bottom: 20px;
+}
+
+.course-img {
+  margin-right: 20px;
+  width: 175px;
+  height: 175px;
+  border-radius: 50%;
+  object-fit: cover;
+}
+
+.course-info {
+  display: flex;
+  flex-direction: column;
+}
+</style>
+
+<div class="course-listing">
+  <img src="images/logo-2mc3.png" alt="images/logo-2mc3.png" class="course-img">
+  <div class="course-info">
+  <h4> [Motor Control and Learning](https://carterjmike.github.io/kinesiol-2mc3/) </h4>
+  <p> KINESIOL 2MC3 </p>
+  <p> Sept-Dec 2025 </p>
+  </div>
+</div>

### 2025-09-26 index.qmd
add new paper info

@@
 #### Recent lab news ---------
+
+<font color="#d08770">[September 26 2024].</font> **Paper accepted**.
+Hussain M, Foglia SD, Park J, Ramdeo KR, Adams FC, Drapeau CC, Bobinski AR, Carter MJ, & Nelson AJ.
+Ipsilateral contraction increases map area and decreases motor threshold for contralateral hand muscle.
+*Neuroscience*.
+[https://doi.org/10.1016/j.neuroscience.2025.09.034](https://doi.org/10.1016/j.neuroscience.2025.09.034){target="_blank"}
 

### 2025-09-26 news.qmd
add new paper info

@@
 ---
+
+<font color="#d08770">[September 26 2024].</font> **Paper accepted**.
+Hussain M, Foglia SD, Park J, Ramdeo KR, Adams FC, Drapeau CC, Bobinski AR, Carter MJ, & Nelson AJ.
+Ipsilateral contraction increases map area and decreases motor threshold for contralateral hand muscle.
+*Neuroscience*.
+[https://doi.org/10.1016/j.neuroscience.2025.09.034](https://doi.org/10.1016/j.neuroscience.2025.09.034){target="_blank"}
 

### 2025-09-26 papers.qmd
add new paper info

@@
 ## 2025
+
+- Hussain M., Foglia SD., Park J., Ramdeo KR., Adams FC., Drapeau CC., Bobinski AR., Carter MJ., & Nelson AJ.
+Ipsilateral contraction increases map area and decreases motor threshold for contralateral hand muscle.
+*Neuroscience*.
+---
+[{{< ai doi >}}](https://doi.org/10.1016/j.neuroscience.2025.09.034){target="_blank" style="color: inherit;"}
+[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2025_hussain-etal_ipsilateral-contraction-increases-map-area-and-decreases-motor-threshold-for-contralateral-hand-muscle.pdf){target="_blank" style="color: inherit;"}
 

### 2025-12-18 index.qmd
add new preprint

@@
 
+<font color="#d08770">[December 15 2025].</font> **New Preprint**.
+Calalo JA, Sullivan SR, Muscara NR, Buggeln JH, Ngo TT, Short MM, Carter MJ, Kurtzer IL, & Cashaback JGA.
+Deliberation is a controllable process governed by desirability and cognitive effort.
+*bioR$\chi$iv*.
+[https://doi.org/10.64898/2025.12.12.693733](https://doi.org/10.64898/2025.12.12.693733 ){target="_blank"}
+
 <font color="#d08770">[September 26 2024].</font> **Paper accepted**.
@@
 Involuntary feedback responses reflect a representation of partner actions.
-*bioR$\chi$iv*.
-[https://doi.org/10.1101/2025.07.29.667240](https://doi.org/10.1101/2025.07.29.667240){target="_blank"}
-
-<font color="#d08770">[June 13 2024].</font> **Paper accepted**.
-Calalo JA, Ngo T, Sullivan S, Strand K, Buggeln JH, Lokesh R, Roth A, Carter MJ, Kurtzer IL, & Cashaback JGA.
-(Accepted).
-Online movements reflect ongoing deliberation.
-*Journal of Neuroscience*.
-[https://doi.org/10.1523/JNEUROSCI.1913-24.2025](https://doi.org/10.1523/JNEUROSCI.1913-24.2025){target="_blank"}
+*bioR$\chi$iv*. [https://doi.org/10.1101/2025.07.29.667240](https://doi.org/10.1101/2025.07.29.667240){target="_blank"}

### 2025-12-18 news.qmd
add new preprint

@@
 ---
+
+<font color="#d08770">[December 15 2025].</font> **New Preprint**.
+Calalo JA, Sullivan SR, Muscara NR, Buggeln JH, Ngo TT, Short MM, Carter MJ, Kurtzer IL, & Cashaback JGA.
+Deliberation is a controllable process governed by desirability and cognitive effort.
+*bioR$\chi$iv*.
+[https://doi.org/10.64898/2025.12.12.693733](https://doi.org/10.64898/2025.12.12.693733 ){target="_blank"}
 

### 2025-12-18 papers.qmd
add new preprint

@@
 
-- Sullivan SR., Buggeln JH., Calalo JA., Ngo TT., Semrau JA., Carter MJ., & Cashaback JGA..
+- Calalo JA., Sullivan SR., Muscara NR., Buggeln JH., Ngo TT., Short MM., Carter MJ., Kurtzer IL., & Cashaback JGA.
+Deliberation is a controllable process governed by desirability and cognitive effort.
+*bioR$\chi$iv*.
+--- [{{< ai doi >}}](https://doi.org/10.64898/2025.12.12.693733){target="_blank" style="color: inherit;"}
+
+- Sullivan SR., Buggeln JH., Calalo JA., Ngo TT., Semrau JA., Carter MJ., & Cashaback JGA.
 Involuntary feedback responses reflect a representation of partner actions.
@@
 - Hussain M., Foglia SD., Park J., Ramdeo KR., Adams FC., Drapeau CC., Bobinski AR., Carter MJ., & Nelson AJ.
+(2025).
 Ipsilateral contraction increases map area and decreases motor threshold for contralateral hand muscle.
